### 2019-12-09 paper/paper.tex
set up project structure

%% For double-blind review submission, w/o CCS and ACM Reference (max submission space)
% \documentclass[sigplan,10pt,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
\documentclass[sigplan,10pt,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For double-blind review submission, w/ CCS and ACM Reference
%\documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=true}
%% For single-blind review submission, w/o CCS and ACM Reference (max submission space)
%\documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For single-blind review submission, w/ CCS and ACM Reference
%\documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true}
%% For final camera-ready submission, w/ required CCS and ACM Reference
% \documentclass[acmsmall]{acmart}\settopmatter{}

%% Journal information
%% Supplied to authors by publisher for camera-ready submission;
%% use defaults for review submission.
\acmJournal{PACMPL}
\acmVolume{1}
\acmNumber{CONF} % CONF = POPL or ICFP or OOPSLA
\acmArticle{1}
\acmYear{2018}
\acmMonth{1}
\acmDOI{} % \acmDOI{10.1145/nnnnnnn.nnnnnnn}
\startPage{1}

%% Copyright information
%% Supplied to authors (based on authors' rights management selection;
%% see authors.acm.org) by publisher for camera-ready submission;
%% use 'none' for review submission.
\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\copyrightyear{2018}           %% If different from \acmYear

%% Bibliography style
\bibliographystyle{ACM-Reference-Format}
%% Citation style
%% Note: author/year citations are required for papers published as an
%% issue of PACMPL.
% \citestyle{acmauthoryear}   %% For author/year citations

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Note: Authors migrating a paper from PACMPL format to traditional
%% SIGPLAN proceedings format must update the '\documentclass' and
%% topmatter commands above; see 'acmart-sigplanproc-template.tex'.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% Some recommended packages.
\usepackage{booktabs}   %% For formal tables:
                        %% http://ctan.org/pkg/booktabs
\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
                        %% http://ctan.org/pkg/subcaption
\usepackage{xcolor}
\usepackage{listings}
\lstset{
  basicstyle=\fontsize{9}{10}\selectfont\ttfamily,
  numbers=left,
  numberstyle= \tiny,
  keywordstyle= \color{ blue!70},
  commentstyle= \color{red!50!green!50!blue!50},
  frame=single,
  rulesepcolor= \color{ red!20!green!20!blue!20} ,
  escapeinside=``,
  xleftmargin=1.5em,xrightmargin=0em, aboveskip=1em,
  framexleftmargin=2em,
  showstringspaces=false,
  showtabs=false,
  breaklines=true
}
\lstdefinelanguage{Solidity}
{
  morekeywords={contract, mapping, address, uint, private, function, public, if, payable},
  morecomment=[l]{//},
  morestring=[b]"
}

\usepackage{multicol}
\usepackage{lipsum}
\usepackage{mathtools}
\usepackage{cuted}

\usepackage{amsmath}
\usepackage{extpfeil}
\usepackage{mathpartir}
\usepackage[mathscr]{eucal}

\usepackage{hyperref}
\usepackage{cleveref}

\crefformat{section}{\S#2#1#3} % see manual of cleveref, section 8.2.1
\crefformat{subsection}{\S#2#1#3}
\crefformat{subsubsection}{\S#2#1#3}

\begin{document}

%% Title information
\title[]{NO TITLE}         %% [Short Title] is optional;
%% when present, will be used in
%% header instead of Full Title.
%\titlenote{ }             %% \titlenote is optional;
%% can be repeated if necessary;
%% contents suppressed with 'anonymous'
%\subtitle{Subtitle}                     %% \subtitle is optional
%\subtitlenote{with subtitle note}       %% \subtitlenote is optional;
%% can be repeated if necessary;
%% contents suppressed with 'anonymous'

%% Author information
%% Contents and number of authors suppressed with 'anonymous'.
%% Each author should be introduced by \author, followed by
%% \authornote (optional), \orcid (optional), \affiliation, and
%% \email.
%% An author may have multiple affiliations and/or emails; repeat the
%% appropriate command.
%% Many elements are not rendered, but should be provided for metadata
%% extraction tools.

\author{Yichen Xie}
% \authornote{Supervised by Qinxiang Cao, Shanghai Jiao Tong University, John Hopcroft Center for Computer Science.}          %% \authornote is optional;
%% can be repeated if necessary
%\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{
	%\position{Position2b}
	%\department{Department2b}             %% \department is recommended
	\institution{Shanghai Jiao Tong University}           %% \institution is required
	%\streetaddress{Street3b Address2b}
	%\city{City2b}
	%\state{State2b}
	%\postcode{Post-Code2b}
	%\country{Country2b}                   %% \country is recommended
}
% \email{}          %% \email is recommended

\author{Zhongye Wang}
% \authornote{Supervised by Qinxiang Cao, Shanghai Jiao Tong University, John Hopcroft Center for Computer Science.}          %% \authornote is optional;
%% can be repeated if necessary
%\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{
	%\position{Position2b}
	%\department{Department2b}             %% \department is recommended
	\institution{Shanghai Jiao Tong University}           %% \institution is required
	%\streetaddress{Street3b Address2b}
	%\city{City2b}
	%\state{State2b}
	%\postcode{Post-Code2b}
	%\country{Country2b}                   %% \country is recommended
}
\email{wangzhongye1110@sjtu.edu.cn}          %% \email is recommended

\author{Xinyu Zhan}
% \authornote{Supervised by Qinxiang Cao, Shanghai Jiao Tong University, John Hopcroft Center for Computer Science.}          %% \authornote is optional;
%% can be repeated if necessary
%\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
\affiliation{
	%\position{Position2b}
	%\department{Department2b}             %% \department is recommended
	\institution{Shanghai Jiao Tong University}           %% \institution is required
	%\streetaddress{Street3b Address2b}
	%\city{City2b}
	%\state{State2b}
	%\postcode{Post-Code2b}
	%\country{Country2b}                   %% \country is recommended
}
% \email{}          %% \email is recommended

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
  The abstract \dots
\end{abstract}

%% 2012 ACM Computing Classification System (CSS) concepts
%% Generate at 'http://dl.acm.org/ccs/ccs.cfm'.

%% End of generated code

%% Keywords
%% comma separated list
\keywords{}  %% \keywords are mandatory in final camera-ready submission

%% \maketitle
%% Note: \maketitle command must come after title commands, author
%% commands, abstract environment, Computing Classification System
%% environment and commands, and keywords command.
\maketitle

\section{Introduction}
The introduction \dots

\section{Body}
The body \dots

\section{Related Work}
The related work \dots

\section{Conclusion}
The conclusion \dots

% Acknowledgments

% Bibliography
% \bibliographystyle{acm}
% \bibliographystyle{unsrt}
\bibliography{../full_list.bib}

%% Appendix
%\appendix
%\section{Appendix}

%Text of appendix \ldots

\end{document}

### 2019-12-09 proposal/proposal.tex
set up project structure

--- 2019-12-09 paper/paper.tex
@@
 % \documentclass[sigplan,10pt,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
-\documentclass[sigplan,10pt,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
 %% For double-blind review submission, w/ CCS and ACM Reference
@@
 %% For final camera-ready submission, w/ required CCS and ACM Reference
-% \documentclass[acmsmall]{acmart}\settopmatter{}
+\documentclass[acmsmall,nonacm]{acmart}\settopmatter{}
 
@@
 \lstset{
-  basicstyle=\fontsize{9}{10}\selectfont\ttfamily,
+  basicstyle=\fontsize{8}{10}\selectfont\ttfamily,
   numbers=left,
@@
 
+% \usepackage{biblatex}
+
 \usepackage{multicol}
@@
 
+\usepackage{caption}
+
 \usepackage{hyperref}
 \usepackage{cleveref}
+
+% \usepackage[style=authoryear-comp]{biblatex}
+% \DeclareLabeldate[online]{%
+%   \field{date}
+%   \field{year}
+%   \field{eventdate}
+%   \field{origdate}
+%   \field{urldate}
+% }
+% \DeclareLabeldate{\field{date}\field{eventdate} \field{origdate}\literal{nodate}}
+
+% \DefineBibliographyStrings{english}{%
+% nodate = {\ifboolexpr{test{\ifentrytype{misc1}} or test{\ifentrytype{misc5}}}{}{o\adddot D\adddot}},
+% }
 
@@
 %% Title information
-\title[]{NO TITLE}         %% [Short Title] is optional;
+\title[]{CS222 Project Proposal}         %% [Short Title] is optional;
 %% when present, will be used in
 %% header instead of Full Title.
-%\titlenote{ }             %% \titlenote is optional;
-%% can be repeated if necessary;
-%% contents suppressed with 'anonymous'
-%\subtitle{Subtitle}                     %% \subtitle is optional
-%\subtitlenote{with subtitle note}       %% \subtitlenote is optional;
-%% can be repeated if necessary;
-%% contents suppressed with 'anonymous'
-
-%% Author information
-%% Contents and number of authors suppressed with 'anonymous'.
-%% Each author should be introduced by \author, followed by
-%% \authornote (optional), \orcid (optional), \affiliation, and
-%% \email.
-%% An author may have multiple affiliations and/or emails; repeat the
-%% appropriate command.
-%% Many elements are not rendered, but should be provided for metadata
-%% extraction tools.
 
@@
 
-%% Abstract
-%% Note: \begin{abstract}...\end{abstract} environment must come
-%% before \maketitle command
-\begin{abstract}
-  The abstract \dots
-\end{abstract}
+% %% Abstract
+% %% Note: \begin{abstract}...\end{abstract} environment must come
+% %% before \maketitle command
+% \begin{abstract}
+% 	Text of abstract \ldots
+% \end{abstract}
 
@@
 
+% xyc, until the last
 \section{Introduction}
-The introduction \dots
 
-\section{Body}
-The body \dots
+% xyc
+\section{Problem Description}
 
+% xzy
+\section{Problem Formulation}
+
+% zxy
 \section{Related Work}
-The related work \dots
 
-\section{Conclusion}
-The conclusion \dots
-
-% Acknowledgments
+%% Acknowledgments
 

### 2019-12-09 proposal/proposal.tex
update formulation and bib

@@
 
-% xzy
+% wzy
 \section{Problem Formulation}
+There has not been much time for us to fully consider the optimal way of addressing those problems, but we do propose one possible formulation and the solution idea in this section.
+
+Assume there are $N$ classes in total, each denoted by $A_i$.
+We further divide each class $A_i$ into $M_i$ subsets $A_{ij}$ according to some features of samples, e.g., the activation of certain convolution filters.
+Now, we have a set $\mathcal{D}$ of $K$ (a relatively large number) binary classifiers each identifying a subset of all $A_{ij}$ classes.
+Say classifier $d$ separates $\{A_{ij} \,|\, (i, j) \in I_d\}$ from the rest of classes, i.e., given any sample, it determines wether the label of the sample belongs to $I_d$.
+Here, $I_d$ is the positive label set defined by the classifier $d$.
+Note that we can always define another classifier whose positive label set is exactly the negative label set of the classifier $d$.
+
+Our task is to find a subset $\mathcal{D}^* \subset \mathcal{D}$, such that for any class $A_i$, there exists a partition that divides it into some subclasses $S_i^{(l)}$ where $\bigcup_l \{A_{ij} \,|\, (i, j) \in S_i^{(l)}\} = A_i$, and for each subclass $S_i^{(l)}$ there exists a subset of classifiers $D^{(l)} \subseteq \mathcal{D}^*$ where $S_i^{(l)} = \bigcap_d \{I_d \,|\, d \in D^{(l)}\}$.
+Here, subclass $S_i^{(l)}$ represents the union of some subsets $A_{ij}$ of class $A_i$, and the union of all subclasses of $A_i$ should reconstruct the $A_i$ itself.
+The optimal set of classifiers $\mathcal{D}^*$ should allow us to determine wether a sample belongs to any given subclass $S_i^{(l)}$ using a subset $D^{(l)}$ in it, which in turn determines wether the sample belongs to $A_i$.
+
+There are further constraints and considerations on the optimal set of classifiers $\mathcal{D}^*$.
+\begin{itemize}
+    \item \textbf{Number of Classifiers.} We need to choose adequate number of classifiers $|\mathcal{D}^*|$ so that it covers all classes.
+But we prefer to use as less classifiers as possible to save computational consumptions.
+    \item \textbf{Network Size.} The size for each classifier is limited.
+Large networks as classifiers improve accuracy but slow down inferences.
+Therefore, we will have penalty for large classifiers.
+    \item \textbf{Overall Accuracy.} We know the accuracy of each classifier as a prior, but we need to derive the overall accuracy based on it.
+The $\mathcal{D}^*$ should optimize the overall accuracy along with other goals.
+\end{itemize}
+These are factors we will consider in the later development and we are open for other suggestions.
 

### 2019-12-09 proposal/proposal.tex
include an example in formulation and update notation

@@
 
-Our task is to find a subset $\mathcal{D}^* \subset \mathcal{D}$, such that for any class $A_i$, there exists a partition that divides it into some subclasses $S_i^{(l)}$ where $\bigcup_l \{A_{ij} \,|\, (i, j) \in S_i^{(l)}\} = A_i$, and for each subclass $S_i^{(l)}$ there exists a subset of classifiers $D^{(l)} \subseteq \mathcal{D}^*$ where $S_i^{(l)} = \bigcap_d \{I_d \,|\, d \in D^{(l)}\}$.
+Our task is to find a subset $D^* \subset \mathcal{D}$, such that for any class $A_i$, there exists a partition that divides it into some subclasses $S_i^{(l)}$ where $A_i = \bigcup_l \{A_{ij} \,|\, (i, j) \in S_i^{(l)}\}$, and for each subclass $S_i^{(l)}$ there exists a subset of classifiers $D^{(l)} \subseteq D^*$ where $S_i^{(l)} = \bigcap_d \{I_d \,|\, d \in D^{(l)}\}$.
 Here, subclass $S_i^{(l)}$ represents the union of some subsets $A_{ij}$ of class $A_i$, and the union of all subclasses of $A_i$ should reconstruct the $A_i$ itself.
-The optimal set of classifiers $\mathcal{D}^*$ should allow us to determine wether a sample belongs to any given subclass $S_i^{(l)}$ using a subset $D^{(l)}$ in it, which in turn determines wether the sample belongs to $A_i$.
+The optimal set of classifiers $D^*$ should allow us to determine wether a sample belongs to any given subclass $S_i^{(l)}$ using a subset $D^{(l)}$ in it, which in turn determines wether the sample belongs to $A_i$.
+Figure~\ref{fig:feasible-example} shows a feasible classifier set $D$ in a simple example.
 
-There are further constraints and considerations on the optimal set of classifiers $\mathcal{D}^*$.
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.45\linewidth]{fig/formulation_example.png}
+    \caption{An Example of Feasible Classifier Set:
+    The samples in class $A_1$ is further divided into $A_{11}, A_{12}$ and those in class $A_2$ is further divided into $A_{21}, A_{22}, A_{23}$.
+    We do not divide $A_3$ but rename it to $A_{31}$.
+    There are 4 discriminators $d_1, d_2, d_3, d_4$ respectively identify $\{A_{11}, A_{12}, A_{21}, A_{22}\}$, $\{A_{21}, A_{31}\}$, $\{A_{22}, A_{23}\}$, and $\{A_{23}, A_{31}\}$.
+    We have: \textit{(a)} the intersection of $d_1$ and the compliments of $d_2, d_3$ identifies $A_1 = A_{11} \cup A_{12}$;
+    \textit{(b)} the intersection of $d_1$ and $d_2$ identifies $A_{21}$, and its union with $d_3$ determines the entire $A_2$;
+    \textit{(c)} the intersection of $d_3$ and the compliment of $d_1$ determines $A_3 = A_{31}$.
+    Clearly, $D = \{d_1, d_2, d_3\}$ is a feasible set, where the redundant classifier $d_4$ is not selected.}
+    \label{fig:feasible-example}
+\end{figure}
+
+There are further constraints and considerations of the optimal set of classifiers $D^*$.
 \begin{itemize}
-    \item \textbf{Number of Classifiers.} We need to choose adequate number of classifiers $|\mathcal{D}^*|$ so that it covers all classes.
+    \item \textbf{Number of Classifiers.} We need to choose adequate number of classifiers $|D^*|$ so that it covers all classes.
 But we prefer to use as less classifiers as possible to save computational consumptions.
@@
     \item \textbf{Overall Accuracy.} We know the accuracy of each classifier as a prior, but we need to derive the overall accuracy based on it.
-The $\mathcal{D}^*$ should optimize the overall accuracy along with other goals.
+The $D^*$ should optimize the overall accuracy along with other goals.
 \end{itemize}

### 2019-12-09 proposal/proposal.tex
Update proposal.tex

@@
 \section{Introduction}
+Recent years have witnessed the rapid development of deep learning(DL).
+Due to the irreplaceable roles of these models in data processing, it is promising to implement it on these edge device such as wearable device.
+However, limited energy supply and computing capabilities on edge device lead to constraint on the scale and depth of the deep learning model.
+Thus, light-weight models are required to fit these features of edge device.
+
+In this project, we propose a combination of light-weight neural networks to substitute the original large deep learning model.
+With this new model, we will try to reduce the parameter number and computing consumption notably at the expense of acceptable accuracy decline compared to the original large model.
 
@@
 \section{Problem Description}
+We mainly deal with the issue to replace a large deep learning model with a set of small models which must be featured with less depth.
+Moreover, the number of small models cannot be too large.
+Equivalently, the sum of parameter number in all small models must be much less than the original model.
+Then, the total computing consumption can decrease definitely.
+As a result, edge device can profit from the lower demand for implementation platforms.
+And these small models are independent from the original deep learning network at least in the inference phase.
+Hence, they can process the data on the edge device without communiction with the cloud or servers, which extend the application range of these device.
+
+We will take the example of image recognition.
+At present, AdaBoost tends to be one possible solution.
+However, the weaker learners in these algorithm, which may be very simple classifiers, are so susceptible that the outcome is senstitive to noisy data and outliers.
+By contrast, thanks to the application of neural networks and more sophiscated combination methods, we will attempt to pursue a more robust and accurate model.
 
@@
 But we prefer to use as less classifiers as possible to save computational consumptions.
-    \item \textbf{Network Size.} The size for each classifier is limited.
-Large networks as classifiers improve accuracy but slow down inferences.
-Therefore, we will have penalty for large classifiers.
+    \item \textbf{Network Size.} The size of each classifier is limited. Large networks as classifiers improve accuracy but slow down inferences. Therefore, we will have penalty for large classifiers.
     \item \textbf{Overall Accuracy.} We know the accuracy of each classifier as a prior, but we need to derive the overall accuracy based on it.

### 2019-12-10 proposal/proposal.tex
update intro, problem desc and formu

--- 2019-12-09 proposal/proposal.tex
@@
 \section{Introduction}
+% Recent years have witnessed the rapid development of deep learning.
+The development of deep learning has proved its great capability, and it will be more beneficial if we can plant deep learning models into edge devices like wearable devices.
+However, the limited energy supply and computational capability of edge devices lead to constraints on the scale and complexity of deep neural networks.
+We need light-weight models to meet these requirements of edge device.
+In this project, we will seek for a combination of light-weight neural networks to substitute the original complex model while preserving its functionality.
+% With this new model, we will try to reduce the parameter number and computing consumption notably at the expense of acceptable accuracy decline compared to the original large model.
 
@@
 \section{Problem Description}
+We mainly focus on the task to replace a large deep learning model with a set of small models with reduced complexity.
+Using too many small models can still result in tremendous amount of calculation in inference and affect models' performance in edge devices, so we limit the overall complexity of models as well.
+% Then, the total computational consumption can decrease definitely.
+As a result, edge device can profit from the lowered demand for computational consumption.
+% And these small models are independent from the original deep learning network at least in the inference phase.
+% Hence, they can process the data on the edge device without communication with the cloud or servers, which extend the application range of these device.
+
+There are many possible approaches in the design of small model system.
+\begin{itemize}
+  \item We could train small models each with specific tasks, which can be implemented with satisfying performance and simple network structure.
+  \item We could train small models each dealing with part of the dataset, which can be combined to handle all data points efficiently.
+\end{itemize}
+Our focus will be the former one, where we want each model to perform binary decisions in the context of classification and the union of these models should uniquely determine the category of any sample.
+In this way, small models serve as feature extractors that jointly produce an embedding for the data sample.
+We can also retrieve such embedding implicitly using neural networks, but we choose to achieve the optimal embedding explicitly by solving the search problem formulated in \cref{sec:formulation}.
+
+We will take the image recognition (classification) task as the example throughout the project.
+At present, AdaBoost tends to be one possible solution.
+However, the weaker learners in these algorithm, which may be very simple classifiers, are so susceptible that the outcome is sensitive to noisy data and outliers.
+By contrast, thanks to the application of neural networks and more sophisticated combination methods, we will attempt to pursue a more robust and accurate model.
 
@@
 \section{Problem Formulation}
-There has not been much time for us to fully consider the optimal way of addressing those problems, but we do propose one possible formulation and the solution idea in this section.
+\label{sec:formulation}
+There has not been much time for us to fully consider the optimal way of addressing the problem, but we do propose one possible formulation and some solution ideas in this section.
 
@@
 Here, $I_d$ is the positive label set defined by the classifier $d$.
-Note that we can always define another classifier whose positive label set is exactly the negative label set of the classifier $d$.
+Note that we can always define a compliment classifier whose positive label set is exactly the negative label set of the classifier $d$.
 
@@
 These are factors we will consider in the later development and we are open for other suggestions.
+
+Beside these factors, there are other implementation issues about the solution to the problem.
+We have considered a given search space for small models, where the performance and functionality of each model is known as a prior.
+This allows us to concentrate on the search part of the solution.
+Nevertheless, we do not have such a prior in practice.
+Instead, we need to determine the next small model to be explored during the search, which we could potentially formulate as a local search problem.
 

### 2019-12-10 proposal/proposal.tex
update related work

--- 2019-12-09 proposal/proposal.tex
@@
 \section{Related Work}
+\paragraph{\textbf{Ensemble method}} 
+Ensemble method solves the learning problem by combining several learners.
+A few researchers have addressed the issue of combining a set of simple classifier. 
+Beriman\cite{BreimanBagging} proposed a method for generating multiple versions of a predictor by making bootstrap replicates of the learning set. 
+However, this method actually increased the amount of computation since it trained the learned repeatedly.
+Schapire\cite{Schapire1989The} proposed the boosting method to converting a weak learning algorithm into one that achieves arbitrarily high accuracy by combining a set of weak learners.
+This method was developed by Freund et al.\cite{Freund1995A}, who proposed an adaptive version of the boost.
+Subsequent weak learners are tweaked in favor of those instances misclassified by previous classifiers. 
+Friedman et al.\cite{FriedmanGreedy} proposed a new method called gradient boosting. 
+It performed additive optimization in functional space, which compensated for the weakness of weak classifiers in the light of the gradient of their loss function.
 
@@
 % \bibliographystyle{acm}
-% \bibliographystyle{unsrt}
+\bibliographystyle{unsrt}
 \bibliography{../full_list.bib}

### 2019-12-10 proposal/proposal.tex
Update proposal.tex

@@
 We will take the image recognition (classification) task as the example throughout the project.
-At present, AdaBoost tends to be one possible solution.
+At present, Boosting\cite{Schapire1989The} tends to be one possible solution.
 However, the weaker learners in these algorithm, which may be very simple classifiers, are so susceptible that the outcome is sensitive to noisy data and outliers.
@@
 However, this method actually increased the amount of computation since it trained the learned repeatedly.
-Schapire\cite{Schapire1989The} proposed the boosting method to converting a weak learning algorithm into one that achieves arbitrarily high accuracy by combining a set of weak learners.
+Schapire\cite{Schapire1989The} proposed the boosting method to converting a weak learning algorithm into one that achieved arbitrarily high accuracy by combining a set of weak learners.
 This method was developed by Freund et al.\cite{Freund1995A}, who proposed an adaptive version of the boost.
-Subsequent weak learners are tweaked in favor of those instances misclassified by previous classifiers. 
+Subsequent weak learners were tweaked in favor of those instances misclassified by previous classifiers. 
 Friedman et al.\cite{FriedmanGreedy} proposed a new method called gradient boosting. 

### 2019-12-10 proposal/proposal.tex
embedding related work

--- 2019-12-10 proposal/proposal.tex
@@
 
+\author{Zhongye Wang}
+\authornote{Student Number: 517030910353, Parallel Authorship}
+% \authornote{Supervised by Qinxiang Cao, Shanghai Jiao Tong University, John Hopcroft Center for Computer Science.}          %% \authornote is optional;
+%% can be repeated if necessary
+%\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
+\affiliation{
+	%\position{Position2b}
+	%\department{Department2b}             %% \department is recommended
+	\institution{Shanghai Jiao Tong University}           %% \institution is required
+	%\streetaddress{Street3b Address2b}
+	%\city{City2b}
+	%\state{State2b}
+	%\postcode{Post-Code2b}
+	%\country{Country2b}                   %% \country is recommended
+}
+% \email{wangzhongye1110@sjtu.edu.cn}          %% \email is recommended
+
 \author{Yichen Xie}
+\authornote{Student Number: 517030910355, Parallel Authorship}
 % \authornote{Supervised by Qinxiang Cao, Shanghai Jiao Tong University, John Hopcroft Center for Computer Science.}          %% \authornote is optional;
@@
 
-\author{Zhongye Wang}
-% \authornote{Supervised by Qinxiang Cao, Shanghai Jiao Tong University, John Hopcroft Center for Computer Science.}          %% \authornote is optional;
-%% can be repeated if necessary
-%\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
-\affiliation{
-	%\position{Position2b}
-	%\department{Department2b}             %% \department is recommended
-	\institution{Shanghai Jiao Tong University}           %% \institution is required
-	%\streetaddress{Street3b Address2b}
-	%\city{City2b}
-	%\state{State2b}
-	%\postcode{Post-Code2b}
-	%\country{Country2b}                   %% \country is recommended
-}
-\email{wangzhongye1110@sjtu.edu.cn}          %% \email is recommended
-
 \author{Xinyu Zhan}
+\authornote{Student Number: 517030910358, Parallel Authorship}
 % \authornote{Supervised by Qinxiang Cao, Shanghai Jiao Tong University, John Hopcroft Center for Computer Science.}          %% \authornote is optional;
@@
 \section{Related Work}
-\paragraph{\textbf{Ensemble method}} 
-Ensemble method solves the learning problem by combining several learners.
-A few researchers have addressed the issue of combining a set of simple classifier. 
-Beriman\cite{BreimanBagging} proposed a method for generating multiple versions of a predictor by making bootstrap replicates of the learning set. 
-However, this method actually increased the amount of computation since it trained the learned repeatedly.
-Schapire\cite{Schapire1989The} proposed the boosting method to converting a weak learning algorithm into one that achieves arbitrarily high accuracy by combining a set of weak learners.
-This method was developed by Freund et al.\cite{Freund1995A}, who proposed an adaptive version of the boost.
-Subsequent weak learners are tweaked in favor of those instances misclassified by previous classifiers. 
-Friedman et al.\cite{FriedmanGreedy} proposed a new method called gradient boosting. 
-It performed additive optimization in functional space, which compensated for the weakness of weak classifiers in the light of the gradient of their loss function.
+% embedding
+As mentioned before, our approach resembles the embedding method, which is a common practice to address the curse of dimensionality, where we map data points into a subspace with reduced dimensionality and carry out the task in this space \cite{2016ml}.
+This can be accomplished with Multiple Dimension Scaling (MDS) \cite{cox2000multidimensional} or implicitly train an embedding in the hidden layers of a neural network.
+However, we explicitly search for an embedding by searching the optimal discriminator set, where each discriminator simulates one component in the embedding and we could directly obtain the category of some samples.
+It is also possible to consider more complex way of classifying using the embedding like adding another layer of network to perform the classification step, but we will stick to the current setting in the early stages of the development.
 
@@
 % \bibliographystyle{acm}
-\bibliographystyle{unsrt}
+% \bibliographystyle{unsrt}
 \bibliography{../full_list.bib}

### 2019-12-10 proposal/proposal.tex

@@
 
+% ensemble
+A similar method that uses several weak learners to accomplish tasks is the ensemble method, which has been explored by many researchers. 
+Beriman\cite{BreimanBagging} proposed a method for generating multiple versions of a predictor by making bootstrap replicates of the learning set. 
+However, this method actually increased the amount of computation since it trained the learned repeatedly.
+Schapire\cite{Schapire1989The} proposed the boosting method to converting a weak learning algorithm into one that achieved arbitrarily high accuracy by combining a set of weak learners.
+This method was developed by Freund \textit{et al.}\cite{Freund1995A}, who proposed an adaptive version of the boost.
+Subsequent weak learners were tweaked in favor of those instances misclassified by previous classifiers. 
+Friedman \textit{et al.}\cite{FriedmanGreedy} proposed a new method called gradient boosting. 
+It performed additive optimization in functional space, which compensated for the weakness of weak classifiers in the light of the gradient of their loss function.
+
 %% Acknowledgments

### 2019-12-10 proposal/proposal.tex
some update of proposal

@@
 We will take the image recognition (classification) task as the example throughout the project.
-At present, Boosting\cite{Schapire1989The} tends to be one possible solution.
+At present, boosting\cite{Schapire1989The} tends to be one possible solution.
 However, the weaker learners in these algorithm, which may be very simple classifiers, are so susceptible that the outcome is sensitive to noisy data and outliers.
@@
 
-There are further constraints and considerations of the optimal set of classifiers $D^*$.
+There are further constraints and considerations of the optimal discriminator set $D^*$.
 \begin{itemize}
@@
 Nevertheless, we do not have such a prior in practice.
-Instead, we need to determine the next small model to be explored during the search, which we could potentially formulate as a local search problem.
+Instead, we need to determine the next small model to be explored during the search, which we could formulate as a local search problem.
 
@@
 It performed additive optimization in functional space, which compensated for the weakness of weak classifiers in the light of the gradient of their loss function.
+We will consider to include their ideas to ensemble models in our discriminator set.
 

### 2019-12-22 proposal/proposal.tex
update proposal

--- 2019-12-10 proposal/proposal.tex
@@
 %% Title information
-\title[]{CS222 Project Proposal}         %% [Short Title] is optional;
+\title[Task-Specific Network Fusion through CDRP Model Decomposition and Assembly]{CS222 Project Proposal: Task-Specific Network Fusion through CDRP Model Decomposition and Assembly}         %% [Short Title] is optional;
 %% when present, will be used in
@@
 \author{Zhongye Wang}
-\authornote{Student Number: 517030910353, Parallel Authorship}
+% \authornote{Student Number: 517030910353, Parallel Authorship}
 % \authornote{Supervised by Qinxiang Cao, Shanghai Jiao Tong University, John Hopcroft Center for Computer Science.}          %% \authornote is optional;
@@
 	%\department{Department2b}             %% \department is recommended
-	\institution{Shanghai Jiao Tong University}           %% \institution is required
+	\institution{Shanghai Jiao Tong University, 517030910353}           %% \institution is required
 	%\streetaddress{Street3b Address2b}
@@
 \author{Yichen Xie}
-\authornote{Student Number: 517030910355, Parallel Authorship}
+% \authornote{Student Number: 517030910355, Parallel Authorship}
 % \authornote{Supervised by Qinxiang Cao, Shanghai Jiao Tong University, John Hopcroft Center for Computer Science.}          %% \authornote is optional;
@@
 	%\department{Department2b}             %% \department is recommended
-	\institution{Shanghai Jiao Tong University}           %% \institution is required
+	\institution{Shanghai Jiao Tong University, 517030910355}           %% \institution is required
 	%\streetaddress{Street3b Address2b}
@@
 \author{Xinyu Zhan}
-\authornote{Student Number: 517030910358, Parallel Authorship}
+% \authornote{Student Number: 517030910358, Parallel Authorship}
 % \authornote{Supervised by Qinxiang Cao, Shanghai Jiao Tong University, John Hopcroft Center for Computer Science.}          %% \authornote is optional;
@@
 	%\department{Department2b}             %% \department is recommended
-	\institution{Shanghai Jiao Tong University}           %% \institution is required
+	\institution{Shanghai Jiao Tong University, 517030910358}           %% \institution is required
 	%\streetaddress{Street3b Address2b}
@@
 However, the limited energy supply and computational capability of edge devices lead to constraints on the scale and complexity of deep neural networks.
-We need light-weight models to meet these requirements of edge device.
-In this project, we will seek for a combination of light-weight neural networks to substitute the original complex model while preserving its functionality.
+The edge devices often need only to perform very specific tasks, whereas the pre-trained models deals with more general cases.
+This makes it possible for us to develop task-specific and light-weighted models to meet various constraints of edge device.
+
+Network fusion is a potential way to further improve the performance of network models with the advance of edge devices, where we could deploy many models through devices, let them perform inference in parallel, and retrieve and join the results \cite{fang2019teamnet}.
+Nevertheless, this could cause redundant complexity across models, making it unable to fully utilize the capability of each edge devices.
+
+In this project, we will seek for a decomposition and a combination of light-weight neural networks to substitute the original complex model while preserving its functionality.
+Moreover, we want to satisfy some given tasks (a subset of the original domain) with the minimum model complexity, i.e., the combination should assemble only necessary parts for the task-specific model.
 % With this new model, we will try to reduce the parameter number and computing consumption notably at the expense of acceptable accuracy decline compared to the original large model.
@@
 \section{Problem Description}
-We mainly focus on the task to replace a large deep learning model with a set of small models with reduced complexity.
-Using too many small models can still result in tremendous amount of calculation in inference and affect models' performance in edge devices, so we limit the overall complexity of models as well.
-% Then, the total computational consumption can decrease definitely.
-As a result, edge device can profit from the lowered demand for computational consumption.
-% And these small models are independent from the original deep learning network at least in the inference phase.
-% Hence, they can process the data on the edge device without communication with the cloud or servers, which extend the application range of these device.
+\label{sec:problem-desc}
+The problem of our interest can be divided into two stages: network decomposition and network assembly.
 
-There are many possible approaches in the design of small model system.
-\begin{itemize}
-  \item We could train small models each with specific tasks, which can be implemented with satisfying performance and simple network structure.
-  \item We could train small models each dealing with part of the dataset, which can be combined to handle all data points efficiently.
+We first look into the assembly task.
+Given a set of decomposed small networks, each covers the classification\footnote{We will take the image recognition (classification) task as the example throughout the project.} task of a subset of the dataset, we need to find a subset of those models for any given tasks.
+Following problems reflect the complexity of the assembly task:\begin{itemize}
+  \item There could exist overlapping functionalities among models, i.e., several models could cover the classification of the same subset of samples, in which case we want a careful selection of those produce the optimal performance.
+  \item The given task could be comparably simpler than that of the original model.
+We need to determine wether a given reduced model can satisfy the requirement and how to further reduce its complexity.
 \end{itemize}
-Our focus will be the former one, where we want each model to perform binary decisions in the context of classification and the union of these models should uniquely determine the category of any sample.
-In this way, small models serve as feature extractors that jointly produce an embedding for the data sample.
-We can also retrieve such embedding implicitly using neural networks, but we choose to achieve the optimal embedding explicitly by solving the search problem formulated in \cref{sec:formulation}.
 
-We will take the image recognition (classification) task as the example throughout the project.
-At present, AdaBoost tends to be one possible solution.
-However, the weaker learners in these algorithm, which may be very simple classifiers, are so susceptible that the outcome is sensitive to noisy data and outliers.
-By contrast, thanks to the application of neural networks and more sophisticated combination methods, we will attempt to pursue a more robust and accurate model.
+Two natural questions follows the above assembly task: how to find the initial set of decomposed small networks, and how to determine the sample subsets they cover.
+That is the network decomposition task we are interested in.
+An intuitive way to achieve such decomposition is to arrange samples into subsets according to their labels, and train separate models for each class.
+Nevertheless, this makes the assembly task trivial, because there exists no overlapping among decomposed models and the problem can be solved in linear time by incrementally selecting required classes.
+It also requires extra training, and the complexity for the resulting model could still be very large.
+It is challenging to find a fine-grained decomposition of an existing model and dataset.
+
+% We mainly focus on the task to replace a large deep learning model with a set of small models with reduced complexity.
+% Using too many small models can still result in tremendous amount of calculation in inference and affect models' performance in edge devices, so we limit the overall complexity of models as well.
+% % Then, the total computational consumption can decrease definitely.
+% As a result, edge device can profit from the lowered demand for computational consumption.
+% % And these small models are independent from the original deep learning network at least in the inference phase.
+% % Hence, they can process the data on the edge device without communication with the cloud or servers, which extend the application range of these device.
+
+% There are many possible approaches in the design of small model system.
+% \begin{itemize}
+%   \item We could train small models each with specific tasks, which can be implemented with satisfying performance and simple network structure.
+%   \item We could train small models each dealing with part of the dataset, which can be combined to handle all data points efficiently.
+% \end{itemize}
+% Our focus will be the former one, where we want each model to perform binary decisions in the context of classification and the union of these models should uniquely determine the category of any sample.
+
+% TODO: still an embedding?
+% A more high-level understanding of the problem is to consider small models as feature extractors that jointly produce an embedding for the data sample.
+% We can also retrieve such embedding implicitly using neural networks, but we choose to achieve the optimal embedding explicitly by solving the search problem formulated in \cref{sec:formulation}.
+
+% We will take the image recognition (classification) task as the example throughout the project.
+% At present, boosting\cite{Schapire1989The} tends to be one possible solution.
+% However, the weaker learners in these algorithm, which may be very simple classifiers, are so susceptible that the outcome is sensitive to noisy data and outliers.
+% By contrast, thanks to the application of neural networks and more sophisticated combination methods, we will attempt to pursue a more robust and accurate model.
 
@@
 \label{sec:formulation}
-There has not been much time for us to fully consider the optimal way of addressing the problem, but we do propose one possible formulation and some solution ideas in this section.
+% There has not been much time for us to fully consider the optimal way of addressing the problem, but we do propose one possible formulation and some solution ideas in this section.
+
+In this section, we propose the critical data routing path (CDRP) decomposition for the decomposition task and a formal formulation of the assembly task.
+
+\subsection{CDRP Models and CDRP Based Clustering}
+In the context of convolutional neural network, critical data routing path \cite{wang2018interpret} \cite{yu2018distilling} describes subsets of filters in all convolutional layers, whose activations are important to the correct classification of some samples.
+Removing them could cause significant performance drop for those samples, while preserving them only, the model still has high chance to classifies some of those samples correctly.
+
+Wang \textit{et al.} trains a set of gates to either suppress or preserve the activation of each filters for one given sample to decrease the model complexity but maintain the correctness classification of the samples.
+The preserved filters becomes the CDRP for the sample, and we get an over-fine-grained model decomposition per sample.
+Also, the CDRP can also be some feature representation of the sample under the context of the original model, i.e., similar samples sharing the similar features will have high probability of sharing the same CDRP.
+Based on this conjecture, we propose the CDRP clustering to merge decomposed models and find the corresponding covering set.
+
+After learning the gates for each sample, we encode the sample using corresponding weights $\Lambda$ assigned to each gate.
+We then cluster samples in this $Lambda$-space, and for samples in the same cluster, we might use the CDRP model of its centroid to correctly classify those samples, assuming the number of clusters is adequate.
+This is true because their CDRP models are similar to the one of the centroid since we are using this similarity to perform the clustering.
+
+We will take the rounded centroid CDRP models as the initial set of decomposed models and take corresponding clusters as the sample subset.
+
+\paragraph{Remark.}
+\label{par:side-project}
+If two samples of different class are assigned the same cluster, they will activate almost identical filters in the original model, causing it to label them as the same class.
+This gives us a potential way to analyze why the model makes mistakes in an intuitive way.
+If time allows, we might consider this as a side project.
+
+\subsection{Network Fusion of CDRP Models}
+However, the CDRP decomposition makes the assembly problem for a single CNN model trivial, because this results in the same situation of the trivial decomposition we proposed in \cref{sec:problem-desc}.
+We now have disjoint cluster of samples, where samples in the same cluster shares the same label (same arguments as the \textit{remark}~\ref{par:side-project}).
+To cover a given set of classes, we only need to cover the set of clusters belonging to those classes, i.e., a linear algorithm to incrementally include corresponding CDRP models.
+There are no feasible solutions other than the optimal one.
+
+But luckily, things become quite different for multiple networks, and the CDRP decomposition makes the fine-grained network fusion possible.
+Let us consider a very general example in Figure~\ref{fig:fusion-example}, where we want to fuse two different networks of the the same task but trained on two different dataset.
+If we only want to determine wether a sample has the orange label correctly, we have following options: $(D_2 \cap C_3) \cup (D_3 \cap C_2)$, $(D_2 \cap C_1^c) \cup (D_3 \cap C_1^c)$, $(D_1^c \cap C_3) \cup (D_1^c \cap C_2)$, where $D^c$ is the compliment classifier.
+The resulting performance could vary among different configurations.
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=0.38\linewidth]{fig/fusion_example.png}
+  \caption{Joint CDRP Decomposition and Clustering on Two Dataset:
+  We have a circle dataset and triangle dataset, where three colors represents three labels.
+  The grey boxes are clusters from model $C$ trained on the circle dataset, and the blue ones are from model $D$ trained on the triangle dataset.}
+  \label{fig:fusion-example}
+\end{figure}
+
+Such problem setting not only allow the problem to stay non-trivial, but also holds great significance in practice.
+If we perform the clustering across datasets, we allow the fused model to generalize better and become more versatile.
+Moreover, the fusion is more efficient, because we have removed many redundant feature overlapping in unit decomposed models.
+
+\subsection{Assembling CDRP Models}
+Next, we give a problem formulation that assembles the decomposed CRP models into a new model satisfying specific classification tasks.
 
@@
 
-Our task is to find a subset $D^* \subset \mathcal{D}$, such that for any class $A_i$, there exists a partition that divides it into some subclasses $S_i^{(l)}$ where $A_i = \bigcup_l \{A_{ij} \,|\, (i, j) \in S_i^{(l)}\}$, and for each subclass $S_i^{(l)}$ there exists a subset of classifiers $D^{(l)} \subseteq D^*$ where $S_i^{(l)} = \bigcap_d \{I_d \,|\, d \in D^{(l)}\}$.
+Given a target label set $\mathcal{A}$, our task is to find a subset $D^* \subset \mathcal{D}$, such that for any class $A_i \in \mathcal{A}$, there exists a partition that divides it into some subclasses $S_i^{(l)}$ where $A_i = \bigcup_l \{A_{ij} \,|\, (i, j) \in S_i^{(l)}\}$, and for each subclass $S_i^{(l)}$ there exists a subset of classifiers $D^{(l)} \subseteq D^*$ where $S_i^{(l)} = \bigcap_d \{I_d \,|\, d \in D^{(l)}\}$.
 Here, subclass $S_i^{(l)}$ represents the union of some subsets $A_{ij}$ of class $A_i$, and the union of all subclasses of $A_i$ should reconstruct the $A_i$ itself.
 The optimal set of classifiers $D^*$ should allow us to determine wether a sample belongs to any given subclass $S_i^{(l)}$ using a subset $D^{(l)}$ in it, which in turn determines wether the sample belongs to $A_i$.
-Figure~\ref{fig:feasible-example} shows a feasible classifier set $D$ in a simple example.
 
@@
     \includegraphics[width=0.45\linewidth]{fig/formulation_example.png}
-    \caption{An Example of Feasible Classifier Set:
+    \caption{An Example Problem Setting:
     The samples in class $A_1$ is further divided into $A_{11}, A_{12}$ and those in class $A_2$ is further divided into $A_{21}, A_{22}, A_{23}$.
     We do not divide $A_3$ but rename it to $A_{31}$.
-    There are 4 discriminators $d_1, d_2, d_3, d_4$ respectively identify $\{A_{11}, A_{12}, A_{21}, A_{22}\}$, $\{A_{21}, A_{31}\}$, $\{A_{22}, A_{23}\}$, and $\{A_{23}, A_{31}\}$.
-    We have: \textit{(a)} the intersection of $d_1$ and the compliments of $d_2, d_3$ identifies $A_1 = A_{11} \cup A_{12}$;
-    \textit{(b)} the intersection of $d_1$ and $d_2$ identifies $A_{21}$, and its union with $d_3$ determines the entire $A_2$;
-    \textit{(c)} the intersection of $d_3$ and the compliment of $d_1$ determines $A_3 = A_{31}$.
-    Clearly, $D = \{d_1, d_2, d_3\}$ is a feasible set, where the redundant classifier $d_4$ is not selected.}
+    There are 4 discriminators $d_1, d_2, d_3, d_4$ respectively identify $\{A_{11}, A_{12}, A_{21}, A_{22}\}$, $\{A_{21}, A_{31}\}$, $\{A_{22}, A_{23}\}$, and $\{A_{22}, A_{31}\}$.}
     \label{fig:feasible-example}
@@
 
-There are further constraints and considerations of the optimal set of classifiers $D^*$.
+Figure~\ref{fig:feasible-example} shows an example problem setting, and we give solutions to the following two instances of the problem:
+\begin{itemize}
+  \item \textbf{$\mathcal{A} = \{A_1, A_2, A_3\}$:}
+  A feasible solution is $D = \{d_1, d_2, d_3\}$, which covers all classes because: \begin{enumerate}
+    \item[\textit{(a)}] the intersection of $d_2, d_3$'s compliments identifies $A_1 = A_{11} \cup A_{12}$;
+    \item[\textit{(b)}] the intersection of $d_1$ and $d_2$ identifies $A_{21}$, and its union with $d_3$ determines the entire $A_2$;
+    \item[\textit{(c)}] the intersection of $d_3$ and the compliment of $d_1$ determines $A_3 = A_{31}$.
+  \end{enumerate}
+  \item \textbf{$\mathcal{A} = \{A_3\}$:}
+  A feasible solution is $D = \{d_2, d_4\}$ because \begin{enumerate}
+    \item[\textit{(a)}] the intersection of $d_2$ and $d_4$ uniquely identifies $A_{31} = A_3$;
+    \item[\textit{(b)}] we do not need to include other discriminators to distinguish between $A_1$ and $A_2$, as long as it classifies them as \textit{not $A_3$}.
+  \end{enumerate}
+\end{itemize}
+
+There are further constraints and considerations of the optimal discriminator set $D^*$.
 \begin{itemize}
@@
 
-Beside these factors, there are other implementation issues about the solution to the problem.
-We have considered a given search space for small models, where the performance and functionality of each model is known as a prior.
-This allows us to concentrate on the search part of the solution.
-Nevertheless, we do not have such a prior in practice.
-Instead, we need to determine the next small model to be explored during the search, which we could potentially formulate as a local search problem.
+% Beside these factors, there are other implementation issues about the solution to the problem.
+% We have considered a given search space for small models, where the performance and functionality of each model is known as a prior.
+% This allows us to concentrate on the search part of the solution.
+% Nevertheless, we do not have such a prior in practice.
+% Instead, we need to determine the next small model to be explored during the search, which we could formulate as a local search problem.
 
@@
 \section{Related Work}
+There have been other similar works trying to understand and prune the complexity of the CNN.
+Zhou \textit{et al.} \cite{zhou2018interpreting} \cite{zhou2018revisiting} seek to understand the influence of certain filters on the accuracy wrt.
+some specific classes of samples by ablation and dissection.
+Their work provides certain explanations of the outcome, but they do not explain how their technique can be utilize to improve or compress the model and it is only useful for network interpretation.
+Yu \textit{et al.} \cite{yu2018distilling} attempt to produce task-specific models with reduced complexity through critical path distillation.
+They identify critical paths through activation visualization for specific classes, which is more efficient than training gates to find them in our work.
+But this means their critical path models are at the class level and these models can not interact with other external models through network fusion.
+
+Qin \textit{et al.} propose the CAPTOR \cite{qin2019captor}, a framework for filter pruning also through clustering.
+Different from our clustering method, they perform the clustering on filters with similar activation maximization visualization and prune similar filters to remove redundances.
+We could also use this technique to remove redundances within a CDRP model.
+Their pruning is again performed at the class level, while ours assembly is performed at the feature level, which is more fine-grained.
+
+On the topic of network fusion, there are also many marvelous researches.
+Du \textit{et al.} \cite{du2017fused} use multiple DNNs to refine the detections of a pedestrian detection generator and fuse these DNNs by fusing their outputs.
+This type of output level fusion is coarse-grained, where redundant feature extractions may have occurred in DNNs.
+On the opposite, Feichtenhofer\cite{feichtenhofer2016convolutional} proposed an extremely fine-grained fusion of multiple CNNs for video action recognition, where they carry out spatial fusion and temporal fusion on the layer level and achieves state-of-the-art results.
+However, there are common problems of both work.
+Their framework are task-specific and is difficult to apply their techniques in other domains.
+And their works do not aim to reduce the network complexity during the fusion process.
+
 % embedding
-As mentioned before, our approach resembles the embedding method, which is a common practice to address the curse of dimensionality, where we map data points into a subspace with reduced dimensionality and carry out the task in this space \cite{2016ml}.
-This can be accomplished with Multiple Dimension Scaling (MDS) \cite{cox2000multidimensional} or implicitly train an embedding in the hidden layers of a neural network.
-However, we explicitly search for an embedding by searching the optimal discriminator set, where each discriminator simulates one component in the embedding and we could directly obtain the category of some samples.
-It is also possible to consider more complex way of classifying using the embedding like adding another layer of network to perform the classification step, but we will stick to the current setting in the early stages of the development.
+% As mentioned before, our approach resembles the embedding method, which is a common practice to address the curse of dimensionality, where we map data points into a subspace with reduced dimensionality and carry out the task in this space \cite{2016ml}.
+% This can be accomplished with Multiple Dimension Scaling (MDS) \cite{cox2000multidimensional} or implicitly train an embedding in the hidden layers of a neural network.
+% However, we explicitly search for an embedding by searching the optimal discriminator set, where each discriminator simulates one component in the embedding and we could directly obtain the category of some samples.
+% It is also possible to consider more complex way of classifying using the embedding like adding another layer of network to perform the classification step, but we will stick to the current setting in the early stages of the development.
+
+% ensemble
+% A similar method that uses several weak learners to accomplish tasks is the ensemble method, which has been explored by many researchers. 
+% Beriman\cite{BreimanBagging} proposed a method for generating multiple versions of a predictor by making bootstrap replicates of the learning set. 
+% However, this method actually increased the amount of computation since it trained the learned repeatedly.
+% Schapire\cite{Schapire1989The} proposed the boosting method to converting a weak learning algorithm into one that achieved arbitrarily high accuracy by combining a set of weak learners.
+% This method was developed by Freund \textit{et al.}\cite{Freund1995A}, who proposed an adaptive version of the boost.
+% Subsequent weak learners were tweaked in favor of those instances misclassified by previous classifiers. 
+% Friedman \textit{et al.}\cite{FriedmanGreedy} proposed a new method called gradient boosting. 
+% It performed additive optimization in functional space, which compensated for the weakness of weak classifiers in the light of the gradient of their loss function.
+% We will consider to include their ideas to ensemble models in our discriminator set.
 

### 2019-12-23 code/CriticalPathPruning/CIFAR_DataLoader.py
critical path pruning

@@ -1,0 +1,123 @@
+# -*- coding: utf-8 -*-
+import tensorflow as tf
+import numpy as np
+import matplotlib.pyplot as plt
+import os
+import keras
+import _pickle as cPickle
+
+# =============== Define Data Loader ===============
+''' Utility Functions '''
+DATA_PATH = "cifar-100-python"
+
+def unpickle(file):
+    with open(os.path.join(DATA_PATH, file), 'rb') as fo:
+        dict = cPickle.load(fo, encoding='latin1')
+        return dict
+
+def one_hot(vec, vals=10):
+    n = len(vec)
+    out = np.zeros((n, vals))
+    out[range(n), vec] = 1
+    return out
+
+class CifarLoader(object):
+    def __init__(self, sourcefiles):
+        self._source = sourcefiles
+        self._i = 0
+
+        self.images = None
+        self.labels = None
+
+    def load(self):
+        data = [unpickle(f) for f in self._source]
+        images = np.vstack(d["data"] for d in data)
+
+        n = len(images)
+        self.images = images.reshape(n, 3, 32, 32).transpose(0, 2, 3, 1).astype(float)
+        # self.labels = one_hot(np.hstack([d["fine_labels"] for d in data]), 100)
+        self.labels = np.hstack([d["fine_labels"] for d in data])
+        self.images = self.normalize_images(self.images)
+        return self
+
+    def next_batch(self, batch_size):
+        x, y = self.images[self._i:self._i+batch_size], self.labels[self._i:self._i+batch_size]
+        self._i = (self._i + batch_size) % len(self.images)
+        return x, one_hot(y, 100) 
+    
+    def next_batch_without_onehot(self, batch_size):
+        x, y = self.images[self._i:self._i+batch_size], self.labels[self._i:self._i+batch_size]
+        self._i = (self._i + batch_size) % len(self.images)
+        return x, y
+
+    def generateSpecializedData(self, class_id, count = 500):
+        train_index = []
+
+        index = list(np.where(self.labels[:] == class_id)[0])[0:count]
+        train_index += index
+
+        sp_x = self.images[train_index]
+        sp_y = self.labels[train_index]
+        sp_y = one_hot(sp_y, 100)
+
+        sp_y = sp_y.astype('float32')
+        sp_x = sp_x.astype('float32')
+        return sp_x, sp_y
+    
+    def generateAllData(self):
+        return self.images, one_hot(self.labels, 100)
+
[…]

### 2019-12-23 code/CriticalPathPruning/CalTech_DataLoader.py

@@ -1,0 +1,128 @@
+import os
+import sys
+import random
+import numpy as np
+from PIL import Image
+import matplotlib.pyplot as plt
+import matplotlib.image as mpimg
+
+PATH = "./CalTech256/256_ObjectCategories"
+PATH_Resized = "./CalTech256/ResizedImages"
+
+'''
+TODO:
+    - Shuffle all images to target directory
+    - Record Corresponding Labels 
+    - Resize Images
+    - Generate Train Dataset and Test Dataset
+'''
+
+def one_hot(vec, vals=10):
+    n = len(vec)
+    out = np.zeros((n, vals))
+    out[range(n), vec] = 1
+    return out
+
+class CalTechLoader(object):
+    def __init__(self, sourceDirs):
+        self.images = None
+        self.labels = None
+
+        self._i = 0
+        self.imgDirs = sourceDirs
+    
+    def load(self):
+        imageList = []
+        labelList = []
+        for imgDir in self.imgDirs:
+            tmpImage = plt.imread(os.path.join(PATH_Resized, imgDir))
+            tmpLabel = imgDir.strip(".jpg")
+            _, tmpLabel = tmpLabel.split("_")
+            tmpLabel = int(tmpLabel)
+            if tmpImage.shape == (32, 32):
+                continue
+            imageList.append(tmpImage)
+            labelList.append(tmpLabel)
+
+        self.images = np.array(imageList).astype(float)
+        self.labels = np.array(labelList)
+        self.length = len(self.labels)
+
+        self.images = self.normalize_images(self.images)
+        
+        return self
+
+    def next_batch(self, batch_size):
+        x, y = self.images[self._i:self._i+batch_size], self.labels[self._i:self._i+batch_size]
+        self._i = (self._i + batch_size) % len(self.images)
+        return x, one_hot(y, 256) 
+
+    def next_batch_without_onehot(self, batch_size):
+        x, y = self.images[self._i:self._i+batch_size], self.labels[self._i:self._i+batch_size]
+        self._i = (self._i + batch_size) % len(self.images)
+        return x, y
+
+    # calculate the means and stds for the whole dataset per channel
+    def measure_mean_and_std(self, images):
+        means = []
+        stds = []
+        for ch in range(images.shape[-1]):
+            means.append(np.mean(images[:, :, :, ch]))
+            stds.append(np.std(images[:, :, :, ch]))
+        return means, stds
+
+    # normalization for per channel
+    def normalize_images(self, images):
[…]

### 2019-12-23 code/CriticalPathPruning/run.py

@@ -1,0 +1,123 @@
+import numpy as np
+import json
+from CIFAR_DataLoader import CifarDataManager, display_cifar
+from vggNet import Model
+
+'''
+Configuration:
+    1. learning rate 
+    2. L1 loss penalty
+    3. Lambda cotrol gate threshold
+'''
+learning_rate = 0.1
+L1_loss_penalty = 0.03
+threshold = 0.0
+''''''
+
+layer_names = ['FC14/gate:0', 
+    'Conv7/composite_function/gate:0', 
+    'Conv12/composite_function/gate:0', 
+    'Conv2/composite_function/gate:0', 
+    'Conv4/composite_function/gate:0', 
+    'Conv1/composite_function/gate:0', 
+    'Conv6/composite_function/gate:0', 
+    'Conv10/composite_function/gate:0', 
+    'Conv9/composite_function/gate:0', 
+    'FC15/gate:0', 
+    'Conv13/composite_function/gate:0', 
+    'Conv5/composite_function/gate:0', 
+    'Conv3/composite_function/gate:0', 
+    'Conv11/composite_function/gate:0', 
+    'Conv8/composite_function/gate:0'
+]
+
+
+def calculate_total_by_threshold(classid):
+	name_shape_match = [
+		{'name': 'FC14/gate:0', 'shape': 4096}, 
+		{'name': 'Conv7/composite_function/gate:0', 'shape': 256}, 
+		{'name': 'Conv12/composite_function/gate:0', 'shape': 512}, 
+		{'name': 'Conv2/composite_function/gate:0', 'shape': 64}, 
+		{'name': 'Conv4/composite_function/gate:0', 'shape': 128}, 
+		{'name': 'Conv1/composite_function/gate:0', 'shape': 64}, 
+		{'name': 'Conv6/composite_function/gate:0', 'shape': 256}, 
+		{'name': 'Conv10/composite_function/gate:0', 'shape': 512}, 
+		{'name': 'Conv9/composite_function/gate:0', 'shape': 512}, 
+		{'name': 'FC15/gate:0', 'shape': 4096}, 
+		{'name': 'Conv13/composite_function/gate:0', 'shape': 512}, 
+		{'name': 'Conv5/composite_function/gate:0', 'shape': 256}, 
+		{'name': 'Conv3/composite_function/gate:0', 'shape': 128}, 
+		{'name': 'Conv11/composite_function/gate:0', 'shape': 512}, 
+		{'name': 'Conv8/composite_function/gate:0', 'shape': 512}
+	]
[…]

### 2019-12-23 code/CriticalPathPruning/run_finetune.py

@@ -1,0 +1,41 @@
+from vggFinetuneModel import FineTuneModel
+from CIFAR_DataLoader import CifarDataManager
+import numpy as np
+
+'''
+For fine tune model, the data label should be different:
+    if the fine tune trimmed model if for classify label:[0]
+    the fine tune model data labels would be of 2
+    Thus, in this case, we need to change the label correspongdingly then go to train 
+'''
+def one_hot(vec, vals=10):
+    n = len(vec)
+    out = np.zeros((n, vals))
+    out[range(n), vec] = 1
+    return out
+
+def modify_label(labels, test_classes = [0]):
+    test_classes.sort()
+    tmp_labels = []
+    for i in labels:
+        if i in test_classes:
+            tmp_labels.append(test_classes.index(i))
+        else:
+            tmp_labels.append(len(test_classes))
+    return one_hot(tmp_labels, vals=len(test_classes)+1)
+
+data_loader = CifarDataManager()
+
+test_images, test_labels = data_loader.test.next_batch_without_onehot(500)
+
+test_labels = modify_label(test_labels, test_classes = [0, 1, 2, 3, 4, 5, 6, 7, 8, 9])
+
+model = FineTuneModel(target_class_id=[0, 1, 2, 3, 4, 5, 6, 7, 8, 9])
+model.assign_weight()
+model.test_accuracy(test_images, test_labels)
+
+for i in range(10):
+    train_images, train_labels = data_loader.train.next_batch_without_onehot(200)
+    train_labels = modify_label(train_labels, test_classes = [0, 1, 2, 3, 4, 5, 6, 7, 8, 9])
+    model.train_model(train_images, train_labels)
+    model.test_accuracy(test_images, test_labels)

### 2019-12-23 code/CriticalPathPruning/run_incremental_train.py

@@ -1,0 +1,39 @@
+from CalTech_DataLoader import CalTechDataManager, one_hot
+from vggFinetuneModel import FineTuneModel
+import numpy as np
+
+def modify_label(labels, test_classes = [0]):
+    test_classes.sort()
+    tmp_labels = []
+    for i in labels:
+        if i in test_classes:
+            tmp_labels.append(test_classes.index(i))
+        else:
+            tmp_labels.append(len(test_classes))
+    return one_hot(tmp_labels, vals=len(test_classes)+1)
+
+data_loader = CalTechDataManager()
+
+test_images, test_labels = data_loader.test.next_batch_without_onehot(500)
+
+'''
+Here you need to designate the test_classes in Caltech256
+'''
+test_labels = modify_label(test_labels, test_classes = [24])
+
+'''
+Here you need to designate the test_classes in Cifar100
+'''
+model = FineTuneModel(target_class_id=[14])
+model.assign_weight()
+model.test_accuracy(test_images, test_labels)
+
+for i in range(10):
+    train_images, train_labels = data_loader.train.next_batch_without_onehot(200)
+    '''
+    Here you need to designate the test_classes in Caltech256
+    '''
+    train_labels = modify_label(train_labels, test_classes = [24])
+    model.train_model(train_images, train_labels)
+    model.test_accuracy(test_images, test_labels)
+

### 2019-12-23 code/CriticalPathPruning/trim_and_test.py

@@ -1,0 +1,25 @@
+from vggTrimmedModel import TrimmedModel
+from CIFAR_DataLoader import CifarDataManager
+import numpy as np
+d = CifarDataManager()
+
+
+model = TrimmedModel(target_class_id= np.random.randint(100,size=10),
+                     multiPruning=True)
+
+'''
+Todo List: 
+    1. Modify the accuracy in trimmed network (Done)
+'''
+for _ in range(50):
+    test_images, test_labels = d.test.next_batch(200)
+
+    model.test_accuracy_pretrim(test_images, test_labels)
+
+    model.assign_weight()
+    model.test_accuracy(test_images, test_labels)
+    break
+
+
+
+

### 2019-12-23 code/CriticalPathPruning/vggFinetuneModel.py

@@ -1,0 +1,477 @@
+import pickle
+import random
+# from decimal import *
+import json
+import keras
+import numpy as np
+import tensorflow as tf
+from sklearn.utils import shuffle
+import os
+os.environ["CUDA_VISIBLE_DEVICES"] = "1"
+class FineTuneModel():
+    '''
+    Fine Tune Model: (Basically doing transfer learning)
+        1. Last FC layer neurons number would be the target class number + 1
+        2. Need to transform the original label to targeted class label
+    '''
+    def __init__(self, target_class_id=[0]):
+        '''
+        Set hyperparameters
+        '''
+        self.learning_rate = 0.01
+        self.epoch = 0
+        self.prune_ratio = 0.9
+
+        '''
+        For one input image :
+            1. Store all the gates infomation
+            2. Store all the gates values 
+        '''
+        self.AllGateVariables = dict()
+        self.AllGateVariableValues = list()
+
+        self.target_class_id = target_class_id # assign the trim class id 
+        self.target_number = len(target_class_id) + 1
+
+        self.graph = tf.Graph()
+        self.build_model(self.graph)
+        print("restored the pretrained model......")
+        self.restore_model(self.graph)
+
+    '''
+    Test Accuracy
+    '''
+    def test_accuracy(self, test_images, test_labels):
+        accuracy = self.sess.run(
+            self.accuracy, feed_dict={
+            self.xs: test_images,
+            self.ys_orig: test_labels, 
+            self.lr : 0.1,
+            self.is_training: False,
+            self.keep_prob: 1.0
+        }) 
+
+        print("Test Accuracy:" + str(accuracy))
+
+    '''
+    Fine tune training
+    '''
+    def train_model(self, input_images, input_labels):
+        if self.epoch == 5: self.learning_rate /= 10
+        if self.epoch == 50: self.learning_rate /= 10
+        if self.epoch == 100: self.learning_rate /= 10
+        self.sess.run(self.train_step, feed_dict = {
+                self.xs: input_images,
+                self.ys_orig : input_labels, 
+                self.lr : self.learning_rate, 
+                self.keep_prob : 1.0, 
+                self.is_training : False
+            })
+        self.epoch += 1
+
+    '''
+    Restore the original network weights
+    '''
+    def restore_model(self, graph):
+        savedVariable = {}
+
+        # If GPU is needed
+        config = tf.ConfigProto()
+        config.gpu_options.allow_growth = True
[…]

### 2019-12-23 code/CriticalPathPruning/vggNet.py

@@ -1,0 +1,400 @@
+import pickle
+import random
+# from decimal import *
+import json
+import keras
+import numpy as np
+import tensorflow as tf
+from sklearn.utils import shuffle
+import os
+os.environ["CUDA_VISIBLE_DEVICES"] = "5,6,7"
+
+# ================== VGG Network Model with Control Gates ==================
+class Model():
+    def __init__(self, learning_rate = 0.1, L1_loss_penalty = 0.02, threshold = 0.1):
+        '''
+        For one input image :
+            1. Store all the gates infomation
+            2. Store all the gates values 
+        '''
+        self.AllGateVariables = dict()
+        self.AllGateVariableValues = list()
+
+        '''
+        For encode images super parameters:
+            1. learning rate
+            2. L1 penalty
+            3. Lambda control gate threshold
+        '''
+        self.learning_rate = learning_rate
+        self.L1_loss_penalty = L1_loss_penalty
+        self.threshold = threshold
+
+    '''
+    Wrap Functions:
+        1. model.build_model()
+        2. model.restore_model()
+        3. model.encode_input()
+    '''
+    def compute_encoding(self, data_input):
+        self.AllGateVariableValues.clear()
+        self.AllGateVariables.clear()
+
+        graph = tf.Graph()
+        self.build_model(graph, 100)
+        self.restore_model(graph)
+        generatedGates = self.encode_input(data_input)
+        self.close_sess()
+
+        return generatedGates
+
+    '''
+    Encode and save for a batch of data
+    '''
+    def encode_class_data(self, class_id , train_images):
+        # filename = "./innerclass/class"+str(class_id)+"gate.json"
+        for i in range(len(train_images)):
+            generatedGate = self.compute_encoding(train_images[i].reshape((1,32,32,3))) # generatedGate is a list of dicts{layername:xx, shape:xx, lambda:xx}
+            picname = "class" + str(class_id) + "-pic" + str(i)
+            jsonpath = "./ImageEncoding/" + picname + ".json"
+            with open(jsonpath,'w') as f:
+                json.dump(generatedGate,f, sort_keys=True, indent=4, separators=(',', ':'))
+
+    '''
+    Restore the original network weights
+    '''
+    def restore_model(self, graph):
+        savedVariable = {}
+
+        # If GPU is needed
+        config = tf.ConfigProto()
+        config.gpu_options.allow_growth = True
+        self.sess = tf.Session(graph = graph, config = config)
[…]

### 2019-12-23 code/CriticalPathPruning/vggTrimmedModel.py

@@ -1,0 +1,464 @@
+# from decimal import *
+import json
+import os
+import pickle
+import random
+import time
+
+import keras
+import numpy as np
+import tensorflow as tf
+from sklearn.utils import shuffle
+
+os.environ["CUDA_VISIBLE_DEVICES"] = "1"
+class TrimmedModel():
+    '''
+    This class does:
+        1. Load original model graph
+        2. Assign new weights to layers 
+        3. Test Accuracy
+    '''
+    def __init__(self,target_class_id=[0], multiPruning=False):
+        self.prune_ratio = 0.9
+
+        self.graph = tf.Graph()
+        self.build_model(self.graph)
+        print("restored the pretrained model......")
+        self.restore_model(self.graph)
+        
+        self.target_class_id = target_class_id # assign the trim class id 
+        self.multiPruning = multiPruning # ready to prune for one single class or multi classes
+        # self.close_sess()
+    
+    '''
+    Find mask class unit
+    '''
+    def mask_class_unit(self, classid):
+        self.test_counter = 0
+        theshold = 10
+        json_path = "./ClassEncoding/class" + str(classid) + ".json"
+        with open(json_path, "r") as f:
+            gatesValueDict = json.load(f)
+            for idx in range(len(gatesValueDict)):
+                layer = gatesValueDict[idx]
+                name = layer["name"]
+                vec = layer["shape"]
+                # process name
+                name = name.split('/')[0]
+                # process vec
+                for i in range(len(vec)):
+                    if vec[i] < 10:
+                        vec[i] = 0
+                    else:
+                        vec[i] = 1
+                layer["name"] = name
+                layer["shape"] = vec
+
+            return gatesValueDict
+
+    '''
+    mask by value
+    '''
+    def mask_unit_by_value(self, classid):
+        formulizedDict = {}
+        json_path = "./ClassEncoding/class" + str(classid) + ".json"
+        
+        allGatesValue = []
+
+        with open(json_path, "r") as f:
+            gatesValueDict = json.load(f)
+            for idx in range(len(gatesValueDict)):
+                layer = gatesValueDict[idx]
+                name = layer["name"]
+                vec = layer["shape"]
+                allGatesValue += vec
+                
+        allGatesValue.sort()
+        allGatesValue = allGatesValue[:int(len(allGatesValue)*0.8)]
+        
+        allGatesValue = set(allGatesValue)
+        with open(json_path, "r") as f:
[…]

### 2019-12-24 code/CriticalPathPruning/run.py
minor CDRP code update

@@ -32,7 +32,7 @@ layer_names = ['FC14/gate:0',
 ]
 
 
-def calculate_total_by_threshold(classid):
+def calculate_total_by_threshold(classid, size=500):
 	name_shape_match = [
 		{'name': 'FC14/gate:0', 'shape': 4096}, 
 		{'name': 'Conv7/composite_function/gate:0', 'shape': 256}, 
@@ -52,7 +52,7 @@ def calculate_total_by_threshold(classid):
 	]
 	for i in range(len(name_shape_match)):
 		name_shape_match[i]['shape'] = name_shape_match[i]['shape']*[0]
-	for i in range(499):
+	for i in range(size):
 		jsonpath = "./ImageEncoding/class" + str(classid) + "-pic" + str(i) + ".json"
 		with open(jsonpath,'r') as f:
 			dataset = json.load(f)
@@ -71,7 +71,7 @@ def calculate_total_by_threshold(classid):
 	with open(json_write_path,'w') as g:
 		json.dump(name_shape_match,g,sort_keys=True, indent=4, separators=(',', ':'))
 
-def calculate_total_by_weights(classid):
+def calculate_total_by_weights(classid, size=500):
 	name_shape_match = [
 		{'name': 'FC14/gate:0', 'shape': 4096}, 
 		{'name': 'Conv7/composite_function/gate:0', 'shape': 256}, 
@@ -91,7 +91,7 @@ def calculate_total_by_weights(classid):
 	]
 	for i in range(len(name_shape_match)):
 		name_shape_match[i]['shape'] = name_shape_match[i]['shape']*[0]
-	for i in range(499):
+	for i in range(size):
 		jsonpath = "./ImageEncoding/class" + str(classid) + "-pic" + str(i) + ".json"
 		with open(jsonpath,'r') as f:
 			dataset = json.load(f)
@@ -113,11 +113,13 @@ model = Model(
     L1_loss_penalty = L1_loss_penalty,
     threshold = threshold
 ) 
-def run():
+def run(size=500):
     # choose class data
-    train_images, train_labels = d.train.generateSpecializedData(class_id = 1, count = 5)
-    model.encode_class_data(1, train_images)
-    calculate_total_by_weights(1)
+	for i in range(100):
+		train_images, train_labels = d.train.generateSpecializedData(class_id = i, count = size)
+		model.encode_class_data(i, train_images)
+		calculate_total_by_weights(i, size=size)
 
-run()
+run(500)
 
+# calculate_total_by_weights(1, 5)

### 2019-12-24 code/CriticalPathPruning/vggNet.py

@@ -7,7 +7,7 @@ import numpy as np
 import tensorflow as tf
 from sklearn.utils import shuffle
 import os
-os.environ["CUDA_VISIBLE_DEVICES"] = "5,6,7"
+os.environ["CUDA_VISIBLE_DEVICES"] = "0, 1"
 
 # ================== VGG Network Model with Control Gates ==================
 class Model():
@@ -54,6 +54,7 @@ class Model():
     def encode_class_data(self, class_id , train_images):
         # filename = "./innerclass/class"+str(class_id)+"gate.json"
         for i in range(len(train_images)):
+            print('{}/{}'.format(i, len(train_images)))
             generatedGate = self.compute_encoding(train_images[i].reshape((1,32,32,3))) # generatedGate is a list of dicts{layername:xx, shape:xx, lambda:xx}
             picname = "class" + str(class_id) + "-pic" + str(i)
             jsonpath = "./ImageEncoding/" + picname + ".json"
@@ -234,8 +235,8 @@ class Model():
                 self.penalty : L1_loss_penalty
             })
 
-            print("Epoch: {}: Cross_Entropy: {}, L1_loss: {}, Accuracy: {}".format(
-                epoch, cross_entropy, L1_loss, accuracy))
+            # print("Epoch: {}: Cross_Entropy: {}, L1_loss: {}, Accuracy: {}".format(
+                # epoch, cross_entropy, L1_loss, accuracy))
 
             # print(self.AllGateVariables.keys())
             '''

### 2019-12-24 code/CriticalPathPruning/group_encoding.py
code for regrouping iamge encoding

@@ -1,0 +1,25 @@
+import os
+import shutil
+import sys
+
+
+"""
+Regroup your image encoding folder. Completed classes only.
+"""
+def group(IE_dir, CE_dir):
+    safe_classes = [fname.split(".")[0] for fname in os.listdir(CE_dir)]
+    files = [(fname, fname.split("-")[0]) for fname in os.listdir(IE_dir) if ".json" in fname]
+    for fname, class_num in files:
+        if class_num not in safe_classes:
+            continue
+        class_dir = os.path.join(IE_dir, class_num)
+        if not os.path.exists(class_dir):
+            os.mkdir(class_dir)
+        shutil.move(os.path.join(IE_dir, fname), os.path.join(class_dir, fname))
+
+
+if __name__ == '__main__':
+    dir = ['ImageEncoding', 'ClassEncoding']
+    if len(sys.argv) > 1: dir[0] = sys.argv[1]
+    if len(sys.argv) > 2: dir[1] = sys.argv[2]
+    group(*dir)

### 2019-12-24 paper/paper.tex
update paper outline
update title and some formulation

@@
 
+\newcommand{\todo}[1]{\textcolor{red}{[TODO: #1]}}
+
 \begin{document}
@@
 %% Title information
-\title[]{NO TITLE}         %% [Short Title] is optional;
+\title[Network Fusion through CDRP Model Decomposition and Assembly]{Network Fusion through CDRP Model\\ Decomposition and Assembly}         %% [Short Title] is optional;
 %% when present, will be used in
@@
 
+\author{Zhongye Wang}
+% \authornote{Supervised by Qinxiang Cao, Shanghai Jiao Tong University, John Hopcroft Center for Computer Science.}          %% \authornote is optional;
+%% can be repeated if necessary
+%\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
+\affiliation{
+	%\position{Position2b}
+	%\department{Department2b}             %% \department is recommended
+	\institution{Shanghai Jiao Tong University}           %% \institution is required
+	%\streetaddress{Street3b Address2b}
+	%\city{City2b}
+	%\state{State2b}
+	%\postcode{Post-Code2b}
+	%\country{Country2b}                   %% \country is recommended
+}
+% \email{wangzhongye1110@sjtu.edu.cn}          %% \email is recommended
+
 \author{Yichen Xie}
@@
 % \email{}          %% \email is recommended
-
-\author{Zhongye Wang}
-% \authornote{Supervised by Qinxiang Cao, Shanghai Jiao Tong University, John Hopcroft Center for Computer Science.}          %% \authornote is optional;
-%% can be repeated if necessary
-%\orcid{nnnn-nnnn-nnnn-nnnn}             %% \orcid is optional
-\affiliation{
-	%\position{Position2b}
-	%\department{Department2b}             %% \department is recommended
-	\institution{Shanghai Jiao Tong University}           %% \institution is required
-	%\streetaddress{Street3b Address2b}
-	%\city{City2b}
-	%\state{State2b}
-	%\postcode{Post-Code2b}
-	%\country{Country2b}                   %% \country is recommended
-}
-\email{wangzhongye1110@sjtu.edu.cn}          %% \email is recommended
 
@@
 
-\section{Body}
-The body \dots
+\subsection{Our Work}
+
+\section{CDRP Model Decomposition and Clustering}
+\subsection{Critical Data Routing Path Model}
+\subsection{CDRP Model Clustering}
+
+\section{CDRP Model Assembly}
+\subsection{The Assembly Problem}
+For a clear formulation, we define the input of a problem instance to have the following components:
+\begin{itemize}
+	\item $L$ class labels, denoted $\{l_j\}$
+	\item $N$ subclasses in total \begin{itemize}
+		\item $M$ target subclasses, denoted $\mathcal{A} = \{A_i\}$
+		\item $N-M$ dummy subclasses (with irrelevant class labels), denoted $\bar{\mathcal{A}} = \{A_i\}$
+	\end{itemize}
+	\item $g(A_i) := l_j$ the partial map from $A_i$ to class label $l_j$
+	\item $K$ classifiers, denoted $\mathcal{D} = \{d_j\}$
+	\item $f(A_i, d_j) := 0, 1$ the classifier certificate that $A_i$ is classified positive in classifier $d_j$
+	\item $score(d_j)$ the accuracy(?) of classifier $d_j$
+	\item $k$ the maximum number of classifier to use
+\end{itemize}
+
+The solution to the instance should contain:
+\begin{itemize}
+	\item $D \subset \mathcal{D}$ a set of $m$ classifiers \textit{covering} all $M$ target subclasses s.t. $m < k$
+	\item $score(D)$ the overall accuracy(?) of the classifier set
+\end{itemize}
+
+We define the concept of \textit{covering} as follows.
+\begin{definition}
+	A set of classifiers covers $M$ target subclasses iff. given any sample, the joint classifier can determine whether it \textit{solely} belongs to \begin{enumerate}
+		\item a subset (with consistent labels) of the $M$ target subclasses, or,
+		\item the rest dummy subclasses $\bar{\mathcal{A}}$.
+	\end{enumerate}
+\end{definition}
+
+We start with analyzing the intractability of the problem.
+\begin{theorem}
+	The assembly problem is an NP problem.
+\end{theorem}
+\begin{proof}
+We prove the theorem by giving a polynomial algorithm for the certificate problem.
+
+Given a certificate $D \subset \mathcal{D}$, we encode each subclass with a binary string $s$ of length $k$, where the $j$-th element for the $i$ subclass is $f(A_i, d_j)$ ($d_j \in D$).
+This step takes $O(Nk) = O(NK)$ time.
+The algorithm returns $yes$ iff. \begin{enumerate}
+	\item No two subclasses in $\mathcal{A}$ share the same encoding but have different labels, and,
+	\item No subclass in $\mathcal{A}$ shares the same encoding with any subclass in $\bar{\mathcal{A}}$.
+\end{enumerate}
+Otherwise, it returns $no$.
+This step takes $O(N)$ if we use hash table to record the occurrence of encoded strings.
+
+% TODO: correctness proof
+\todo{More proof of the algorithm's correctness}
+\end{proof}
+
+\subsection{The Algorithm}
+
+\section{Experiments}
+\subsection{CDRP Models of VGGNet and ? trained on CIFAR-100}
+\subsection{Fusing VGGNet and ? for Specific Tasks through CDRP Assembly}
 

### 2019-12-25 code/utils.py
utils to load and contract data

@@ -1,0 +1,39 @@
+import os
+import json
+import numpy as np
+
+
+def load_data(root="CriticalPathPruning/ImageEncoding", classes=None):
+    if classes is None:
+        classes = [dir for dir in os.listdir(root) if ".json" not in dir]
+    data = []
+    labels = []
+    sample_names = []
+    for class_id in classes:
+        print("loading {}".format(class_id))
+        path = os.path.join(root, class_id)
+        for fname in os.listdir(path):
+            with open(os.path.join(path, fname), "r") as f:
+                res = json.load(f)
+            tmp = []
+            res.sort(key=lambda item: item["layer_name"])
+            for layer in res:
+                tmp += layer["layer_lambda"]
+            data.append(tmp)
+            labels.append(int(class_id[5:]))
+            sample_names.append(fname)
+    return np.array(data), np.array(labels), sample_names
+
+
+def to_txt(path, data, labels):
+    if not os.path.exists(path):
+        os.mkdir(path)
+    np.savetxt(os.path.join(path, "data.txt"), data)
+    np.savetxt(os.path.join(path, "labels.txt"), labels)
+
+
+if __name__ == '__main__':
+    data, labels, sample_names = load_data(classes=['class0', 'class1', 'class2', 'class3', 'class4',])
+    print(data.shape, labels.shape)
+    print(np.histogram(labels, bins=15))
+    to_txt("./data", data, labels)

### 2019-12-25 code/utils.py
include layer2idx mapping

@@ -2,6 +2,44 @@ import os
 import json
 import numpy as np
 
+# layer names are sorted
+layer2idx = {
+    'Conv1': (0, 64),
+    'Conv10': (64, 576),
+    'Conv11': (576, 1088),
+    'Conv12': (1088, 1600),
+    'Conv13': (1600, 2112),
+    'Conv2': (2112, 2176),
+    'Conv3': (2176, 2304),
+    'Conv4': (2304, 2432),
+    'Conv5': (2432, 2688),
+    'Conv6': (2688, 2944),
+    'Conv7': (2944, 3200),
+    'Conv8': (3200, 3712),
+    'Conv9': (3712, 4224),
+    'FC14': (4224, 8320),
+    'FC15': (8320, 12416)
+}
+
+
+# layer2idx = {
+#     'Conv1': (0, 64),
+#     'Conv10': (2176, 2688),
+#     'Conv11': (2688, 3200),
+#     'Conv12': (3200, 3712),
+#     'Conv13': (3712, 4224),
+#     'Conv2': (64, 128),
+#     'Conv3': (128, 256),
+#     'Conv4': (256, 384),
+#     'Conv5': (384, 640),
+#     'Conv6': (640, 896),
+#     'Conv7': (896, 1152),
+#     'Conv8': (1152, 1664),
+#     'Conv9': (1664, 2176),
+#     'FC14': (4224, 8320),
+#     'FC15': (8320, 12416),
+# }
+
 
 def load_data(root="CriticalPathPruning/ImageEncoding", classes=None):
     if classes is None:
@@ -32,8 +70,20 @@ def to_txt(path, data, labels):
     np.savetxt(os.path.join(path, "labels.txt"), labels)
 
 
+def update_layer2idx():
+    dist = 0
+    for key, item in layer2idx.items():
+        incr = item[1] - item[0]
+        layer2idx[key] = (dist, dist + incr)
+        dist += incr
+    print(layer2idx)
+
+
 if __name__ == '__main__':
-    data, labels, sample_names = load_data(classes=['class0', 'class1', 'class2', 'class3', 'class4',])
+    data, labels, sample_names = load_data(classes=['class0', 'class1', 'class2', 'class3', 'class4', ])
     print(data.shape, labels.shape)
-    print(np.histogram(labels, bins=15))
+    print(np.histogram(labels, bins=np.unique(labels).shape[0]))
     to_txt("./data", data, labels)
+
+    # update_layer2idx()
+    pass

### 2019-12-25 paper/paper.tex
update NP proof

@@
 \usepackage{cleveref}
-
 \crefformat{section}{\S#2#1#3} % see manual of cleveref, section 8.2.1
@@
 \crefformat{subsubsection}{\S#2#1#3}
+
+\usepackage{algorithm}
+\usepackage{algorithmicx}
+\usepackage{algpseudocode}
+\renewcommand{\algorithmicrequire}{\textbf{Input:}}
+\renewcommand{\algorithmicensure}{\textbf{Output:}}
 
@@
 
-% TODO: correctness proof
-\todo{More proof of the algorithm's correctness}
+% \begin{algorithm}[h]
+% 	\caption{}
+% 	\begin{algorithmic}
+% 		\Require A assembly problem instance $k$; a certificate $D \subset \mathcal{D}$.
+% 		\Ensure Whether problem instance $k$ is solvable.
+% 		\State initialize a hash table $H$ with default value -1;
+% 		\For{$i = 1, \cdots, N$}
+% 			\For{$d_j \in D$}
+% 				\State $s_{i,j} \leftarrow f(A_i, d_j)$;
+% 			\EndFor
+% 			\If{$H[s_i]$ != $g(A_i)$}
+% 				\State \Return $no$
+% 			\ElsIf{$H[s_i]$ == -1}
+% 				\State a
+% 			\EndIf
+% 		\EndFor
+% 	\end{algorithmic}
+% \end{algorithm}
+
+We then show the algorithm returns $yes$ iff. $D$ is a certificate to the problem.
+\begin{enumerate}
+	\item[$\Rightarrow$:]
+	The encoding for each target subclass is different from that of another subclass having different labels, meaning the classifier set can distinguish them from subclasses with other labels, and it is then clear that $D$ covers all target subclasses.
+	\item[$\Leftarrow$:]
+	Assume the algorithm returns $no$, then
+	\begin{enumerate}
+		\item Two subclasses with different labels share the same encoding, i.e., the classifier set cannot determine which label to assign for both subclasses, which violates the first condition of the "covering";
+		\item Some target subclass (with meaningful label) share the same encoding with some dummy subclasses.
+		The classifier set cannot determine whether samples of the target subclass belong to the dummy class or not, which violates the second condition.
+	\end{enumerate}
+	Therefor, $D$ is not a certificate to the problem.
+\end{enumerate}
+As a result, the problem instance $k$ is solvable iff. there exists a $D$ with size $k$ such that the algorithm returns $yes$.
+By definition, the problem is an NP problem.
 \end{proof}

### 2019-12-28 code/CriticalPathPruning/run.py
upgrade the CDRP decomposition code to decompose image net vgg

@@ -1,7 +1,8 @@
 import numpy as np
 import json
 from CIFAR_DataLoader import CifarDataManager, display_cifar
-from vggNet import Model
+from vggNet import Model, NameMapping
+import argparse
 
 '''
 Configuration:
@@ -9,117 +10,159 @@ Configuration:
     2. L1 loss penalty
     3. Lambda cotrol gate threshold
 '''
-learning_rate = 0.1
-L1_loss_penalty = 0.03
-threshold = 0.0
-''''''
 
-layer_names = ['FC14/gate:0', 
-    'Conv7/composite_function/gate:0', 
-    'Conv12/composite_function/gate:0', 
-    'Conv2/composite_function/gate:0', 
-    'Conv4/composite_function/gate:0', 
-    'Conv1/composite_function/gate:0', 
-    'Conv6/composite_function/gate:0', 
-    'Conv10/composite_function/gate:0', 
-    'Conv9/composite_function/gate:0', 
-    'FC15/gate:0', 
-    'Conv13/composite_function/gate:0', 
-    'Conv5/composite_function/gate:0', 
-    'Conv3/composite_function/gate:0', 
-    'Conv11/composite_function/gate:0', 
-    'Conv8/composite_function/gate:0'
-]
+layer_names = ['FC14/gate:0',
+               'Conv7/composite_function/gate:0',
+               'Conv12/composite_function/gate:0',
+               'Conv2/composite_function/gate:0',
+               'Conv4/composite_function/gate:0',
+               'Conv1/composite_function/gate:0',
+               'Conv6/composite_function/gate:0',
+               'Conv10/composite_function/gate:0',
+               'Conv9/composite_function/gate:0',
+               'FC15/gate:0',
+               'Conv13/composite_function/gate:0',
+               'Conv5/composite_function/gate:0',
+               'Conv3/composite_function/gate:0',
+               'Conv11/composite_function/gate:0',
+               'Conv8/composite_function/gate:0'
+               ]
 
 
 def calculate_total_by_threshold(classid, size=500):
-	name_shape_match = [
-		{'name': 'FC14/gate:0', 'shape': 4096}, 
-		{'name': 'Conv7/composite_function/gate:0', 'shape': 256}, 
-		{'name': 'Conv12/composite_function/gate:0', 'shape': 512}, 
-		{'name': 'Conv2/composite_function/gate:0', 'shape': 64}, 
-		{'name': 'Conv4/composite_function/gate:0', 'shape': 128}, 
[…]

### 2019-12-28 code/CriticalPathPruning/vggNet.py

@@ -7,15 +7,64 @@ import numpy as np
 import tensorflow as tf
 from sklearn.utils import shuffle
 import os
+
+
 os.environ["CUDA_VISIBLE_DEVICES"] = "0, 1"
+
+
+class NameMapping:
+    # Network name mappings
+    @staticmethod
+    def default_mapping_(name):
+        # print(name, name[:-2])
+        return name[:-2]
+
+    @staticmethod
+    def imagenet_mapping_(name):
+        variable_dict = {
+            "Conv1/composite_function/kernel:0": "block1_conv1/kernel",
+            "Conv1/composite_function/bias:0": "block1_conv1/bias",
+            "Conv2/composite_function/kernel:0": "block1_conv2/kernel",
+            "Conv2/composite_function/bias:0": "block1_conv2/bias",
+            "Conv3/composite_function/kernel:0": "block2_conv1/kernel",
+            "Conv3/composite_function/bias:0": "block2_conv1/bias",
+            "Conv4/composite_function/kernel:0": "block2_conv2/kernel",
+            "Conv4/composite_function/bias:0": "block2_conv2/bias",
+            "Conv5/composite_function/kernel:0": "block3_conv1/kernel",
+            "Conv5/composite_function/bias:0": "block3_conv1/bias",
+            "Conv6/composite_function/kernel:0": "block3_conv2/kernel",
+            "Conv6/composite_function/bias:0": "block3_conv2/bias",
+            "Conv7/composite_function/kernel:0": "block3_conv3/kernel",
+            "Conv7/composite_function/bias:0": "block3_conv3/bias",
+            "Conv8/composite_function/kernel:0": "block4_conv1/kernel",
+            "Conv8/composite_function/bias:0": "block4_conv1/bias",
+            "Conv9/composite_function/kernel:0": "block4_conv2/kernel",
+            "Conv9/composite_function/bias:0": "block4_conv2/bias",
+            "Conv10/composite_function/kernel:0": "block4_conv3/kernel",
+            "Conv10/composite_function/bias:0": "block4_conv3/bias",
+            "Conv11/composite_function/kernel:0": "block5_conv1/kernel",
+            "Conv11/composite_function/bias:0": "block5_conv1/bias",
+            "Conv12/composite_function/kernel:0": "block5_conv2/kernel",
+            "Conv12/composite_function/bias:0": "block5_conv2/bias",
[…]

### 2019-12-28 code/CriticalPathPruning/run.py
auto generate encoding directory

@@ -1,4 +1,5 @@
 import numpy as np
+import os
 import json
 from CIFAR_DataLoader import CifarDataManager, display_cifar
 from vggNet import Model, NameMapping
@@ -29,7 +30,7 @@ layer_names = ['FC14/gate:0',
                ]
 
 
-def calculate_total_by_threshold(classid, size=500):
+def calculate_total_by_threshold(classid, size=500, dataset='cifar'):
     name_shape_match = [
         {'name': 'FC14/gate:0', 'shape': 4096},
         {'name': 'Conv7/composite_function/gate:0', 'shape': 256},
@@ -69,7 +70,7 @@ def calculate_total_by_threshold(classid, size=500):
         json.dump(name_shape_match, g, sort_keys=True, indent=4, separators=(',', ':'))
 
 
-def calculate_total_by_weights(classid, size=500):
+def calculate_total_by_weights(classid, size=500, dataset='cifar'):
     name_shape_match = [
         {'name': 'FC14/gate:0', 'shape': 4096},
         {'name': 'Conv7/composite_function/gate:0', 'shape': 256},
@@ -90,7 +91,14 @@ def calculate_total_by_weights(classid, size=500):
     for i in range(len(name_shape_match)):
         name_shape_match[i]['shape'] = name_shape_match[i]['shape'] * [0]
     for i in range(size):
-        jsonpath = "./ImageEncoding/class" + str(classid) + "-pic" + str(i) + ".json"
+        if dataset == 'cifar':
+            if not os.path.exists('ImageEncoding'):
+                os.mkdir('ImageEncoding')
+            jsonpath = "./ImageEncoding/class" + str(classid) + "-pic" + str(i) + ".json"
+        else:
+            if not os.path.exists(dataset + "-ImageEncoding"):
+                os.mkdir(dataset + "-ImageEncoding")
+            jsonpath = "./" + dataset + "-ImageEncoding/class" + str(classid) + "-pic" + str(i) + ".json"
         with open(jsonpath, 'r') as f:
             dataset = json.load(f)
             for gate in range(len(dataset)):
@@ -101,7 +109,14 @@ def calculate_total_by_weights(classid, size=500):
                             name_shape_match[index]['shape'][conv] += tmp[conv]
                     else:
                         pass
-    json_write_path = "./ClassEncoding/class" + str(classid) + ".json"
+    if dataset == 'cifar':
+        if not os.path.exists('ClassEncoding'):
+            os.mkdir('ClassEncoding')
[…]

### 2019-12-28 code/CriticalPathPruning/vggNet.py
minor changes to orignal search

@@ -376,9 +376,9 @@ class Model():
                 continue
 
             ## Original version: only accept those that are still correct
-            # if accuracy > 0.99 and L1_loss != 'nan' and L1_loss < 1000:
+            if accuracy > 0.99 and L1_loss != 'nan' and L1_loss < 1000:
             ## In another network without correct labels
-            if L1_loss != 'nan' and L1_loss < 1000:
+            # if L1_loss != 'nan' and L1_loss < 1000:
                 if self.verbose:
                     print("Assign gate")
                 generateGate = newGate

### 2019-12-31 code/utils.py
parse CLI input for better data conversion

@@ -1,6 +1,7 @@
 import os
 import json
 import numpy as np
+import argparse
 
 # layer names are sorted
 layer2idx = {
@@ -83,11 +84,40 @@ def normalize(x, lim):
     return (x - x.min()) / (x.max() - x.min()) * (lim[1] - lim[0]) + lim[0]
 
 
+def bool_string(s):
+    s = str.lower(s)
+    assert s in ["true", "false"], "The bool value can only be 'True' or 'False'."
+    return s == "true"
+
+
 if __name__ == '__main__':
-    data, labels, sample_names = load_data(classes=['class0', 'class1', 'class2', 'class3', 'class4', ])
+    parser = argparse.ArgumentParser("Utils")
+    parser.add_argument("prog", help="One of the 'CvtTxt'.", type=str)
+    parser.add_argument(
+        "--encoding_dir", help="Encoding directory.",
+        default="CriticalPathPruning/ImageEncoding", type=str)
+    parser.add_argument(
+        "--save_dir", help="The directory to save converted data.",
+        default="data", type=str)
+    parser.add_argument(
+        "--conv_only", help="Only save the convolution layers.",
+        default="False", type=bool_string)
+    parser.add_argument(
+        "--begin", help="The index of the class to begin.",
+        default=0, type=int)
+    parser.add_argument(
+        "--end", help="The index of the class to end.",
+        default=500, type=int)
+    args = parser.parse_args()
+
+    data, labels, sample_names = load_data(root=args.encoding_dir,
+                                           classes=['class{}'.format(i) for i in range(args.begin, args.end)])
     print(data.shape, labels.shape)
     print(np.histogram(labels, bins=np.unique(labels).shape[0]))
-    to_txt("./data", data, labels)
+    if args.conv_only:
+        to_txt(args.save_dir, data[:, :layer2idx['FC14'][0]], labels)
+    else:
+        to_txt(args.save_dir, data, labels)
 
     # update_layer2idx()
     pass

### 2019-12-31 code/subclass_encoder.py
implement subclass encoder

@@ -1,0 +1,112 @@
+from utils import *
+import pickle
+from copy import deepcopy
+from sklearn.cluster import KMeans, MiniBatchKMeans
+
+
+class SubclassEncoder(object):
+    def __init__(self, data, labels, cluster_per_class=2, threshold=None, verbose=0):
+        classes = np.unique(labels)
+        if verbose: print("Clustering...")
+        kmeans = KMeans(n_clusters=int(len(classes) * cluster_per_class), n_jobs=-1, verbose=verbose).fit(data)
+        if threshold is not None:
+            if verbose: print("Removing anomalies...")
+            cluster_cnts = np.histogram(kmeans.labels_, bins=len(np.unique(kmeans.labels_)))[0]
+            print(cluster_cnts)
+            kmeans.cluster_centers_ = kmeans.cluster_centers_[cluster_cnts > 10]
+            elim_labels = np.where(cluster_cnts <= 10)[0]
+            print(elim_labels)
+            for label in elim_labels:
+                print(kmeans.labels_, label)
+                print(sum(kmeans.labels_ == label))
+                print(data[kmeans.labels_ == label, :].shape)
+                kmeans.labels_[kmeans.labels_ == label] = kmeans.predict(
+                    data[kmeans.labels_ == label, :])
+        self.encoders = [kmeans, ]
+        self._labels = labels.copy()
+
+    def merge(self, other):
+        encoder = deepcopy(self)
+        encoder.encoders += deepcopy(other.encoders)
+        return encoder
+
+    def encode(self, data=None, labels=None):
+        if data is None and labels is None:
+            encoding = np.array([encoder.labels_ for encoder in self.encoders]).T
+            print(encoding.shape, self._labels.shape)
+            encoding = np.concatenate([encoding, self._labels.reshape([-1, 1])], axis=1)
+        else:
+            encoding = np.array([encoder.predict(data) for encoder in self.encoders]).T
+            encoding = np.concatenate([encoding, labels.reshape([-1, 1])], axis=1)
+        return encoding
+
+    @staticmethod
+    def merge_encoding(encodings):
+        res = encodings[0]
+        for i, encoding in enumerate(encodings):
+            if i == 0: continue
+            res = np.concatenate([encoding[:, :-1], res], axis=1)
+        return res
+
+
+if __name__ == '__main__':
+    parser = argparse.ArgumentParser("Subclass Encoder")
+    parser.add_argument("prog", help="One of the 'encode', 'merge'.")
+    parser.add_argument(
[…]

### 2019-12-31 code/utils.py
handle error files

@@ -55,12 +55,18 @@ def load_data(root="CriticalPathPruning/ImageEncoding", classes=None):
             with open(os.path.join(path, fname), "r") as f:
                 res = json.load(f)
             tmp = []
-            res.sort(key=lambda item: item["layer_name"])
+            res = sorted(res, key=lambda item: item["layer_name"])
             for layer in res:
                 tmp += layer["layer_lambda"]
-            data.append(tmp)
-            labels.append(int(class_id[5:]))
+            # assert len(tmp) == 12416, fname + " is bad shaped."
             sample_names.append(fname)
+            if len(tmp) != 12416:
+                print(fname + " is bad shaped.")
+                data.append(np.array(data[-1][:]))
+                labels.append(labels[-1])
+                continue
+            data.append(np.array(tmp))
+            labels.append(int(class_id[5:]))
     return np.array(data), np.array(labels), sample_names
 
 

### 2020-01-01 code/drawer.py
some other updates

@@ -1,9 +1,11 @@
 import os
-
 import imageio
-import matplotlib.pyplot as plt
 import numpy as np
+
+import matplotlib.pyplot as plt
+from mpl_toolkits.mplot3d import Axes3D
 from sklearn.decomposition import PCA
+from sklearn.cluster import KMeans, MiniBatchKMeans
 
 from utils import *
 
@@ -79,6 +81,24 @@ def pca_isolation_gif(data_path="data/data.txt", label_path="data/labels.txt", d
                gif_name, duration, extend=True)
 
 
+def plot_3d_cluster(data, labels, target, n_cluster):
+    fig = plt.figure()
+    ax = Axes3D(fig, rect=[0, 0, .95, 1], elev=48, azim=134)
+
+    X = data[labels == target, :]
+
+    pca = PCA(n_components=3)
+    data_pca = pca.fit_transform(X)
+
+    kmeans = KMeans(n_clusters=n_cluster, random_state=0, n_jobs=-1, verbose=1).fit(X)
+    centers = pca.transform(kmeans.cluster_centers_)
+
+    for label in np.unique(kmeans.labels_):
+        mask = (kmeans.labels_ == label)
+        plt.scatter(data_pca[mask, 0], data_pca[mask, 1], data_pca[mask, 2], label="cluster " + str(int(label)))
+    plt.scatter(centers[:, 0], centers[:, 1], centers[:, 2], marker='s', label='centers', c='b')
+
+
 def run_pca_gif():
     flips = [
         [],  # 1
@@ -112,6 +132,14 @@ def run_pca_gif():
     ])
     rotates = rotates / 180 * np.pi
     pca_isolation_gif(flips=flips, rotates=rotates)
+
+
+def run_plot_3d_cluster(data_path="data/data.txt", label_path="data/labels.txt"):
+    print("Importing data...")
+    data = np.loadtxt(data_path)
+    print("Importing labels...")
+    labels = np.loadtxt(label_path)
+    plot_3d_cluster(data, labels, 4, 3)
 
 
 if __name__ == '__main__':

### 2020-01-01 code/subclass_encoder.py

@@ -14,7 +14,9 @@ class SubclassEncoder(object):
             cluster_cnts = np.histogram(kmeans.labels_, bins=len(np.unique(kmeans.labels_)))[0]
             print(cluster_cnts)
             kmeans.cluster_centers_ = kmeans.cluster_centers_[cluster_cnts > 10]
-            elim_labels = np.where(cluster_cnts <= 10)[0]
+            elim_labels = np.where(cluster_cnts <= 10)
+            if type(elim_labels) is tuple and len(elim_labels) == 1:
+                elim_labels = elim_labels[0]
             print(elim_labels)
             for label in elim_labels:
                 print(kmeans.labels_, label)
@@ -63,7 +65,7 @@ if __name__ == '__main__':
         default="data/sub_encoding.txt", type=str)
     parser.add_argument(
         "--cluster_per_class", help="Clusters per class.",
-        default=2, type=int)
+        default=2, type=float)
     parser.add_argument(
         "--threshold", help="Minimum samples a cluster should have.",
         default=None, type=float)

### 2020-01-01 code/utils.py

@@ -109,10 +109,10 @@ if __name__ == '__main__':
         "--conv_only", help="Only save the convolution layers.",
         default="False", type=bool_string)
     parser.add_argument(
-        "--begin", help="The index of the class to begin.",
+        "--begin", help="The index of the class to begin. Inclusive.",
         default=0, type=int)
     parser.add_argument(
-        "--end", help="The index of the class to end.",
+        "--end", help="The index of the class to end. Exclusive",
         default=500, type=int)
     args = parser.parse_args()
 

### 2020-01-02 code/drawer.py
update plot network venn

@@ -1,6 +1,7 @@
 import os
 import imageio
 import numpy as np
+import networkx as nx
 
 import matplotlib.pyplot as plt
 from mpl_toolkits.mplot3d import Axes3D
@@ -99,6 +100,45 @@ def plot_3d_cluster(data, labels, target, n_cluster):
     plt.scatter(centers[:, 0], centers[:, 1], centers[:, 2], marker='s', label='centers', c='b')
 
 
+def plot_network_venn(data, subclasses, cluster_sets, ncol):
+    count = lambda x: sum((data[:, 0] == x[0]) & (data[:, 1] == x[1]))
+    per_col = np.ceil(subclasses.shape[0] / ncol)
+    labels = subclasses[:, -1]
+    subclasses = subclasses[:, :-1]
+    stride = 15 * 0.5 / per_col
+    markers = dict()
+    cluster_markers = dict()
+
+    G = nx.Graph()
+    cl_pos = dict()
+    cmap = ['b', 'g']
+    for i, subclass in enumerate(subclasses):
+        for j, cl in enumerate(subclass):
+            plt.plot([1 + 1 * (i // per_col), j * 4], [stride * (i % per_col) - 0.5, cl * 1],
+                     c=plt.cm.Blues(j * 0.4 + 0.4))
+    for i, subclass in enumerate(subclasses):
+        G.add_node(i, encoding=subclass, size=count(subclass) * 5 + 200, shape='skyblue',
+                   pos=(1 + 1 * (i // per_col) - 0.2, stride * (i % per_col) - 0.5))
+        markers[int(labels[i])], = plt.plot(1 + 1 * (i // per_col), stride * (i % per_col) - 0.5, marker='o', ms=5,
+                                            c=plt.cm.winter(labels[i] / labels.max()))
+        plt.plot(1 + 1 * (i // per_col), stride * (i % per_col) - 0.5, marker='o', ms=count(subclass) / 10 + 5,
+                 c=plt.cm.winter(labels[i] / labels.max()))
+    for i, clusters in enumerate(cluster_sets):
+        for cl in clusters:
+            G.add_node('{:.0f}-{:.0f}'.format(i, cl), encoding=None, size=500, shape='orangered', pos=(i * 4, cl * 1))
+            cluster_markers[i], = plt.plot(i * 4, cl * 1, ms=5, marker='s', c=plt.cm.Blues(i * 0.3 + 0.3))
[…]

### 2020-01-02 Pseudo Code/template.tex
Create template.tex

%!TEX program = Xelatex
\documentclass{article}
\usepackage{amsmath,amscd,amsbsy,amssymb,latexsym,url,bm,amsthm}
\usepackage{epsfig,graphicx,subfigure}
\usepackage{enumitem,balance,mathtools}
\usepackage{wrapfig}
\usepackage{mathrsfs, euscript}
\usepackage{hyperref}
\usepackage{listings}
\usepackage[ruled,lined,boxed,linesnumbered]{algorithm2e}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{exercise}{Exercise}[section]
\newtheorem*{solution}{Solution}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\newcommand{\postscript}[2]
    {\setlength{\epsfxsize}{#2\hsize}
    \centerline{\epsfbox{#1}}}
\renewcommand{\baselinestretch}{1.0}

\setlength{\oddsidemargin}{-0.365in}
\setlength{\evensidemargin}{-0.365in}
\setlength{\topmargin}{-0.3in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textheight}{10.1in}
\setlength{\textwidth}{7in}

\begin{document}

% ------------------ your name and number ----------------- %

% --------------------------------------------------------- %
\begin{itemize}
\item $U$: used classifiers $(d_{i})$
\item $R_i$: coding results: $(r_{i_1},r_{i_2},\cdots,r_{i_{n}}),r_i\in\{0,1\}$
\item $Pos_i$: Remaining labels if result of $d_i$ is $1$
\item $Neg_i$: Remaining labels if result of $d_i$ is $0$
\item $C$: array of coding results $(R_1,R_2,\cdots,R_m)$
\item $E$: Remaining labels of each coding in $C$: $(\{l_j\}),|C|=|R|$
\item $m_i$: possibility of result $r_i$:
$$
m_i=\left\{
\begin{array}{cc}
\frac{2}{K} & r_i=1, positive\\
\frac{K-2}{K} & r_i=0, negative\\
1 & r_i=2, meaningless\\
\end{array}
\right.
$$

\item $a=(a_1,a_2)$: concatenation of two arrays

\end{itemize}

\begin{algorithm}
\caption{}
$U=\phi$\\
$Entropy\leftarrow \sum_{i=1}^{L}\frac{1}{L}\log\frac{1}{L}=L$\\
\While {$Entropy>0$}{
	$min\leftarrow\infty$\\
	\ForEach {$d_i\in D-U$}{
			$S,T\leftarrow Split(E,C,d_i)$\\

			\ForEach{$i\in\{1,2,\cdots,|S|\}$}{
				$p_i=\prod_{j=1}^{|T_i|}m_{T_i^j}$\\
			}
			$e_i\leftarrow\sum_{j=1}^{|S_i|}\frac{1}{|S_i|}\log\frac{1}{|S_i|}=S_i$\\
			$H\leftarrow\sum_{j=1}^{|S|}p_je_j$\\
			\If{$H<min$}{
				$S_{min}\leftarrow S$\\
				$T_{min}\leftarrow T$\\
				$k\leftarrow i$\\
				$min\leftarrow H$\\
			}
	}
	$Entropy\leftarrow min$\\
	$E\leftarrow S_{min}$\\
	$C\leftarrow T_{min}$\\
	$U\leftarrow (U,d_k)$\\
}

\end{algorithm}

\begin{algorithm}
\caption{$Split(E,C,d_i)$}
$S\leftarrow$ Empty Array\\
$T\leftarrow$ Empty Array\\
\ForEach{$E_i\in E$}{
	\If {$Pos_i\cap E_i=\phi$ or $Neg_i\cap E_i=\phi$}{
		$S\leftarrow S+\{E_i\}$\\
		$T_0\leftarrow (C_i,2)$\\
		$T\leftarrow (T,(T_0))$\\
	}
	\Else{
		$S\leftarrow S+\{E_i\}\cap Pos_i$\\
		$T_0\leftarrow (C_i,1)$\\
		$T\leftarrow (T,(T_0))$\\
		$S\leftarrow S+\{E_i\}\cap Neg_i$\\
		$T_0\leftarrow (C_i,0)$\\
		$T\leftarrow (T,(T_0))$\\
	}
\Return $S,T$\\
}

\end{algorithm}

\end{document}

### 2020-01-03 Pseudo Code/template.tex
Update template.tex

@@
 \begin{itemize}
-\item $U$: used classifiers $(d_{i})$
-\item $R_i$: coding results: $(r_{i_1},r_{i_2},\cdots,r_{i_{n}}),r_i\in\{0,1\}$
+\item $U$: used classifiers: $(d_{i})$
+
 \item $Pos_i$: Remaining labels if result of $d_i$ is $1$
 \item $Neg_i$: Remaining labels if result of $d_i$ is $0$
-\item $C$: array of coding results $(R_1,R_2,\cdots,R_m)$
-\item $E$: Remaining labels of each coding in $C$: $(\{l_j\}),|C|=|R|$
-\item $m_i$: possibility of result $r_i$:
+\item $R_i$: code: array $(r_{i_1},r_{i_2},\cdots,r_{i_{n}}),r_i\in\{0,1,2\}$
 $$
-m_i=\left\{
+r_i=\left\{
 \begin{array}{cc}
-\frac{2}{K} & r_i=1, positive\\
-\frac{K-2}{K} & r_i=0, negative\\
-1 & r_i=2, meaningless\\
+1 & result\ of\ d_i\ is\ true\\
+0 & result\ of\ d_i\ is\ false\\
+2 & d_i\ can\ only\ be\ true\ or\ false\ theoretically\\
 \end{array}
@@
 $$
-
-\item $a=(a_1,a_2)$: concatenation of two arrays
+\item $C$: array of codes $(R_1,R_2,\cdots,R_m)$
+\item $E$: Remaining labels of each code in $C$: $(\{l_j\}),|C|=|R|$
 
@@
 \caption{}
-$U=\phi$\\
-$Entropy\leftarrow \sum_{i=1}^{L}\frac{1}{L}\log\frac{1}{L}=L$\\
+$U=\phi$;\\
+$Entropy\leftarrow -\sum_{i=1}^{L}\frac{1}{L}\log\frac{1}{L}=logL$;\\
 \While {$Entropy>0$}{
-	$min\leftarrow\infty$\\
+	$min\leftarrow\infty$;\\
 	\ForEach {$d_i\in D-U$}{
-			$S,T\leftarrow Split(E,C,d_i)$\\
+			$S,T\leftarrow Split(E,C,d_i)$\tcp*[r]{if we choose $d_i$ as new classifier, renew the code and result}
 
 			\ForEach{$i\in\{1,2,\cdots,|S|\}$}{
-				$p_i=\prod_{j=1}^{|T_i|}m_{T_i^j}$\\
+				$p_i=\prod_{j=1}^{|T_i|}m_{T_i^j}$ \tcp*[r]{probability of result $T_i$}
 			}
-			$e_i\leftarrow\sum_{j=1}^{|S_i|}\frac{1}{|S_i|}\log\frac{1}{|S_i|}=S_i$\\
-			$H\leftarrow\sum_{j=1}^{|S|}p_je_j$\\
+			$e_i\leftarrow-\sum_{j=1}^{|S_i|}\frac{1}{|S_i|}\log\frac{1}{|S_i|}$;\\
+			$H\leftarrow\sum_{j=1}^{|S|}p_je_j$;\\
 			\If{$H<min$}{
-				$S_{min}\leftarrow S$\\
-				$T_{min}\leftarrow T$\\
-				$k\leftarrow i$\\
-				$min\leftarrow H$\\
+				\tcc{record the min value of entropy and args}
+				$S_{min}\leftarrow S$;\\
+				$T_{min}\leftarrow T$;\\
+				$k\leftarrow i$;\\
+				$min\leftarrow H$;\\
 			}
 	}
-	$Entropy\leftarrow min$\\
-	$E\leftarrow S_{min}$\\
-	$C\leftarrow T_{min}$\\
-	$U\leftarrow (U,d_k)$\\
+	\tcc{renew the min value of entropy and args}
+	$Entropy\leftarrow min$;\\
+	$E\leftarrow S_{min}$;\\
+	$C\leftarrow T_{min}$;\\
+	add $d_k$ to used classifiers set $U$;\\
 }
@@
 \caption{$Split(E,C,d_i)$}
-$S\leftarrow$ Empty Array\\
-$T\leftarrow$ Empty Array\\
+$S\leftarrow$ Empty Array;\\
+$T\leftarrow$ Empty Array;\\
 \ForEach{$E_i\in E$}{
 	\If {$Pos_i\cap E_i=\phi$ or $Neg_i\cap E_i=\phi$}{
-		$S\leftarrow S+\{E_i\}$\\
-		$T_0\leftarrow (C_i,2)$\\
-		$T\leftarrow (T,(T_0))$\\
+		$S\leftarrow S+\{E_i\}$\tcp*[r]{add $E_i$ to $S$ as an item directly}
+		add a $2$ to the end of code $C_i$, and add the new code item to $T$;\\
 	}
 	\Else{
-		$S\leftarrow S+\{E_i\}\cap Pos_i$\\
-		$T_0\leftarrow (C_i,1)$\\
-		$T\leftarrow (T,(T_0))$\\
-		$S\leftarrow S+\{E_i\}\cap Neg_i$\\
-		$T_0\leftarrow (C_i,0)$\\
-		$T\leftarrow (T,(T_0))$\\
+
+		$S\leftarrow S+(\{E_i\}\cap Pos_i)$\tcp*[r]{Split $E_i$ into two items, add the two items to $S$ separately}
+		$S\leftarrow S+(\{E_i\}\cap Neg_i)$;\\
+		add an $1$ to the end of code $C_i$, and add the new code item to $T$;\\
+		add a $0$ to the end of code $C_i$, and add the new code item to $T$;\\
+
 	}
-\Return $S,T$\\
+\Return $S,T$;\\
+}
+
+\end{algorithm}
+
+\begin{algorithm}
+\caption{Heuristic-Search(U,C,E)}
+\If {$|U|=k$}{
+	\If {$|E_i|=1,\forall i\in\{1,2,\cdots,|E|\}$}
+	{
+		End the search and $U$ are the chosen classifiers\tcp*[r]{one code maps to one label}
+	}
+	\Else{
+		\Return to the previous recursion;\\
+	}
+}
+$PriorityQueue\leftarrow empty$\tcp*[r]{the priority queue(big-end) to record the entropy}
+\ForEach {$d_i\in D-U$}{
+	$E',C'\leftarrow Split(E,C,d_i)$\tcp*[r]{if choose $d_i$ as next classifier, renew codes and mapped labels}
+	\ForEach{$j\in\{1,2,\cdots,|C|\}$}{
+		$p_j=p(C_j)=p(r_1,r_2,\cdots,r_{|C_j|})$\tcp*[r]{probability of result $C_j'$}
+	}
+	$H'=\sum_{j=1}^{|E|}p_j(-\sum_{k=1}^{|E_j|}\frac{1}{|E_j|}\log\frac{1}{|E_j|})=\sum_{j=1}^{|E|}p_j\log |E_j|$;\\
+	add $((E',C',k),H')$ to $PriorityQueue$ as $(key,value)$ pair;
+}
+
+\While{$PriorityQueue$ not empty}{
+	$((E',C',k),H')\leftarrow$ top of $PriorityQueue$\tcp*[r]{fetch the element on the top of priority queue}
+	Heuristic-Search($U\cup\{d_k\},C',E'$);
 }

### 2020-01-06 paper/paper.tex
update the paper to re-organize, and include the intro sample and more illustrative problem formulation

@@
 \section{Introduction}
+\label{sec:intro}
 The introduction \dots
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.75\linewidth]{fig/formulation_example.png}
+    \caption{An Example Assembly Problem}
+    \label{fig:assemble-example-venn}
+\end{figure}
+
+Figure~\ref{fig:assemble-example-venn} shows an example of the assembly problem of our interest.
+The original dataset contains 3 classes $A_1, A_2$, and $A_3$, and we are able to decompose each into some subclasses, e.g., $A_1$ is decomposed into two subclasses of samples $A_{11}$ and $A_{12}$.
+There are 4 binary classifiers, each determines whether a sample belongs to the union of some subclasses marked with boxes, e.g., $d_1$ determines whether a sample belongs to the union of $\{A_{11}, A_{12}, A_{21}, A_{22}\}$.
+We can use classifiers $d_1, d_2, d_3$ and set operations for the classification task:
+\begin{itemize}
+	\item $d_1 - (d_2 + d_3)$ determines samples belong to $A_1$;
+	\item $d_1 \cdot d_2 + d_3$ determines samples belong to $A_2$;
+	\item $d_2 - d_1$ determines samples belong to $A_3$.
+\end{itemize}
+For the partial classification task of class $A_3$, it suffices to use only $d_2$ and $d_4$ and their intersection $d_2 \cdot d_4$ to determine samples in $A_3$.
 
@@
 
-\section{CDRP Model Decomposition and Clustering}
-\subsection{Critical Data Routing Path Model}
-\subsection{CDRP Model Clustering}
+\section{The General Assembly Framework}
+\label{sec:assembly}
+In this section, we give the general framework to assemble multiple classifiers into one that performs complex classification tasks.
+The classification task only need to cover a given set of labels, and we do not need to distinguish the remaining dummy classes.
+We also propose an heuristic search algorithm to find a feasible solution to the assembly problem.
 
-\section{CDRP Model Assembly}
+We only consider the general case of such assembly in this section, while we specialize the assembly problem w.r.t. input composed of CDRP models in \cref{sec:cdrp}.
+The assembly problem can be easily extended to general classifier input, but we only discuss the case for binary classifier input for simplicity.
+
 \subsection{The Assembly Problem}
-For a clear formulation, we define the input of a problem instance to have the following components:
+\label{sec:assemble-problem}
+We first formulate the problem by defining the input of an assembly problem and the output it requires.
+
+The input have the following components:
 \begin{itemize}
@@
 		\item $M$ target subclasses, denoted $\mathcal{A} = \{A_i\}$
-		\item $N-M$ dummy subclasses (with irrelevant class labels), denoted $\bar{\mathcal{A}} = \{A_i\}$
+		\item $N-M$ dummy subclasses, denoted $\bar{\mathcal{A}} = \{A_i\}$
 	\end{itemize}
@@
 	\item $K$ classifiers, denoted $\mathcal{D} = \{d_j\}$
-	\item $f(A_i, d_j) := 0, 1$ the classifier certificate that $A_i$ is classified positive in classifier $d_j$
-	\item $score(d_j)$ the accuracy(?) of classifier $d_j$
+	\item $f(A_i, d_j) := 0, 1$ the classifier certificate function that $A_i$ is classified positive in classifier $d_j$
+	\item $score(d_j)$ the performance score of classifier $d_j$
 	\item $k$ the maximum number of classifier to use
@@
 
-The solution to the instance should contain:
+The original dataset consists of $L$ classes with different labels.
+Some prior knowledge allows us to decompose the dataset into $N$ subclasses of samples.
+A subclass is the unit sample group we will consider in the assembly problem, and for a subclass to be \textit{consistent}, we assume all samples in a subclass have the sample label given by the partial map $g$.
+Since we are only interested in a subset of labels, we group all $M$ target subclasses having these labels into $\mathcal{A}$
+The rest $N-M$ subclasses are dummy ones.
+
+We are given $K$ binary classifiers with domains of the entire dataset.
+All samples in a subclass $A_i$ should be assigned the same 0-1 label by a classifier $d_j$, which is determined by the certificate function $f$.
+To extend the assembly problem to general classifier inputs, we only need to change the certificate function $f$ for classifiers to allow return values from a set of multiple symbols.
+The cardinality of $f$'s range should be $n$ for an $n$-classifier assembly problem.
+For example, a ternary classifier assembly problem needs the certificate function to produce three possible symbols, i.e., $|range(f)| = 3$.
+
+For each classifier, we also know its performance score, which could be its accuracy, its model complexity, or both.
+There is a constraint for a problem instance that we can only use up to $k$ classifiers to assemble the final classifier.
+
+The solution to the problem instance should contain:
 \begin{itemize}
-	\item $D \subset \mathcal{D}$ a set of $m$ classifiers \textit{covering} all $M$ target subclasses s.t. $m < k$
-	\item $score(D)$ the overall accuracy(?) of the classifier set
+	\item $D \subset \mathcal{D}$ a set of $m$ classifiers \textit{distinguishing} all $M$ target subclasses s.t. $m < k$
+	\item $score(D)$ the overall performance of the classifier set
 \end{itemize}
 
-We define the concept of \textit{covering} as follows.
+\todo{The overal performance score.}
+
+We define the concept of \textit{distinguishing} as follows.
 \begin{definition}
@@
 \end{definition}
+In other word, the classifier should uniquely determine whether a sample have which of the target labels or the dummy label.
 
@@
 \subsection{The Algorithm}
+\label{sec:assembly-algorithm}
+
+\section{Model Assembly based on CDRP Decomposition and Clustering}
+\label{sec:cdrp}
+\subsection{Critical Data Routing Path Model}
+\subsection{CDRP Model Clustering}
+\subsection{CDRP Model Assembly}
 

### 2020-01-06 proposal/proposal.tex
update proposal figure and some notation

@@
 
+\newpage
+\begin{itemize}
+	\item $L$ class labels, denoted $\{l_j\}$
+	\item $N$ subclasses in total \begin{itemize}
+		\item $M$ target subclasses, denoted $\mathcal{A} = \{A_i\}$
+		\item $N-M$ dummy subclasses (with irrelevant class labels), denoted $\bar{\mathcal{A}} = \{A_i\}$
+	\end{itemize}
+	\item $g(A_i) := l_j$ the partial map from $A_i$ to class label $l_j$
+	\item $K$ classifiers, denoted $\mathcal{D} = \{d_j\}$
+	\item $f(A_i, d_j) := 0, 1$ the classifier certificate that $A_i$ is classified positive in classifier $d_j$
+	\item $score(d_j)$ the performance of classifier $d_j$
+	\item $k$ the maximum number of classifier to use
+\end{itemize}
+
+\begin{itemize}
+	\item $D \subset \mathcal{D}$ a set of $m$ classifiers \textit{covering} all $M$ target subclasses s.t. $m < k$
+	\item $score(D)$ the overall performance of the classifier set
+\end{itemize}
+
+We define the concept of \textit{covering} as follows.
+\begin{definition}
+	A set of classifiers covers $M$ target subclasses iff. given any sample, the joint classifier can determine whether it \textit{solely} belongs to \begin{enumerate}
+		\item a subset (with consistent labels) of the $M$ target subclasses, or,
+		\item the rest dummy subclasses $\bar{\mathcal{A}}$.
+	\end{enumerate}
+\end{definition}
+
 % embedding

### 2020-01-07 paper/paper.tex
include encoding demo for the intro example, include the heuristic search algorithm, need better entropy formula

@@
 \usepackage{multicol}
+\usepackage{multirow}
 \usepackage{lipsum}
@@
 	\begin{enumerate}
-		\item Two subclasses with different labels share the same encoding, i.e., the classifier set cannot determine which label to assign for both subclasses, which violates the first condition of the "covering";
+		\item Two subclasses with different labels share the same encoding, i.e., the classifier set cannot determine which label to assign for both subclasses, which violates the first condition of the \textit{distinguishing};
 		\item Some target subclass (with meaningful label) share the same encoding with some dummy subclasses.
@@
 
-\subsection{The Algorithm}
+The table in Figure~\ref{fig:assemble-example-encoding} shows the encoding mentioned in the certificate algorithm.
+If we only use the encoding from $d_1, d_2, d_3$, we find no two subclasses with different labels share the same encoding, and therefore certify the correctness of the feasible solution proposed before.
+For the partial classification task for $A_3$, using two bits from $d_2, d_4$ already provides distinguishable encoding for $A_{31}$ and the remaining dummy classes.
+
+% \linespread{1.1}
+\begin{figure}[h]
+	\begin{tabular}{|c|c|cccc|}
+	\cline{1-6}
+	\multicolumn{2}{|c|}{} & $d_1$ & $d_2$ & $d_3$ & $d_4$ \\ \cline{1-6}
+	\multirow{2}{*}{$A_1$} & $A_{11}$ & 1 & 0 & 0 & 0 \\ \cline{2-6}
+	 & $A_{12}$ & 1 & 0 & 0 & 0 \\ \cline{1-6}
+	\multirow{3}{*}{$A_2$} & $A_{21}$ & 1 & 1 & 0 & 0 \\ \cline{2-6}
+	 & $A_{22}$ & 1 & 0 & 1 & 1 \\ \cline{2-6}
+	 & $A_{23}$ & 0 & 0 & 1 & 0 \\ \cline{1-6}
+	$A_3$ & $A_{31}$ & 0 & 1 & 0 & 1 \\ \cline{1-6}
+	\end{tabular}
+	\caption{Encoding for the Intro Example}
+	\label{fig:assemble-example-encoding}
+\end{figure}
+% \linespread{1.0}
+
+\subsection{The Heuristic Search Algorithm}
 \label{sec:assembly-algorithm}
+Based on the encoding method, we propose a search algorithm based on greedy heuristics in Table~\ref{tab:heuristic-search} for finding a feasible solution to the problem instance with constraint $k$.
+
+\begin{algorithm}
+	\caption{The General Algorithm}
+	\label{tab:heuristic-search}
+	\begin{algorithmic}[1]
+		\Require The inputs to the assembly problem;
+		\Ensure $D$, a classifier set satisfying constraints, or $\emptyset$ if not feasible.
+		\State $Q \gets \emptyset$; \Comment A priority queue, the last element $h$ is the key
+		\Function{Expand}{$D$} \Comment $D$, the classifier set
+			\For{$d \in \mathcal{D} - D$}
+				\State Calculate the encoding $C$ using $D \cup \{d\}$;
+				\State Calculate the entropy $h$ for $C$;
+				\State $Q \gets Q \cup \{(D \cup \{d\}, C, h)\}$;
+			\EndFor
+		\EndFunction
+		\Function{HeuristicSearch}{}
+			\State $\Call{Expand}{\emptyset}$;
+			\While{$Q \neq \emptyset$}
+				\State $(D, C, h) \gets Pop(Q)$;
+				\If{$e_0 == 0$}
+					\State \Return $D$;
+				\EndIf
+				\If{|D| < k}
+					\State $\Call{Expand}{D}$;
+				\EndIf
+			\EndWhile
+			\State \Return $\emptyset$;
+		\EndFunction
+	\end{algorithmic}
+\end{algorithm}
+
+The search is guided by the residual entropy of target subclasses and dummy subclasses.
+\begin{equation}
+	H(C) = \sum_{c \in C} p(c)H(c) = \sum_{c \in C} p(c)\sum_{l \in \mathcal{L}'} p(c, l)\log\frac{1}{p(c, l)}
+\end{equation}
 

### 2020-01-07 code/CriticalPathPruning/CIFAR_DataLoader.py
finetune and fusion

@@ -4,7 +4,9 @@ import numpy as np
 import matplotlib.pyplot as plt
 import os
 import keras
+import random
 import _pickle as cPickle
+import pickle
 
 # =============== Define Data Loader ===============
 ''' Utility Functions '''
@@ -28,8 +30,20 @@ class CifarLoader(object):
 
         self.images = None
         self.labels = None
+        self.class_image = None
+        self.class_label = None
 
     def load(self):
+        with open("../data/clusters.pkl","rb") as file:
+            self.cluster = pickle.load(file,encoding="bytes")
+        with open("../data/class_clusters.pkl","rb") as file:
+            self.class_cluster = pickle.load(file,encoding="bytes")
+
+        with open("../data/clusters_test.pkl","rb") as file:
+            self.cluster_test = pickle.load(file,encoding="bytes")
+        with open("../data/class_clusters_test.pkl","rb") as file:
+            self.class_cluster_test = pickle.load(file,encoding="bytes")
+
         data = [unpickle(f) for f in self._source]
         images = np.vstack(d["data"] for d in data)
 
@@ -38,13 +52,94 @@ class CifarLoader(object):
         # self.labels = one_hot(np.hstack([d["fine_labels"] for d in data]), 100)
         self.labels = np.hstack([d["fine_labels"] for d in data])
         self.images = self.normalize_images(self.images)
+
+        self.class_image = []
+        self.class_label = []
+        for id in range(100):
+            self.class_label.append(list(self.labels[self.labels==id]))
+            self.class_image.append(list(self.images[self.labels == id]))
+
+        # self.class_label = np.array(self.class_label)
+        # self.class_image = np.array(self.class_image)
         return self
 
     def next_batch(self, batch_size):
         x, y = self.images[self._i:self._i+batch_size], self.labels[self._i:self._i+batch_size]
         self._i = (self._i + batch_size) % len(self.images)
-        return x, one_hot(y, 100) 
-    
+        return x, one_hot(y, 100)
+
+    def next_batch_balance(self,batch_size,target_class_id,mode = "class", type = "train"):
+        num = batch_size // (len(target_class_id)+1)
+        tmp = []
+        if type == "train":
+            class_cluster = self.class_cluster
+        else:
+            class_cluster = self.class_cluster_test
+        for class_id in target_class_id:
+            # class_image = random.sample(self.class_image[class_id],num)
+            # class_label = random.sample(self.class_label[class_id],num)
+            for _ in range(num):
[…]

### 2020-01-07 code/CriticalPathPruning/cluster_predictor.py

@@ -1,0 +1,63 @@
+import pickle
+import json
+from copy import deepcopy
+from sklearn.cluster import KMeans, MiniBatchKMeans
+# from utils import *
+from CIFAR_DataLoader import CifarDataManager, display_cifar
+from subclass_encoder import SubclassEncoder
+import sys
+import argparse
+
+if __name__ == '__main__':
+    parser = argparse.ArgumentParser("Cluster predictor")
+    parser.add_argument(
+        "--start_class", help="start class of predictor",
+        default=0, type=int
+    )
+    parser.add_argument(
+        "--end_class", help="end class of predictor",
+        default=99, type=int
+    )
+
+    args = parser.parse_args()
+
+
+    class_counter = {}
+    class_clusters = {}
+    for class_id in range(args.start_class,args.end_class+1):
+        class_counter[class_id] = 0
+        class_clusters[class_id] = []
+
+
+
+    with open("../data/encoder.pkl", "rb") as file:
+        encoder = pickle.load(file)
+    kmeans = encoder.encoders[0]
+
+    data_loader = CifarDataManager()
+
+    batch_size = 100
+    clusters = []
+    for _ in range(100*100//batch_size):
+        print(_)
+        train_images, test_labels = data_loader.test.next_batch_without_onehot(batch_size)
+        for i in range(batch_size):
+            label = test_labels[i]
+            if label<args.start_class or label>args.end_class:
+                continue
+            path = "ImageEncoding_test/class%d/class%d-pic%d.json"%(label,label,class_counter[label])
+            with open(path, "r") as file:
+                res = json.load(file)
+            tmp = []
+            res = sorted(res, key=lambda item: item["layer_name"])
+            for layer in res:
+                tmp += layer["layer_lambda"]
+            cluster = kmeans.predict([tmp])[0]
+            clusters.append(cluster)
+            class_clusters[label].append(cluster)
+            class_counter[label] += 1
+
+    with open("../data/clusters_test.pkl","wb") as file:
+        pickle.dump(clusters,file)
+    with open("../data/class_clusters_test.pkl","wb") as file:
+        pickle.dump(class_clusters,file)

### 2020-01-07 code/CriticalPathPruning/cluster_translator.py

@@ -1,0 +1,72 @@
+import pickle
+import json
+from copy import deepcopy
+from sklearn.cluster import KMeans, MiniBatchKMeans
+# from utils import *
+from CIFAR_DataLoader import CifarDataManager, display_cifar
+# from subclass_encoder import SubclassEncoder
+import sys
+import argparse
+
+
+if __name__ == '__main__':
+    parser = argparse.ArgumentParser("Cluster predictor")
+    parser.add_argument(
+        "--encoder_save_path", help="The file to save the encoder.",
+        default="../data/encoder.pkl", type=str)
+    parser.add_argument(
+        "--start_class", help="start class of predictor",
+        default=0, type=int
+    )
+    parser.add_argument(
+        "--end_class", help="end class of predictor",
+        default=99, type=int
+    )
+    args = parser.parse_args()
+
+    #
+    # with open(args.encoder_save_path, "rb") as file:
+    #     encoder = pickle.load(file)
+    with open("../data/sub_encoding.txt") as file:
+        sub_encoding = file.readlines()
+    classid_cluster = {}
+    for l in sub_encoding:
+        line = l.strip()
+        line = line.split(" ")
+        if len(line)<2:
+            continue
+        label = int(float(line[1]))
+        cluster = int(float(line[0]))
+        if label in classid_cluster:
+            classid_cluster[label].append(cluster)
+        else:
+            classid_cluster[label] = [cluster]
+
+    class_counter = {}
+    class_clusters = {}
+    for class_id in range(args.start_class,args.end_class+1):
+        class_counter[class_id] = 0
+        class_clusters[class_id] = []
+
+    data_loader = CifarDataManager()
+
+    batch_size = 100
+    clusters = []
+    for _ in range(500*100//batch_size):
+        train_images, train_labels = data_loader.train.next_batch_without_onehot(batch_size)
+        for i in range(batch_size):
+            label = train_labels[i]
+            if label<args.start_class or label>args.end_class:
+                continue
+            clusters.append(classid_cluster[label][class_counter[label]])
+            class_clusters[label].append(classid_cluster[label][class_counter[label]])
+            class_counter[label] += 1
+
+    with open("../data/clusters.pkl","wb") as file:
+        pickle.dump(clusters,file)
+    with open("../data/class_clusters.pkl","wb") as file:
+        pickle.dump(class_clusters,file)
+
+
+
+

### 2020-01-07 code/CriticalPathPruning/kmeans.py

@@ -1,0 +1,214 @@
+# coding: utf-8
+import math
+import random
+import os
+import json
+from collections import defaultdict
+import numpy as np
+
+
+def distance(point1, point2):
+    """
+    计算两点之间的欧拉距离，支持多维
+    """
+    # distance = 0.0
+    # for a, b in zip(point1, point2):
+    #     distance += math.pow(a - b, 2)
+    # return math.sqrt(distance)
+    # return np.sqrt(np.sum((point1 - point2) ** 2))
+    # return np.sqrt(np.sum((point1 - point2) ** 2))
+    return np.linalg.norm(point1-point2,ord=1)
+
+
+def get_closest_dist(point, centroids):
+    min_dist = math.inf  # 初始设为无穷大
+    for i, centroid in enumerate(centroids):
+        dist = distance(centroid, point)
+        if dist < min_dist:
+            min_dist = dist
+    return min_dist
+
+
+def kpp_centers(data_set: list, k: int) -> list:
+    """
+    从数据集中返回 k 个对象可作为质心
+    """
+    cluster_centers = []
+    cluster_centers.append(random.choice(data_set))
+    d = [0 for _ in range(len(data_set))]
+    for _ in range(1, k):
+        total = 0.0
+        for i, point in enumerate(data_set):
+            d[i] = get_closest_dist(point, cluster_centers) # 与最近一个聚类中心的距离
+            total += d[i]
+        total *= random.random()
+        for i, di in enumerate(d): # 轮盘法选出下一个聚类中心；
+            total -= di
+            if total > 0:
+                continue
+            cluster_centers.append(data_set[i])
+            break
+    return cluster_centers
+
+
+def point_avg(points):
+    '''
+    Accepts a list of points, each with the same number of dimensions.
+    NB. points can have more dimensions than 2
+    Returns a new points which is the center of all the points
+    :param points:
+    :return:
+    '''
+    dimensions = len(points[0])
+
+    new_center = []
+    points = np.array(points)
+    # for dimension in range(dimensions):
+    #     dim_sum = 0
+    #     for p in points:
+    #         dim_sum += p[dimension]
+    #
+    #     # average of each dimension
+    #     new_center.append(dim_sum / float(len(points)))
+
+    return np.mean(points,axis=0)[0]
+
+
+def update_centers(date_set, assignments):
+    '''
+    Accepts a dataset and a list of assignments; the indexes of both lists correspond
+    to each other.
[…]

### 2020-01-07 code/CriticalPathPruning/run.py

@@ -4,6 +4,9 @@ import json
 from CIFAR_DataLoader import CifarDataManager, display_cifar
 from vggNet import Model, NameMapping
 import argparse
+import warnings
+warnings.filterwarnings("ignore")
+
 
 '''
 Configuration:
@@ -156,6 +159,12 @@ if __name__ == '__main__':
     parser.add_argument(
         "--verbose", help="Print messages.",
         default=True, type=bool_string)
+    parser.add_argument(
+        "--save_folder", help="folder to save results",
+        default=None, type=str)
+    parser.add_argument(
+        "--mode", help="'train' or 'test' data",
+        default="train", type=str)
 
     args = parser.parse_args()
     assert args.dataset in ['imagenet', 'cifar'], "--dataset can only be 'imagenet' or 'cifar'."
@@ -171,13 +180,16 @@ if __name__ == '__main__':
     for i in range(args.begin_class, args.end_class+1):
         print("Current class: {}".format(i))
         print("Gnerating data...")
-        train_images, train_labels = d.train.generateSpecializedData(class_id=i, count=args.max_samples)
+        if args.mode == "train":
+            train_images, train_labels = d.train.generateSpecializedData(class_id=i, count=args.max_samples)
+        else:
+            train_images, train_labels = d.test.generateSpecializedData(class_id=i, count=args.max_samples)
         print("Encoding data...")
         if args.dataset == 'cifar':
-            model.encode_class_data(i, train_images)
+            model.encode_class_data(i, train_images,save_folder = args.save_folder)
         elif args.dataset == 'imagenet':
             model.encode_class_data(i, train_images, "vgg-imagenet/vgg16-imagenet.ckpt", NameMapping.imagenet_mapping_,
                                     use_batch_norm=False, with_bias=True, vgg_type='D', output_size=1000,
-                                    dataset_name='imagenet', verbose=args.verbose)
+                                    dataset_name='imagenet', verbose=args.verbose, save_folder = args.save_folder)
         print("Encoding class...")
-        calculate_total_by_weights(i, size=args.max_samples, dataset=args.dataset)
+        #calculate_total_by_weights(i, size=args.max_samples, dataset=args.dataset)

### 2020-01-07 code/CriticalPathPruning/run_finetune.py

@@ -1,6 +1,7 @@
 from vggFinetuneModel import FineTuneModel
 from CIFAR_DataLoader import CifarDataManager
 import numpy as np
+import argparse
 
 '''
 For fine tune model, the data label should be different:
@@ -24,18 +25,47 @@ def modify_label(labels, test_classes = [0]):
             tmp_labels.append(len(test_classes))
     return one_hot(tmp_labels, vals=len(test_classes)+1)
 
+
+parser = argparse.ArgumentParser("run finetune")
+parser.add_argument(
+    "--mode", help="run finetune for 'class' or 'cluster' CDRP classifier",
+    type=str)
+args = parser.parse_args()
+
+mode = args.mode
+assert mode in ["class","cluster"]
+
 data_loader = CifarDataManager()
 
-test_images, test_labels = data_loader.test.next_batch_without_onehot(500)
+class_ids = [0]
+cluster_ids = [137]
 
-test_labels = modify_label(test_labels, test_classes = [0, 1, 2, 3, 4, 5, 6, 7, 8, 9])
+# test_images, test_labels = data_loader.test.next_batch_balance_without_onehot(200,class_ids)
 
-model = FineTuneModel(target_class_id=[0, 1, 2, 3, 4, 5, 6, 7, 8, 9])
+if mode == "class":
+    target_ids = class_ids
+else:
+    target_ids = cluster_ids
+if mode == "class":
+    test_images, test_labels = data_loader.test.next_batch_balance_without_onehot(200, class_ids, mode=mode)
+else:
+    test_images, test_labels = data_loader.test.next_batch_balance_without_onehot(200,class_ids,mode = mode,type="test")
+test_labels = modify_label(test_labels, test_classes = target_ids)
+
+model = FineTuneModel(target_class_id=class_ids,target_cluster_id = cluster_ids, mode = mode)
 model.assign_weight()
 model.test_accuracy(test_images, test_labels)
 
-for i in range(10):
-    train_images, train_labels = data_loader.train.next_batch_without_onehot(200)
-    train_labels = modify_label(train_labels, test_classes = [0, 1, 2, 3, 4, 5, 6, 7, 8, 9])
+for i in range(1000):
+    print(i)
+    train_images, train_labels = data_loader.train.next_batch_balance_without_onehot(200,class_ids,mode = mode)
+    # train_images, train_labels = data_loader.train.next_batch_without_onehot(100)
+
+    train_labels = modify_label(train_labels, test_classes = target_ids)
+
[…]

### 2020-01-07 code/CriticalPathPruning/trim_and_test.py

@@ -4,7 +4,7 @@ import numpy as np
 d = CifarDataManager()
 
 
-model = TrimmedModel(target_class_id= np.random.randint(100,size=10),
+model = TrimmedModel(target_class_id=[99],target_cluster_id = [0],mode="class",
                      multiPruning=True)
 
 '''
@@ -12,10 +12,9 @@ Todo List:
     1. Modify the accuracy in trimmed network (Done)
 '''
 for _ in range(50):
-    test_images, test_labels = d.test.next_batch(200)
+    test_images, test_labels = d.test.next_batch_balance(200,[99])
 
     model.test_accuracy_pretrim(test_images, test_labels)
-
     model.assign_weight()
     model.test_accuracy(test_images, test_labels)
     break

### 2020-01-07 code/CriticalPathPruning/vggFinetuneModel.py

@@ -14,11 +14,11 @@ class FineTuneModel():
         1. Last FC layer neurons number would be the target class number + 1
         2. Need to transform the original label to targeted class label
     '''
-    def __init__(self, target_class_id=[0]):
+    def __init__(self, target_class_id=[0], target_cluster_id = [0], mode = "class"):
         '''
         Set hyperparameters
         '''
-        self.learning_rate = 0.01
+        self.learning_rate = 0.1
         self.epoch = 0
         self.prune_ratio = 0.9
 
@@ -30,8 +30,15 @@ class FineTuneModel():
         self.AllGateVariables = dict()
         self.AllGateVariableValues = list()
 
-        self.target_class_id = target_class_id # assign the trim class id 
-        self.target_number = len(target_class_id) + 1
+        self.mode = mode
+        if mode == "class":
+            self.target_id = target_class_id
+            self.target_number = len(target_class_id) + 1
+        else:
+            self.target_id = target_cluster_id
+            self.target_number = len(target_cluster_id) + 1
+
+        self.target_class_id = target_class_id # assign the trim class id
 
         self.graph = tf.Graph()
         self.build_model(self.graph)
@@ -42,32 +49,57 @@ class FineTuneModel():
     Test Accuracy
     '''
     def test_accuracy(self, test_images, test_labels):
-        accuracy = self.sess.run(
-            self.accuracy, feed_dict={
+
+        accuracy,ys_pred_argmax = self.sess.run(
+            [self.accuracy,self.ys_pred_argmax], feed_dict={
             self.xs: test_images,
             self.ys_orig: test_labels, 
             self.lr : 0.1,
             self.is_training: False,
-            self.keep_prob: 1.0
+            self.keep_prob: 1.0,
         }) 
 
-        print("Test Accuracy:" + str(accuracy))
+        new_test_labels = []
+        for item in test_labels:
+            if item[0]>item[1]:
+                new_test_labels.append(0)
+            else:
+                new_test_labels.append(1)
+        new_test_labels = np.array(new_test_labels)
 
+        p = new_test_labels==0
+        n = new_test_labels==1
+
+        p_label = new_test_labels[p]
+        p_pred = ys_pred_argmax[p]
+        n_label = new_test_labels[n]
+        n_pred = ys_pred_argmax[n]
+
+        tp = sum(p_label == p_pred)
+        fp = sum(p) - tp
+        tn = sum(n_label == n_pred)
+        fn = sum(n) - tn
+
[…]

### 2020-01-07 code/CriticalPathPruning/vggNet.py

@@ -9,7 +9,7 @@ from sklearn.utils import shuffle
 import os
 
 
-os.environ["CUDA_VISIBLE_DEVICES"] = "0, 1"
+os.environ["CUDA_VISIBLE_DEVICES"] = "6"
 
 
 class NameMapping:
@@ -114,7 +114,7 @@ class Model():
 
     def encode_class_data(self, class_id, train_images, checkpoint_path="vggNet/augmentation.ckpt-120",
                           name_mapping=None, use_batch_norm=True, with_bias=False, vgg_type='C', output_size=100,
-                          dataset_name='cifar', verbose=True):
+                          dataset_name='cifar', verbose=True,save_folder = None):
         self.use_batch_norm = use_batch_norm
         self.with_bias = with_bias
         self.vgg_type = vgg_type
@@ -128,7 +128,15 @@ class Model():
             generatedGate = self.compute_encoding(train_images[i].reshape((1, 32, 32, 3)),
                                                   checkpoint_path, name_mapping, output_size)
             picname = "class" + str(class_id) + "-pic" + str(i)
-            jsonpath = "./ImageEncoding/" + picname + ".json"
+            if save_folder == None:
+                if dataset_name == 'imagenet':
+                    save_folder = "imagenet-ImageEncoding"
+                else:
+                    save_folder = "ImageEncoding"
+            if dataset_name == 'imagenet':
+                jsonpath = "./"+save_folder+"/" + picname + ".json"
+            else:
+                jsonpath = "./"+save_folder+"/" + picname + ".json"
             with open(jsonpath, 'w') as f:
                 json.dump(generatedGate, f, sort_keys=True, indent=4, separators=(',', ':'))
 
@@ -298,7 +306,7 @@ class Model():
         })
 
         tmpLoss = 1000
-        for epoch in range(100):
+        for epoch in range(150):
             if epoch == 50:
                 learning_rate /= 10
                 # L1_loss_penalty *= 10
@@ -312,7 +320,7 @@ class Model():
                 self.penalty: L1_loss_penalty
             })
 
-            [cross_entropy, L1_loss, accuracy] = self.sess.run([self.cross_entropy, self.l1_loss, self.accuracy],
+            [cross_entropy, L1_loss, accuracy, ys_orig] = self.sess.run([self.cross_entropy, self.l1_loss, self.accuracy,self.ys_orig],
                                                                feed_dict={
                                                                    self.xs: input_data,
                                                                    self.ys_orig: label_orig,
@@ -321,6 +329,7 @@ class Model():
[…]

### 2020-01-07 code/CriticalPathPruning/vggTrimmedModel.py

@@ -18,25 +18,33 @@ class TrimmedModel():
         2. Assign new weights to layers 
         3. Test Accuracy
     '''
-    def __init__(self,target_class_id=[0], multiPruning=False):
-        self.prune_ratio = 0.9
+    def __init__(self,target_class_id=[0],target_cluster_id=[0], mode = 'cluster',multiPruning=False):
+        self.prune_ratio = 0
 
         self.graph = tf.Graph()
         self.build_model(self.graph)
         print("restored the pretrained model......")
         self.restore_model(self.graph)
-        
-        self.target_class_id = target_class_id # assign the trim class id 
+        self.mode = mode
+        if self.mode=="cluster":
+            self.target_id = target_cluster_id
+        else:
+            self.target_id = target_class_id
+        self.target_cluster_id = target_cluster_id
+        self.target_class_id = target_class_id # assign the trim class id
         self.multiPruning = multiPruning # ready to prune for one single class or multi classes
         # self.close_sess()
     
     '''
     Find mask class unit
     '''
-    def mask_class_unit(self, classid):
+    def mask_unit(self, classid):
         self.test_counter = 0
         theshold = 10
-        json_path = "./ClassEncoding/class" + str(classid) + ".json"
+        if self.mode == "class":
+            json_path = "./ClassEncoding/class" + str(classid) + ".json"
+        else:
+            json_path = "./ClusterEncoding/cluster" + str(classid) + ".json"
         with open(json_path, "r") as f:
             gatesValueDict = json.load(f)
             for idx in range(len(gatesValueDict)):
@@ -56,13 +64,16 @@ class TrimmedModel():
 
             return gatesValueDict
 
+
     '''
     mask by value
     '''
     def mask_unit_by_value(self, classid):
         formulizedDict = {}
-        json_path = "./ClassEncoding/class" + str(classid) + ".json"
-        
+        if self.mode=="class":
+            json_path = "./ClassEncoding/class" + str(classid) + ".json"
+        else:
+            json_path = "./ClusterEncoding/cluster" + str(classid) + ".json"
         allGatesValue = []
 
         with open(json_path, "r") as f:
@@ -74,7 +85,7 @@ class TrimmedModel():
                 allGatesValue += vec
                 
         allGatesValue.sort()
-        allGatesValue = allGatesValue[:int(len(allGatesValue)*0.8)]
[…]

### 2020-01-07 code/classifier_fusion.py

@@ -1,0 +1,108 @@
+import json
+import math
+import argparse
+from queue import PriorityQueue
+
+
+class Element(object):
+    def __init__(self, priority, description):
+        self.priority = priority
+        self.description = description
+
+    def __lt__(self, other):
+        return self.priority < other.priority
+
+    def get_value(self):
+        return self.description
+
+
+def check(used,encodings):
+    for code in encodings:
+        if len(encodings[code])>1:
+            return False
+    return True
+
+
+def renew(classifier,used,encodings):
+    pos = classifer_label[classifier][0]
+    neg = classifer_label[classifier][1]
+    new_used = used + [classifier]
+    new_encodings = {}
+    other_pos = set()
+    for classifier_id in classifier_ids-set(used)-{classifier}:
+        other_pos = other_pos | classifer_label[classifier_id][0]
+    for key,label_set in encodings.items():
+        if pos & label_set == set() or neg & label_set == set() or len(label_set)==1:
+            code = key + "2"
+            new_encodings[code] = label_set
+            continue
+        code1 = key + "0"
+        new_encodings[code1] = label_set & pos
+        code2 = key + "1"
+        new_encodings[code2] = label_set & neg & other_pos
+    return new_used,new_encodings
+
+
+def calculate_entropy(classifier,used,encodings):
+    new_used, new_encodings = renew(classifier,used,encodings)
+    entropy = 0
+    for key in new_encodings:
+        p = 1
+        for i in range(len(key)):
+            classifier_id = new_used[i]
+            if key[i] == "0":
+                p = p * classifier_poss[classifier_id]
+            if key[i] == "1":
+                p = p * (1 - classifier_poss[classifier_id])
+            if key[i] == "2":
+                p = p * 1
+            entropy += p * math.log(len(new_encodings[key]),2)
+    return entropy
+
+
+def heuristic_search(used,encodings):
+    # print(used,encodings)
+    if check(used,encodings):
+        return used,encodings,True
+    if len(used)==k:
+        return used,encodings,False
+    pq = PriorityQueue()
+    for classifier in classifier_ids-set(used):
+        entropy = calculate_entropy(classifier,used,encodings)
+        pq.put(Element(entropy, classifier))
+    while not pq.empty():
+        classifier = pq.get()
+        classifier = classifier.get_value()
+        new_used, new_encodings = renew(classifier,used,encodings)
[…]

### 2020-01-07 code/cluster_label.py

@@ -1,0 +1,49 @@
+import json
+
+
+if __name__=="__main__":
+    with open("data/sub_encoding.txt","r") as file:
+        sub_encoding = file.readlines()
+    cluster_label = {}
+    for l in sub_encoding:
+        line = l.strip().split()
+        cluster = int(float(line[0]))
+        label = int(float(line[1]))
+        if cluster not in cluster_label:
+            cluster_label[cluster] = {label:1}
+        else:
+            if label in cluster_label[cluster]:
+                cluster_label[cluster][label] += 1
+            else:
+                cluster_label[cluster][label] = 1
+    keys = cluster_label
+    clusters = {}
+    for key in keys:
+        clusters[key] = {}
+        labels = sorted(cluster_label[key],key=cluster_label[key].__getitem__,reverse=True)
+        for label in labels:
+            clusters[key][label] =  cluster_label[key][label]
+    cluster_label = clusters
+
+
+    classifier_label = {}
+
+    for key in cluster_label:
+        cluster_keys = list(cluster_label[key].keys())
+        cluster_size = sum(list(cluster_label[key].values()))
+        if cluster_size<500*100/len(cluster_label)/5:
+            continue
+        tmp1 = []
+        tmp2 = []
+        for label in cluster_keys:
+            if cluster_label[key][label]/cluster_size >0.05:
+                tmp1.append(label)
+                if cluster_label[key][label]<500*0.95:
+                    tmp2.append(label)
+        others = list(set(range(100))-set(tmp1))
+        tmp2 += others
+        classifier_label[key] = (tmp1,tmp2,cluster_size/(500*100))
+        # cluster_label[key] = sorted(cluster_label[key],key=cluster_label[key].__getitem__,reverse=True)
+        print(key,cluster_label[key],classifier_label[key])
+    with open("classifier.json","w") as file:
+        json.dump(classifier_label,file)

### 2020-01-07 code/cluster_predictor.py

@@ -1,0 +1,71 @@
+import pickle
+import json
+from copy import deepcopy
+from sklearn.cluster import KMeans, MiniBatchKMeans
+from utils import *
+from CriticalPathPruning.CIFAR_DataLoader import CifarDataManager, display_cifar
+# from subclass_encoder import SubclassEncoder
+import sys
+
+
+if __name__ == '__main__':
+    parser = argparse.ArgumentParser("Cluster predictor")
+    parser.add_argument(
+        "--encoder_save_path", help="The file to save the encoder.",
+        default="data/encoder.pkl", type=str)
+    parser.add_argument(
+        "--start_class", help="start class of predictor",
+        default=0, type=int
+    )
+    parser.add_argument(
+        "--end_class", help="end class of predictor",
+        default=99, type=int
+    )
+    args = parser.parse_args()
+
+
+    # with open(args.encoder_save_path, "rb") as file:
+    #     encoder = pickle.load(file)
+    with open("data/sub_encoding.txt") as file:
+        sub_encoding = file.readlines()
+    classid_cluster = {}
+    for l in sub_encoding:
+        line = l.strip()
+        line = line.split(" ")
+        if len(line)<2:
+            continue
+        label = int(line[1][0])
+        cluster = int(line[0][0])
+        if label in classid_cluster:
+            classid_cluster[label].append(cluster)
+        else:
+            classid_cluster[label] = [cluster]
+
+    class_counter = {}
+    class_clusters = {}
+    for class_id in range(args.start_class,args.end_class+1):
+        class_counter[class_id] = 0
+        class_clusters[class_id] = []
+
+    data_loader = CifarDataManager()
+
+    batch_size = 100
+    clusters = []
+    for _ in range(500*1000//batch_size):
+        train_images, train_labels = data_loader.train.next_batch_without_onehot(batch_size)
+        for i in range(batch_size):
+            label = train_labels[i]
+            if label<args.start_class or label>args.end_class:
+                continue
+            clusters.append(classid_cluster[label][class_counter[label]])
+            class_clusters[label].append(classid_cluster[label][class_counter[label]])
+            class_counter[label] += 1
+
+    with open("data/clusters.pkl","wb") as file:
+        pickle.dump(clusters,file)
+    with open("data/class_clusters.pkl","wb") as file:
+        pickle.dump(class_clusters,file)
+
+
+
+

### 2020-01-08 code/CriticalPathPruning/run.py
update code to train CDRP for vgg16-D

@@ -169,7 +169,7 @@ if __name__ == '__main__':
     args = parser.parse_args()
     assert args.dataset in ['imagenet', 'cifar'], "--dataset can only be 'imagenet' or 'cifar'."
 
-    d = CifarDataManager()
+    d = CifarDataManager(load_cluster=False)
     model = Model(
         learning_rate=args.learning_rate,
         L1_loss_penalty=args.l1_loss_penalty,
@@ -188,8 +188,8 @@ if __name__ == '__main__':
         if args.dataset == 'cifar':
             model.encode_class_data(i, train_images,save_folder = args.save_folder)
         elif args.dataset == 'imagenet':
-            model.encode_class_data(i, train_images, "vgg-imagenet/vgg16-imagenet.ckpt", NameMapping.imagenet_mapping_,
-                                    use_batch_norm=False, with_bias=True, vgg_type='D', output_size=1000,
+            model.encode_class_data(i, train_images, "vgg16-d/best.ckpt", NameMapping.default_mapping_,
+                                    use_batch_norm=False, with_bias=True, vgg_type='D', output_size=100,
                                     dataset_name='imagenet', verbose=args.verbose, save_folder = args.save_folder)
         print("Encoding class...")
         #calculate_total_by_weights(i, size=args.max_samples, dataset=args.dataset)

### 2020-01-08 code/CriticalPathPruning/vggNet.py

@@ -9,7 +9,7 @@ from sklearn.utils import shuffle
 import os
 
 
-os.environ["CUDA_VISIBLE_DEVICES"] = "6"
+os.environ["CUDA_VISIBLE_DEVICES"] = "0"
 
 
 class NameMapping:
@@ -18,6 +18,10 @@ class NameMapping:
     def default_mapping_(name):
         # print(name, name[:-2])
         return name[:-2]
+
+    @staticmethod
+    def identity_mapping_(name):
+        return name
 
     @staticmethod
     def imagenet_mapping_(name):
@@ -169,6 +173,7 @@ class Model():
                     name_prefix += ':0'
                     if name_prefix in self.AllGateVariables:
                         continue
+                print(name)
                 savedVariable[name_mapping(name)] = variable
             saver = tf.train.Saver(savedVariable)
             # saver = tf.train.Saver(max_to_keep = None)

### 2020-01-08 paper/paper.tex
write begining of section 3 and some guideline

@@
 
-The table in Figure~\ref{fig:assemble-example-encoding} shows the encoding mentioned in the certificate algorithm.
+The table in Figure~\ref{fig:assemble-example-encoding} shows the encoding mentioned in the certificate algorithm for the intro example in Figure~\ref{fig:assemble-example-venn}.
 If we only use the encoding from $d_1, d_2, d_3$, we find no two subclasses with different labels share the same encoding, and therefore certify the correctness of the feasible solution proposed before.
@@
 
-The search is guided by the residual entropy of target subclasses and dummy subclasses.
+The search is guided by the residual entropy \eqref{eq:entropy} of target subclasses and dummy subclasses.
 \begin{equation}
 	H(C) = \sum_{c \in C} p(c)H(c) = \sum_{c \in C} p(c)\sum_{l \in \mathcal{L}'} p(c, l)\log\frac{1}{p(c, l)}
+	\label{eq:entropy}
 \end{equation}
+where $p(c)$ is the probability for encoding $c$ to occur, and $p(c, l)$ is the probability of a sample having encoding $c$ and label $l$.
+Note that the label ranges over $\mathcal{L}'$, the set of target labels and one dummy label, and all labels that are not target is defined to be equal to the dummy one.
+In each search iteration, the algorithm will choose the classifier set that minimizes the entropy greedily, so that the search could possibly to end with minimum search depth.
+
+\todo{Analysis}
 
@@
 \label{sec:cdrp}
-\subsection{Critical Data Routing Path Model}
-\subsection{CDRP Model Clustering}
+In \cref{sec:assembly}, we have formalized the problem and proposed a general algorithm searching for a feasible solution to a search problem instance.
+In this section, we want to instantiate the assembly problem in a concrete setting.
+To do so, we need to find an efficient way to generate the input to the problem.
+More specifically, we need to find an initial set of binary classifiers with following constrains.
+\begin{itemize}
+	\item The initial set should guarantee at least one feasible solution for some $k$.
+	\item There should exist overlapping subclasses among classifiers to allow multiple choices, i.e., allow removing of redundant feature extractors.
+	\item We can not train a large set of binary classifiers from scratch, because it takes too many prior knowledge and time to get an initial set that have feasible solution with the space for improvements.
+\end{itemize}
+
+\paragraph{Remark.} We do not need to provide the subclasses in the input, because they can be derived from the initial set of classifiers.
+Given encodings under the initial classifier set, samples share the same encoding can be considered as a subclass, and there is no need to further split those subclasses.
+For example, in the intro example in Figure~\ref{fig:assemble-example-venn}, there is no need to distinguish $A_{11}$ and $A_{12}$ and we can group them as a single subclass.
+
+To satisfy the above constraints, we follow the previous work of Wang \textit{et al.} \cite{wang2018interpret} to use critical data routing path (CDRP) for generating the input.
+CDRP clustering allow us to decompose a large network model into several disjoint small ones.
+To have overlapping classifiers, we decompose two different networks on the same dataset and fine tuning the CDRP models into binary classifiers.
+We use image classification task on CIFAR-100 and VGG16 of type C and D for demonstration.
+
+\subsection{CDRP Decomposition and Clustering}
+Guideline:
+\begin{itemize}
+	\item How to train gates, the functionality of the gates, how to interpret gate weight (lambda) feature of samples (similar to original paper)
+	\item How to get decomposed classifiers: clustering
+	\item Why clustered CDRP models might work (PCA visualization demonstration) (not performance analysis, inference experiments later)
+	\item Why fine tuning the clustered CDRP model into binary classifiers, and how we fine tune them
+\end{itemize}
+
 \subsection{CDRP Model Assembly}
@@
 \section{Experiments}
-\subsection{CDRP Models of VGGNet and ? trained on CIFAR-100}
-\subsection{Fusing VGGNet and ? for Specific Tasks through CDRP Assembly}
+\subsection{Verifying CDRP Models of VGGNets trained on CIFAR-100}
+\subsection{Fusing VGGNets for Specific Tasks through CDRP Assembly}
 

### 2020-01-09 code/vgg16-imagenet/CIFAR_DataLoader.py
vgg16-imagenet retrain

@@ -1,0 +1,135 @@
+# -*- coding: utf-8 -*-
+import tensorflow as tf
+import numpy as np
+import matplotlib.pyplot as plt
+import os
+import random
+import _pickle as cPickle
+import pickle
+
+# =============== Define Data Loader ===============
+''' Utility Functions '''
+DATA_PATH = "../CriticalPathPruning/cifar-100-python"
+
+def unpickle(file):
+    with open(os.path.join(DATA_PATH, file), 'rb') as fo:
+        dict = cPickle.load(fo, encoding='latin1')
+        return dict
+
+def one_hot(vec, vals=10):
+    n = len(vec)
+    out = np.zeros((n, vals))
+    out[range(n), vec] = 1
+    return out
+
+class CifarLoader(object):
+    def __init__(self, sourcefiles):
+        self._source = sourcefiles
+        self._i = 0
+
+        self.images = None
+        self.labels = None
+        self.class_image = None
+        self.class_label = None
+
+    def load(self):
+        data = [unpickle(f) for f in self._source]
+        images = np.vstack(d["data"] for d in data)
+
+        n = len(images)
+        self.images = images.reshape(n, 3, 32, 32).transpose(0, 2, 3, 1).astype(float)
+        # self.labels = one_hot(np.hstack([d["fine_labels"] for d in data]), 100)
+        self.labels = np.hstack([d["fine_labels"] for d in data])
+        self.images = self.normalize_images(self.images)
+
+        self.class_image = []
+        self.class_label = []
+        for id in range(100):
+            self.class_label.append(list(self.labels[self.labels==id]))
+            self.class_image.append(list(self.images[self.labels == id]))
+
+        # self.class_label = np.array(self.class_label)
+        # self.class_image = np.array(self.class_image)
+        return self
+
+    def next_batch(self, batch_size):
+        x, y = self.images[self._i:self._i+batch_size], self.labels[self._i:self._i+batch_size]
+        self._i = (self._i + batch_size) % len(self.images)
+        return x, one_hot(y, 100)
+
+    def next_batch_without_onehot(self, batch_size):
+        x, y = self.images[self._i:self._i+batch_size], self.labels[self._i:self._i+batch_size]
+        self._i = (self._i + batch_size) % len(self.images)
+        return x, y
+
+    def generateSpecializedData(self, class_id, count = 500):
+        train_index = []
+
[…]

### 2020-01-09 code/vgg16-imagenet/run.py

@@ -1,0 +1,35 @@
+from vgg16 import Model, NameMapping
+import numpy as np
+import argparse
+import os
+import sys
+import tensorflow as tf
+from CIFAR_DataLoader import CifarDataManager
+
+data_loader = CifarDataManager()
+model = Model()
+checkpoint_path = "vgg-imagenet/vgg16-imagenet.ckpt"
+name_mapping = NameMapping.imagenet_mapping_
+output_size = 100
+
+print("Restoring network...")
+graph = tf.Graph()
+model.build_model(graph, output_size)
+model.restore_model(graph, checkpoint_path, name_mapping)
+
+max_acc = 0
+
+for i in range(1000):
+    print(i)
+    train_images, train_labels = data_loader.train.next_batch(200)
+    model.train_model(train_images, train_labels)
+    test_images, test_labels = data_loader.test.next_batch(200)
+    cur_acc = model.test_accuracy(test_images, test_labels)
+    if i % 100 == 0:
+        model.save_ckpt()
+        if cur_acc > max_acc:
+            model.save_ckpt('best')
+            max_acc = cur_acc
+
+
+model.close_sess()

### 2020-01-09 code/vgg16-imagenet/vgg16.py

@@ -1,0 +1,345 @@
+import pickle
+import random
+import json
+import numpy as np
+import tensorflow as tf
+import os
+
+
+os.environ["CUDA_VISIBLE_DEVICES"] = "0"
+
+
+class NameMapping:
+    # Network name mappings
+    @staticmethod
+    def default_mapping_(name):
+        # print(name, name[:-2])
+        return name[:-2]
+
+    @staticmethod
+    def imagenet_mapping_(name):
+        variable_dict = {
+            "Conv1/composite_function/kernel:0": "block1_conv1/kernel",
+            "Conv1/composite_function/bias:0": "block1_conv1/bias",
+            "Conv2/composite_function/kernel:0": "block1_conv2/kernel",
+            "Conv2/composite_function/bias:0": "block1_conv2/bias",
+            "Conv3/composite_function/kernel:0": "block2_conv1/kernel",
+            "Conv3/composite_function/bias:0": "block2_conv1/bias",
+            "Conv4/composite_function/kernel:0": "block2_conv2/kernel",
+            "Conv4/composite_function/bias:0": "block2_conv2/bias",
+            "Conv5/composite_function/kernel:0": "block3_conv1/kernel",
+            "Conv5/composite_function/bias:0": "block3_conv1/bias",
+            "Conv6/composite_function/kernel:0": "block3_conv2/kernel",
+            "Conv6/composite_function/bias:0": "block3_conv2/bias",
+            "Conv7/composite_function/kernel:0": "block3_conv3/kernel",
+            "Conv7/composite_function/bias:0": "block3_conv3/bias",
+            "Conv8/composite_function/kernel:0": "block4_conv1/kernel",
+            "Conv8/composite_function/bias:0": "block4_conv1/bias",
+            "Conv9/composite_function/kernel:0": "block4_conv2/kernel",
+            "Conv9/composite_function/bias:0": "block4_conv2/bias",
+            "Conv10/composite_function/kernel:0": "block4_conv3/kernel",
+            "Conv10/composite_function/bias:0": "block4_conv3/bias",
+            "Conv11/composite_function/kernel:0": "block5_conv1/kernel",
+            "Conv11/composite_function/bias:0": "block5_conv1/bias",
+            "Conv12/composite_function/kernel:0": "block5_conv2/kernel",
+            "Conv12/composite_function/bias:0": "block5_conv2/bias",
[…]

### 2020-01-09 paper/paper.tex

@@
 
+\todo{metion CIFAR-5}
 \subsection{CDRP Model Assembly}
+Based on the results of CDRP decomposition in VGG16-C and VGG16-D, we determine subclasses for CIFAR-5 and their relationship to the CDRP clusters by encoding samples using all CDRP models.
+Instead of using Venn diagram like the intro example in Figure~\ref{fig:assemble-example-venn}, we use the network diagram in Figure~\ref{fig:network-venn} to represent the relationship between subclasses and clusters.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\linewidth]{fig/network_venn.png}
+	\caption{Network Venn Diagram for CIFAR-5}
+	\label{fig:network-venn}
+\end{figure}
+
+The cluster nodes (boxes) on the right side of the figure represent CDRP clusters in VGG16-C, and those on the left side represent clusters in VGG16-D.
+The subclass nodes (circles) in the middle represent subclasses, the size of which indicate the number of samples belonging to the subclass and the color of which indicate the label assigned to it.
+A subclass node is connected with a cluster node iff. the subclass is a subset of the cluster.
+
+Since we decompose two networks into two sets of internally disjoint clusters, each subclass will fall into exactly two clusters from separate models.
+In other word, the encoding for a subclass is a two-hot encoding.
+\todo{This means that the assembly problem can be solved with more efficient algorithms.}
 

### 2020-01-10 paper/paper.tex
Update paper.tex

@@
                         %% http://ctan.org/pkg/booktabs
-\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
+\usepackage{subfigure} %% For complex figures with subfigures/subcaptions
                         %% http://ctan.org/pkg/subcaption
@@
 \label{sec:assembly-algorithm}
-Based on the encoding method, we propose a search algorithm based on greedy heuristics in Table~\ref{tab:heuristic-search} for finding a feasible solution to the problem instance with constraint $k$.
+Based on the encoding method, we propose a search algorithm based on greedy heuristics in Algorithm~\ref{tab:heuristic-search} for finding a feasible solution to the problem instance with constraint $k$.
 
@@
 \subsection{Verifying CDRP Models of VGGNets trained on CIFAR-100}
+\paragraph{Clusters.} We perform K-Means on the CDRP control gates of each sample. 
+For VGGNet, we generate $1.5$ clusters per class.
+Then, we get $14$ clusters from $5$ classes, among which $7$ clusters are from VGG16-C and $7$ clusters from VGG16-D.
+
+The sample distribution of each cluster is shown in Figure~\ref{fig:vgg-cluster}.
+
+\begin{figure}[!htp]
+    \centering
+\subfigure[Clusters from VGG-C]{
+    \begin{minipage}[t]{1\linewidth}
+        \includegraphics[height=1.5in,width=2.8in]{fig/chart1.pdf}
+        \label{fig:net2a}
+    \end{minipage}
+}
+
+    %\vfill
+\subfigure[Clusters from VGG-D]{
+    \begin{minipage}[t]{1\linewidth}
+        \includegraphics[height=1.5in,width=2.8in]{fig/chart2.pdf}
+        \label{fig:net2b}
+    \end{minipage}
+}
+    \caption{Sample Distribution of Clusters from Different Types of VGGNets}
+    \label{fig:vgg-cluster}
+
+\end{figure}
+
+From Figure~\ref{fig:vgg-cluster}, a cluster from VGG-C typically consists of samples from a single class, which is consistent with the result shown in Figure~\ref{}. 
+By contrast, a cluster from VGG-D may contain samples with different labels.
+
+We notice that some clusters only contain extremely few samples such as Cluster-5 so we won't take these clusters into account when choosing classifiers.
+
+\paragraph{Classifiers.} Except some too small ones, we consider one cluster as a classifer. Each classifier judges whether the test sample should in the corresponding cluster. 
+From Figure~\ref{fig:vgg-cluster}, we determine the possibile labels of samples in each cluster as is shown in Table~\ref{tab:cluster_label}.
+
+\begin{table}[!htp]
+	\begin{tabular}{|c|c|c|}
+	\hline
+	\multirow{2}{*}{Classifier} &\multicolumn{2}{|c|}{Possible Class Labels}\\
+	\cline{2-3}
+	& In (0) & Not in (1)\\
+	\hline
+	classifier-0,6 & 4 & 0,1,2,3,4,5\\
+	classifier-1 & 1 & 0,2,3,4,5\\
+	classifier-2 & 2 & 0,1,3,4,5\\
+	classifier-3 & 0 & 1,2,3,4,5\\
+	classifier-4 & 3 & 0,1,2,4,5\\
+	classifier-7 & 3,4 & 0,1,2,3,4,5\\ 
+	classifier-9 & 2,3,4 & 0,1,5\\ 
+	classifier-8,13 & 0 & 1,2,3,4,5\\
+	classifier-10,12 & 1 & 0,1,2,3,4,5\\
+	classifier-11 & 3 & 0,1,2,3,4,5\\
+	\hline
+
+	\end{tabular}
+	\caption{Corresponding Class Labels of Each Cluster}
+	\label{tab:cluster_label}
+\end{table}
+
+Since we want to get 0/1-classifiers, we slightly change the original VGGNet architecture in output dimension of the last Fully-Connected Layer from $100$ to $2$. 
+We also prune the original full VGGNet in the guide of CDRP with a prune ratio $0.9$ i.e. $90\%$ of channels in all layers are pruned. 
+As a result, each classifer only has $10\%$ parameters of the original full network.
+
+\paragraph{Finetune.} The classifiers we get above cannot achieve any meaningful results because they tend to classifiy all test samples not in the cluster and the weights of the last layer is initialized randomly.
+We implement finetune on these classifers to make the results more meaningful and accurate. 
+Since the negative samples are greatly more than positive ones in the dataset, we need to implement some strategies to balance them i.e.
+in each iteration we ensure the ratio of positive and negative samples is about $1:1$ in the batch.
+
+We train each classifer with $1500$ iterations with a batch size $200$.
+The learning rate is $0.1$ for the first $1200$ iterations and $0.01$ for the remaining $300$.
+We only train the pruned model i.e.
+weights of the pruned channels will remain zero.
+
 \subsection{Fusing VGGNets for Specific Tasks through CDRP Assembly}

### 2020-01-10 paper/paper.tex
cdrp

--- 2020-01-09 paper/paper.tex
@@
 
+Critical Data Routing Path is a method to find a path containing critical nodes, whose removal causes great preformance setback, from a existing trained model.
+We introduce CDRP to decomposite one existing pretrained model from selecting representing CDRPs in a given dataset.
+
+\paragraph{CDRP extraction}
+
+From the original model, we introduce a scalar control gate to every output channel of one layer, with nonnegative and sparse value.
+They will be multiplied to the layer’s output channelwise, resulting in the routing nodes.
+The nodes that are not suppressed, or have control gate weight greater zero, will be linked together to compose the routing paths.
+Then finding the critical data routing path can be reduced to optimize the weights of the control gates.
+
+Critical data routing path is extracted through optimizaition of control gates values.
+We freeze the weights of the model, and for each sampe we follow the procedure of Distillation Guided Routing (algorithm \ref{alg:dgr}) \cite{wang2018interpret} to get the gate values.
+The gate values can be concatenated into one single vector as representation of that sample.
+
+\begin{algorithm}
+	\caption{Distillation Guided Routing, introduced in paper \cite{wang2018interpret}}
+	\label{alg:dgr}
+	\begin{algorithmic}[1]
+		\Require Input image $\boldsymbol{x}$, pretrained network $f_\theta(\cdot)$, control gates $\boldsymbol{\Lambda}$ initialized with 1, balanced parameter $\gamma$. Max iterations $T$, SGD optimizer
+		\Ensure identified CDRPs representation $\boldsymbol{v}$
+		\State original prediction class $i \gets \arg\max f_\theta(\boldsymbol{x})$
+		\For{$t \gets 1$ to $T$}
+			\State compute loss $cur\_loss$: $$\mathcal{L}\left(f_\theta(\boldsymbol{x}), f_\theta(\boldsymbol{x}; \boldsymbol{\Lambda})\right) + \gamma \sum_k |\boldsymbol{\lambda}_k|_1$$
+			\State compute control gates gradients $\boldsymbol{\Lambda}$: $$\frac{\partial Loss}{\partial \boldsymbol{\Lambda}} = \frac{\partial \mathcal{L}}{\partial \boldsymbol{\Lambda}} + \gamma \times \mathrm{sign}(\boldsymbol{\Lambda})$$
+			\State update $\boldsymbol{\Lambda}$ by SGD optimzier and clip $\boldsymbol{\Lambda}$ to be nonnegative
+			\State new prediction class $j \gets \arg\max f_\theta(\boldsymbol{x};\boldsymbol{\Lambda})$
+			\If{$i=j$} \Comment keep the prediction same
+				\If{$cur\_loss$ is minimun}
+					\State $\boldsymbol{v} \gets \mathrm{concatenate}(\boldsymbol{\Lambda})$
+				\EndIf
+			\EndIf
+		\EndFor		
+	\end{algorithmic}
+\end{algorithm}
+
+\paragraph{CDRP clustering}
+
+Once the gate vectors of all samples is obtained, we use k-means clusterng to cluster these vectors.
+With clustering, we can prune the original model according to the samples within one cluster and produce a smaller model.
+
+\paragraph{Model pruning and fine tuning}
+
+We use methods introduced in paper \cite{LiDongYue} to prune the model according to gate vector of cluster centers (algorithm \ref{alg:prune}).
+
+\begin{algorithm}
+	\caption{Model Pruning of clusters}
+	\label{alg:prune}
+	\begin{algorithmic}[1]
+		\Require input images of one given cluster $TargetImages$, pretrained network $f_\theta(\cdot)$, $prune\_ratio$
+		\Ensure Pruned neural network $f_{\theta'}(\cdot)$
+		\State $Paths = \{\}$
+		\For{each given training image $\boldsymbol{x}$ in $TargetImages$}
+			\State $Path_{\boldsymbol{x}} = \mathrm{DistillationGuidedRouting}(\boldsymbol{x}, f_\theta(\cdot))$
+			\State $Paths.add(Path_{\boldsymbol{x}})$
+		\EndFor		
+		\State compute cluster-wise critical data routing path $SumPath$ via merging $Paths$, resulting gate vector $\boldsymbol{\Lambda} = [\boldsymbol{\lambda}_k]$
+		\For{$\boldsymbol{\lambda}_k$ in the $k$-th convolution layers}
+			\State sort all $\lambda$s in $\boldsymbol{\lambda}_k$ decreasingly and discard the channels in the last within range of $prune\_ration$
+		\EndFor
+	\end{algorithmic}
+\end{algorithm}
+
 \todo{metion CIFAR-5}

### 2020-01-10 paper/paper.tex
Update paper.tex

--- 2020-01-10 paper/paper.tex
@@
 
-The table in Figure~\ref{fig:assemble-example-encoding} shows the encoding mentioned in the certificate algorithm for the intro example in Figure~\ref{fig:assemble-example-venn}.
+Table~\ref{tab:assemble-example-encoding} shows the encoding mentioned in the certificate algorithm for the intro example in Figure~\ref{fig:assemble-example-venn}.
 If we only use the encoding from $d_1, d_2, d_3$, we find no two subclasses with different labels share the same encoding, and therefore certify the correctness of the feasible solution proposed before.
@@
 % \linespread{1.1}
-\begin{figure}[h]
+\begin{table}[h]
 	\begin{tabular}{|c|c|cccc|}
@@
 	\caption{Encoding for the Intro Example}
-	\label{fig:assemble-example-encoding}
-\end{figure}
+	\label{tab:assemble-example-encoding}
+\end{table}
 % \linespread{1.0}
@@
 
-Since we want to get 0/1-classifiers, we slightly change the original VGGNet architecture in output dimension of the last Fully-Connected Layer from $100$ to $2$. 
+Since we want to get binary-classifiers, we slightly change the original VGGNet architecture in output dimension of the last Fully-Connected Layer from $100$ to $2$. 
 We also prune the original full VGGNet in the guide of CDRP with a prune ratio $0.9$ i.e. $90\%$ of channels in all layers are pruned. 
@@
 We train each classifer with $1500$ iterations with a batch size $200$. 
-The learning rate is $0.1$ for the first $1200$ iterations and $0.01$ for the remaining $300$.
-We only train the pruned model i.e.
-weights of the pruned channels will remain zero.
+The learning rate is $0.1$ for the first $1200$ iterations and $0.01$ for the remaining $300$ iterations. 
+We only train the pruned model i.e. weights of the pruned channels will remain zero.
+After finetune, most of the classifers can reach an accuracy more than 80\%, which is much higher than the overall accuracy of the original full network.
 
 \subsection{Fusing VGGNets for Specific Tasks through CDRP Assembly}
+\paragraph{Fusion} We implement the heuristic search in Algorithm~\ref{tab:heuristic-search} to fuse the classifiers. 
+Since we want to finish a specific task of classifying among five classes, we set a upper bound of the number of classifiers $k=4$. 
+After we select these classifiers with this algorithm, different results of each classifier ($0$ and $1$ represent the sample is or isn't in the cluster respectively) correspond to a unique label.
+In our implementation, the algorithm choose four classifiers: 3,4,1,2 in order. 
+The accuracy of the four classifiers are shown in Table~\ref{tab:classifer-accuracy}.The test set has also been balanced to make the number of positive and negative samples nearly $1:1$.
+
+\begin{table}[!htp]
+	\begin{tabular}{|c|c|c|c|c|}
+	\hline
+	& classifier-3 & classifier-4 & classifier-1 & classifier-2 \\
+	\hline
+	Accuracy & 96.0\% & 86.0\% & 91.5\% & 87.0\%\\
+	\hline
+	\end{tabular}
+    \caption{Accuracy of Chosen Binary-Classifiers}
+    \label{tab:classifer-accuracy}
+\end{table}
+
+\paragraph{Verifying Result.}By combining the 0/1-results of the four classifiers, we can determine the class label unqiuely of one test sample.
+For example, if the result of classifer-3 is $0$ whether results of others are all $1$s, the encoding will be $0111$ and we can determine the sample is in class $0$.
+
+Actually, we can determine the class uniquely with the prefix of encodings. 
+For instance, if the result of classifer-3 is $0$, we don't need to take other classifers into consideration since the only class $0$ is possible in cluster-3 according to Table~\ref{tab:cluster_label}
+
+The corresponding encoding of each class label is shown in Table~\ref{tab:encoding-and-accuarcy}.
+We can determine the class label with this encoding, the accuracy of which is also shown in Table~\ref{tab:encoding-and-accuarcy}.
+
+\begin{table}[!htp]
+	\begin{tabular}{|c|c|c|c|c|c|c|}
+	\hline
+	& class-0 & class-1 & class-2 & class-3 & class-4 & Overall \\
+	\hline
+	Encoding &0 & 110 & 1110 &10 & 1111 &\\
+	\hline
+	\end{tabular}
+    \caption{Encoding and Accuracy of Each Class Label}
+    \label{tab:encoding-and-accuarcy}
+\end{table}
 

### 2020-01-10 paper/paper.tex
cdrp

--- 2020-01-10 paper/paper.tex
@@
 
+Afterwards we modify the network architecture of fully connected layers to form a binary classifer $g_{\theta'}(\cdot)$.
+We finetune this model with samples having positive labels in the clusterwhich is used to prune the model, and all other samples having negative labels.
+
 \todo{metion CIFAR-5}

### 2020-01-10 paper/paper.tex
cdrp

@@
 The gate values can be concatenated into one single vector as representation of that sample.
+As the original paper \cite{wang2018interpret} states, these gate values encode patterns inside the input images, e.g.
+tinca in horizontal positions or squat positions will have different encodings.
 
@@
 
-Once the gate vectors of all samples is obtained, we use k-means clusterng to cluster these vectors.
-With clustering, we can prune the original model according to the samples within one cluster and produce a smaller model.
+The fact that CDRP as encoding of samples directly leads to the idea that decompoisite one large model into several smaller models, each of which processing one pattern of input data.
+Once the gate vectors of all samples is obtained, we use k-means clusterng to cluster these vectors to gather samples sharing similar patterns together.
+
+The visualization of clustering results is presented in figure \ref{fig:vgg-cluster-pca}.
+
+\begin{figure}[!htp]
+	\centering
+	\subfigure[Result of VGG-16(C)] {
+		\includegraphics[width=\linewidth]{fig/vgg16c-cluster.png}
+        \label{fig:vgg16c-cluster}
+	}
+	\subfigure[Result of VGG-19(D)] {
+		\includegraphics[width=\linewidth]{fig/vgg16d-cluster.png}
+        \label{fig:vgg16d-cluster}
+    }
+    \caption{Visualization of clustering results.
+The axes are the first two components of of PCA results on all extracted gate vectors.
+The figure in the top is the result of VGG-16 (type C) trained on cifar-100 dataset, and the one below is the result of VGG-16 (type D) fine-tuned on cifar-100 initialized with pretrained weights on ImageNet.
+Different colors represent different class labels in cifar-100 dataset, and the cluster centers are denoted as blue squares.}
+    \label{fig:vgg-cluster-pca}
+\end{figure}
+
+From the visualization result, it can be observed that the clustering can distinguish samples of difference class lables, i.e.
+samples in one cluster are not prone to have different class labels.
+Besides, gate vectors extracted on the same data by different models differs.
+
+The results shows we can derive a good basis of binary classifers through these clusters.
+First, the good mapping from cluster to class label means we can use these binary classifiers to construct subclasses mentioned in the beginning of this section.
+The fact that gate vectors from different models varies will prevent the trival case that cluster one-to-one map to class label, leading to substantial reduction on number of model parameters.
 
@@
 
-Afterwards we modify the network architecture of fully connected layers to form a binary classifer $g_{\theta'}(\cdot)$.
+Afterwards we modify the network architecture of fully connected layers to form a binary classifer $g_{\theta'}(\cdot)$. The reason to do this includes:
+\begin{itemize}
+	\item It has less parameters than 100-class classifers.
+	\item It is easier to train, i.e. easier to have higher accuarcy.
+	\item Weights of convolution layers in the orginal model could be reused. We just need to finetune the model without running long sessions to train from scratch.
+\end{itemize}
+
 We finetune this model with samples having positive labels in the clusterwhich is used to prune the model, and all other samples having negative labels.

### 2020-01-10 paper/paper.tex
cdrp

@@
 
-\todo{metion CIFAR-5}
+%\todo{metion CIFAR-5}
 \subsection{CDRP Model Assembly}
-Based on the results of CDRP decomposition in VGG16-C and VGG16-D, we determine subclasses for CIFAR-5 and their relationship to the CDRP clusters by encoding samples using all CDRP models.
+Based on the results of CDRP decomposition in VGG16-C and VGG16-D, we determine subclasses for CIFAR-5	\footnote{CIFAR-5 is a shorthand refering to samples having the first 5 class labels in CIFAR-100.} and their relationship to the CDRP clusters by encoding samples using all CDRP models.
 Instead of using Venn diagram like the intro example in Figure~\ref{fig:assemble-example-venn}, we use the network diagram in Figure~\ref{fig:network-venn} to represent the relationship between subclasses and clusters.

### 2020-01-10 paper/paper.tex
cdrp fix typo

@@
 
-Critical Data Routing Path is a method to find a path containing critical nodes, whose removal causes great preformance setback, from a existing trained model.
+Critical Data Routing Path is a method to find a path containing critical nodes, whose removal causes great preformance setback, from an existing trained model.
 We introduce CDRP to decomposite one existing pretrained model from selecting representing CDRPs in a given dataset.
@@
 Critical data routing path is extracted through optimizaition of control gates values.
-We freeze the weights of the model, and for each sampe we follow the procedure of Distillation Guided Routing (algorithm \ref{alg:dgr}) \cite{wang2018interpret} to get the gate values.
+We freeze the weights of the model, and for each sample we follow the procedure of Distillation Guided Routing (algorithm \ref{alg:dgr}) \cite{wang2018interpret} to get the gate values.
 The gate values can be concatenated into one single vector as representation of that sample.

### 2020-01-10 paper/paper.tex
some fix

--- 2020-01-10 paper/paper.tex
@@
 
-Table~\ref{tab:assemble-example-encoding} shows the encoding mentioned in the certificate algorithm for the intro example in Figure~\ref{fig:assemble-example-venn}.
+Figure~\ref{fig:assemble-example-encoding} shows the encoding mentioned in the certificate algorithm for the intro example in Figure~\ref{fig:assemble-example-venn}.
 If we only use the encoding from $d_1, d_2, d_3$, we find no two subclasses with different labels share the same encoding, and therefore certify the correctness of the feasible solution proposed before.
@@
 % \linespread{1.1}
-\begin{table}[h]
+\begin{figure}[h]
 	\begin{tabular}{|c|c|cccc|}
@@
 	\caption{Encoding for the Intro Example}
-	\label{tab:assemble-example-encoding}
-\end{table}
+	\label{fig:assemble-example-encoding}
+\end{figure}
 % \linespread{1.0}
@@
 
-\begin{algorithm}
+\begin{algorithm}[h]
 	\caption{The General Algorithm}
@@
 
-Critical Data Routing Path is a method to find a path containing critical nodes, whose removal causes great preformance setback, from a existing trained model.
-We introduce CDRP to decomposite one existing pretrained model from selecting representing CDRPs in a given dataset.
-
-\paragraph{CDRP extraction}
-
-From the original model, we introduce a scalar control gate to every output channel of one layer, with nonnegative and sparse value.
-They will be multiplied to the layer’s output channelwise, resulting in the routing nodes.
-The nodes that are not suppressed, or have control gate weight greater zero, will be linked together to compose the routing paths.
-Then finding the critical data routing path can be reduced to optimize the weights of the control gates.
-
-Critical data routing path is extracted through optimizaition of control gates values.
-We freeze the weights of the model, and for each sampe we follow the procedure of Distillation Guided Routing (algorithm \ref{alg:dgr}) \cite{wang2018interpret} to get the gate values.
-The gate values can be concatenated into one single vector as representation of that sample.
-As the original paper \cite{wang2018interpret} states, these gate values encode patterns inside the input images, e.g.
-tinca in horizontal positions or squat positions will have different encodings.
-
-\begin{algorithm}
-	\caption{Distillation Guided Routing, introduced in paper \cite{wang2018interpret}}
-	\label{alg:dgr}
-	\begin{algorithmic}[1]
-		\Require Input image $\boldsymbol{x}$, pretrained network $f_\theta(\cdot)$, control gates $\boldsymbol{\Lambda}$ initialized with 1, balanced parameter $\gamma$. Max iterations $T$, SGD optimizer
-		\Ensure identified CDRPs representation $\boldsymbol{v}$
-		\State original prediction class $i \gets \arg\max f_\theta(\boldsymbol{x})$
-		\For{$t \gets 1$ to $T$}
-			\State compute loss $cur\_loss$: $$\mathcal{L}\left(f_\theta(\boldsymbol{x}), f_\theta(\boldsymbol{x}; \boldsymbol{\Lambda})\right) + \gamma \sum_k |\boldsymbol{\lambda}_k|_1$$
-			\State compute control gates gradients $\boldsymbol{\Lambda}$: $$\frac{\partial Loss}{\partial \boldsymbol{\Lambda}} = \frac{\partial \mathcal{L}}{\partial \boldsymbol{\Lambda}} + \gamma \times \mathrm{sign}(\boldsymbol{\Lambda})$$
-			\State update $\boldsymbol{\Lambda}$ by SGD optimzier and clip $\boldsymbol{\Lambda}$ to be nonnegative
-			\State new prediction class $j \gets \arg\max f_\theta(\boldsymbol{x};\boldsymbol{\Lambda})$
-			\If{$i=j$} \Comment keep the prediction same
-				\If{$cur\_loss$ is minimun}
-					\State $\boldsymbol{v} \gets \mathrm{concatenate}(\boldsymbol{\Lambda})$
-				\EndIf
-			\EndIf
-		\EndFor		
-	\end{algorithmic}
-\end{algorithm}
-
-\paragraph{CDRP clustering}
-
-The fact that CDRP as encoding of samples directly leads to the idea that decompoisite one large model into several smaller models, each of which processing one pattern of input data.
-Once the gate vectors of all samples is obtained, we use k-means clusterng to cluster these vectors to gather samples sharing similar patterns together.
-
-The visualization of clustering results is presented in figure \ref{fig:vgg-cluster-pca}.
-
-\begin{figure}[!htp]
-	\centering
-	\subfigure[Result of VGG-16(C)] {
-		\includegraphics[width=\linewidth]{fig/vgg16c-cluster.png}
-        \label{fig:vgg16c-cluster}
-	}
-	\subfigure[Result of VGG-19(D)] {
-		\includegraphics[width=\linewidth]{fig/vgg16d-cluster.png}
-        \label{fig:vgg16d-cluster}
-    }
-    \caption{Visualization of clustering results.
-The axes are the first two components of of PCA results on all extracted gate vectors.
-The figure in the top is the result of VGG-16 (type C) trained on cifar-100 dataset, and the one below is the result of VGG-16 (type D) fine-tuned on cifar-100 initialized with pretrained weights on ImageNet.
-Different colors represent different class labels in cifar-100 dataset, and the cluster centers are denoted as blue squares.}
-    \label{fig:vgg-cluster-pca}
-\end{figure}
-
-From the visualization result, it can be observed that the clustering can distinguish samples of difference class lables, i.e.
-samples in one cluster are not prone to have different class labels.
-Besides, gate vectors extracted on the same data by different models differs.
-
-The results shows we can derive a good basis of binary classifers through these clusters.
-First, the good mapping from cluster to class label means we can use these binary classifiers to construct subclasses mentioned in the beginning of this section.
-The fact that gate vectors from different models varies will prevent the trival case that cluster one-to-one map to class label, leading to substantial reduction on number of model parameters.
-
-\paragraph{Model pruning and fine tuning}
-
-We use methods introduced in paper \cite{LiDongYue} to prune the model according to gate vector of cluster centers (algorithm \ref{alg:prune}).
-
-\begin{algorithm}
-	\caption{Model Pruning of clusters}
-	\label{alg:prune}
-	\begin{algorithmic}[1]
-		\Require input images of one given cluster $TargetImages$, pretrained network $f_\theta(\cdot)$, $prune\_ratio$
-		\Ensure Pruned neural network $f_{\theta'}(\cdot)$
-		\State $Paths = \{\}$
-		\For{each given training image $\boldsymbol{x}$ in $TargetImages$}
-			\State $Path_{\boldsymbol{x}} = \mathrm{DistillationGuidedRouting}(\boldsymbol{x}, f_\theta(\cdot))$
-			\State $Paths.add(Path_{\boldsymbol{x}})$
-		\EndFor		
-		\State compute cluster-wise critical data routing path $SumPath$ via merging $Paths$, resulting gate vector $\boldsymbol{\Lambda} = [\boldsymbol{\lambda}_k]$
-		\For{$\boldsymbol{\lambda}_k$ in the $k$-th convolution layers}
-			\State sort all $\lambda$s in $\boldsymbol{\lambda}_k$ decreasingly and discard the channels in the last within range of $prune\_ration$
-		\EndFor
-	\end{algorithmic}
-\end{algorithm}
-
-Afterwards we modify the network architecture of fully connected layers to form a binary classifer $g_{\theta'}(\cdot)$. The reason to do this includes:
-\begin{itemize}
-	\item It has less parameters than 100-class classifers.
-	\item It is easier to train, i.e. easier to have higher accuarcy.
-	\item Weights of convolution layers in the orginal model could be reused. We just need to finetune the model without running long sessions to train from scratch.
-\end{itemize}
-
-We finetune this model with samples having positive labels in the clusterwhich is used to prune the model, and all other samples having negative labels.
-
 \todo{metion CIFAR-5}
@@
 
-\begin{table}[!htp]
+\begin{table}[h]
+	\caption{Corresponding Class Labels of Each Cluster}
+	\label{tab:cluster_label}
 	\begin{tabular}{|c|c|c|}
@@
 	\hline
-
 	\end{tabular}
-	\caption{Corresponding Class Labels of Each Cluster}
-	\label{tab:cluster_label}
 \end{table}
@@
 
-\begin{table}[!htp]
+\begin{table}[h]
+    \caption{Accuracy of Chosen Binary-Classifiers}
+    \label{tab:classifer-accuracy}
 	\begin{tabular}{|c|c|c|c|c|}
 	\hline
-	& classifier-3 & classifier-4 & classifier-1 & classifier-2 \\
+	Classifier ID & 3 & 4 & 1 & 2 \\
 	\hline
@@
 	\end{tabular}
-    \caption{Accuracy of Chosen Binary-Classifiers}
-    \label{tab:classifer-accuracy}
 \end{table}
@@
 
-\begin{table}[!htp]
+\begin{table}[h]
+    \caption{Encoding and Accuracy of Each Class Label}
+    \label{tab:encoding-and-accuarcy}
 	\begin{tabular}{|c|c|c|c|c|c|c|}
 	\hline
-	& class-0 & class-1 & class-2 & class-3 & class-4 & Overall \\
+	Class ID & 0 & 1 & 2 & 3 & 4 & Overall \\
 	\hline
@@
 	\end{tabular}
-    \caption{Encoding and Accuracy of Each Class Label}
-    \label{tab:encoding-and-accuarcy}
 \end{table}

### 2020-01-10 paper/paper.tex
Update paper.tex

--- 2020-01-10 paper/paper.tex
@@
 \usepackage{cuted}
+\usepackage{makecell}
 
@@
 
-Figure~\ref{fig:assemble-example-encoding} shows the encoding mentioned in the certificate algorithm for the intro example in Figure~\ref{fig:assemble-example-venn}.
+Table~\ref{tab:assemble-example-encoding} shows the encoding mentioned in the certificate algorithm for the intro example in Figure~\ref{fig:assemble-example-venn}.
 If we only use the encoding from $d_1, d_2, d_3$, we find no two subclasses with different labels share the same encoding, and therefore certify the correctness of the feasible solution proposed before.
@@
 
-\begin{algorithm}[h]
+\begin{algorithm}
 	\caption{The General Algorithm}
@@
 \subsection{Verifying CDRP Models of VGGNets trained on CIFAR-100}
-\paragraph{Clusters.} We perform K-Means on the CDRP control gates of each sample. 
-For VGGNet, we generate $1.5$ clusters per class.
+In this section, we perform K-Means on the CDRP control gates of each sample.
+For each cluster, we get a binary-classifier to determine whether the test sample should be in the cluster.
+Then, we fine tune each classifier in the CIFAR-100 dataset.
+
+\paragraph{Clusters.} For VGGNet, we generate $1.5$ clusters per class.
 Then, we get $14$ clusters from $5$ classes, among which $7$ clusters are from VGG16-C and $7$ clusters from VGG16-D.
@@
 
-\begin{table}[h]
-	\caption{Corresponding Class Labels of Each Cluster}
-	\label{tab:cluster_label}
+\begin{table}[!htp]
 	\begin{tabular}{|c|c|c|}
@@
 	\hline
+
 	\end{tabular}
+	\caption{Corresponding Class Labels of Each Cluster}
+	\label{tab:cluster_label}
 \end{table}
@@
 Since we want to get binary-classifiers, we slightly change the original VGGNet architecture in output dimension of the last Fully-Connected Layer from $100$ to $2$. 
-We also prune the original full VGGNet in the guide of CDRP with a prune ratio $0.9$ i.e. $90\%$ of channels in all layers are pruned. 
+We also prune the original full VGGNet in the guide of CDRP with a prune ratio $pr$ i.e. if $pr=0.9$, $90\%$ of channels in all layers are pruned. 
 As a result, each classifer only has $10\%$ parameters of the original full network.
@@
 We only train the pruned model i.e. weights of the pruned channels will remain zero.
-After finetune, most of the classifers can reach an accuracy more than 80\%, which is much higher than the overall accuracy of the original full network.
+With a prune ratio $pr\leq0.9$, most of the classifers can reach an accuracy more than 80\% after finetune, which is much higher than the overall accuracy of the original full network.
 
 \subsection{Fusing VGGNets for Specific Tasks through CDRP Assembly}
-\paragraph{Fusion} We implement the heuristic search in Algorithm~\ref{tab:heuristic-search} to fuse the classifiers. 
-Since we want to finish a specific task of classifying among five classes, we set a upper bound of the number of classifiers $k=4$. 
-After we select these classifiers with this algorithm, different results of each classifier ($0$ and $1$ represent the sample is or isn't in the cluster respectively) correspond to a unique label.
+In this section, we implement the heuristic search in Algorithm~\ref{tab:heuristic-search} to fuse the classifiers.
+According to the 0/1 result of each classifer, we can get an unique encoding for each sample, which corresponds to a unqiue label so that we can determine the class of each test sample.
+
+\paragraph{Fusion}We implement Algorithm~\ref{tab:heuristic-search} to fuse the classifiers since we want to finish a specific task of classifying among five classes, we set a upper bound of the number of classifiers $k=4$.
+After we select these classifiers with this Algorithm~\ref{tab:heuristic-search}, different results of each classifier ($0$ and $1$ represent the sample is or isn't in the cluster respectively) correspond to a unique label.
 In our implementation, the algorithm choose four classifiers: 3,4,1,2 in order. 
-The accuracy of the four classifiers are shown in Table~\ref{tab:classifer-accuracy}.The test set has also been balanced to make the number of positive and negative samples nearly $1:1$.
+The accuracy of the four classifiers with different prune ratio is shown in Table~\ref{tab:classifer-accuracy}.The test set has also been balanced to make the number of positive and negative samples nearly $1:1$.
 
-\begin{table}[h]
+\begin{table}[!htp]
     \caption{Accuracy of Chosen Binary-Classifiers}
@@
 	\hline
-	Classifier ID & 3 & 4 & 1 & 2 \\
+	& classifier-3 & classifier-4 & classifier-1 & classifier-2 \\
 	\hline
-	Accuracy & 96.0\% & 86.0\% & 91.5\% & 87.0\%\\
+	\begin{tabular}{c}Accuracy\\pr=0.95\end{tabular} & 62.3\% & 82.3\% & 83.5\% & 67.0\%\\
+	\hline
+	\begin{tabular}{c}Accuracy\\pr=0.9\end{tabular} & 96.0\% & 86.0\% & 91.5\% & 87.0\%\\
+	\hline
+	\begin{tabular}{c}Accuracy\\pr=0.8\end{tabular} & 97.5\% & 80.5\% & 94.5\% & 89.5\%\\
 	\hline
 	\end{tabular}
+
 \end{table}
@@
 
-\begin{table}[h]
+\begin{table}[!htp]
     \caption{Encoding and Accuracy of Each Class Label}
@@
 	\hline
-	Class ID & 0 & 1 & 2 & 3 & 4 & Overall \\
+	& class0 & class1 & class2 & class3 & class4 & overall \\
 	\hline
-	Encoding &0 & 110 & 1110 &10 & 1111 &\\
+	Encoding &0 & 110 & 1110 &10 & 1111 & -\\
 	\hline
+	\begin{tabular}{c}Accuracy\\pr=0.95\end{tabular} & 100\% & 30.0\% & 11.0\% & 28.0\% & 7.0\% & 34.4\%\\
+	\hline
+	\begin{tabular}{c}Accuracy\\pr=0.9\end{tabular} & 92.0\% & 93.0\% & 58.0\% & 85.0\% & 67.0\% & 79.0\%\\
+	\hline
+	\begin{tabular}{c}Accuracy\\pr=0.8\end{tabular} & 95.0\% & 91.0\% & 76.0\% & 78.0\% & 76.0\% & 83.2\%\\
+
+	\hline
+
 	\end{tabular}
+
 \end{table}
+
+From Table~\ref{tab:encoding-and-accuarcy}, we find the overall accuracy is quite high if prune ratio $pr\leq0.9$ while the accuracy drops dramatically when $pr=0.95$ since we prune too much channels or even destroy the connectivity of the network.
+When it comes to the trade-off between parameter number and overall accuracy, it is suitable to set prune ratio $pr=0.9$.
+Compared to the accuracy of original full model in these $5$ classes ($70.57\%$), our classifier not only achieve higher precision but also improve the efficiency.
+When $pr=0.9$, we can inference with the $4$ classifiers in parallel, which can save about $90\%$ computing consumption on a single device.
 

### 2020-01-10 paper/paper.tex
change to cref

--- 2020-01-10 paper/paper.tex
@@
 
-Figure~\ref{fig:assemble-example-venn} shows an example of the assembly problem of our interest.
+\Cref{fig:assemble-example-venn} shows an example of the assembly problem of our interest.
 The original dataset contains 3 classes $A_1, A_2$, and $A_3$, and we are able to decompose each into some subclasses, e.g., $A_1$ is decomposed into two subclasses of samples $A_{11}$ and $A_{12}$.
@@
 
-Figure~\ref{fig:assemble-example-encoding} shows the encoding mentioned in the certificate algorithm for the intro example in Figure~\ref{fig:assemble-example-venn}.
+\Cref{tab:assemble-example-encoding} shows the encoding mentioned in the certificate algorithm for the intro example in \cref{fig:assemble-example-venn}.
 If we only use the encoding from $d_1, d_2, d_3$, we find no two subclasses with different labels share the same encoding, and therefore certify the correctness of the feasible solution proposed before.
@@
 \label{sec:assembly-algorithm}
-Based on the encoding method, we propose a search algorithm based on greedy heuristics in Algorithm~\ref{tab:heuristic-search} for finding a feasible solution to the problem instance with constraint $k$.
+Based on the encoding method, we propose a search algorithm based on greedy heuristics in \cref{tab:heuristic-search} for finding a feasible solution to the problem instance with constraint $k$.
 
-\begin{algorithm}[h]
+\begin{algorithm}
 	\caption{The General Algorithm}
@@
 Given encodings under the initial classifier set, samples share the same encoding can be considered as a subclass, and there is no need to further split those subclasses.
-For example, in the intro example in Figure~\ref{fig:assemble-example-venn}, there is no need to distinguish $A_{11}$ and $A_{12}$ and we can group them as a single subclass.
+For example, in the intro example in \cref{fig:assemble-example-venn}, there is no need to distinguish $A_{11}$ and $A_{12}$ and we can group them as a single subclass.
 
@@
 Critical data routing path is extracted through optimizaition of control gates values.
-We freeze the weights of the model, and for each sample we follow the procedure of Distillation Guided Routing (algorithm \ref{alg:dgr}) \cite{wang2018interpret} to get the gate values.
+We freeze the weights of the model, and for each sample we follow the procedure of Distillation Guided Routing (\cref{alg:dgr}) \cite{wang2018interpret} to get the gate values.
 The gate values can be concatenated into one single vector as representation of that sample.
@@
 
-The visualization of clustering results is presented in figure \ref{fig:vgg-cluster-pca}.
+The visualization of clustering results is presented in \cref{fig:vgg-cluster-pca}.
 
@@
 
-We use methods introduced in paper \cite{LiDongYue} to prune the model according to gate vector of cluster centers (algorithm \ref{alg:prune}).
+We use methods introduced in paper \cite{LiDongYue} to prune the model according to gate vector of cluster centers (\cref{alg:prune}).
 
@@
 Based on the results of CDRP decomposition in VGG16-C and VGG16-D, we determine subclasses for CIFAR-5	\footnote{CIFAR-5 is a shorthand refering to samples having the first 5 class labels in CIFAR-100.} and their relationship to the CDRP clusters by encoding samples using all CDRP models.
-Instead of using Venn diagram like the intro example in Figure~\ref{fig:assemble-example-venn}, we use the network diagram in Figure~\ref{fig:network-venn} to represent the relationship between subclasses and clusters.
+Instead of using Venn diagram like the intro example in \cref{fig:assemble-example-venn}, we use the network diagram in \cref{fig:network-venn} to represent the relationship between subclasses and clusters.
 
@@
 
-From Figure~\ref{fig:vgg-cluster}, a cluster from VGG-C typically consists of samples from a single class, which is consistent with the result shown in Figure~\ref{}. 
+From \cref{fig:vgg-cluster}, a cluster from VGG-C typically consists of samples from a single class, which is consistent with the result shown in \cref{fig:vgg-cluster-pca}. 
 By contrast, a cluster from VGG-D may contain samples with different labels.
@@
 \paragraph{Classifiers.} Except some too small ones, we consider one cluster as a classifer. Each classifier judges whether the test sample should in the corresponding cluster. 
-From Figure~\ref{fig:vgg-cluster}, we determine the possibile labels of samples in each cluster as is shown in Table~\ref{tab:cluster_label}.
+From \cref{fig:vgg-cluster}, we determine the possibile labels of samples in each cluster as is shown in \cref{tab:cluster_label}.
 
-\begin{table}[h]
-	\caption{Corresponding Class Labels of Each Cluster}
-	\label{tab:cluster_label}
+\begin{table}[!htp]
 	\begin{tabular}{|c|c|c|}
@@
 \subsection{Fusing VGGNets for Specific Tasks through CDRP Assembly}
-\paragraph{Fusion} We implement the heuristic search in Algorithm~\ref{tab:heuristic-search} to fuse the classifiers. 
+\paragraph{Fusion} We implement the heuristic search in \cref{tab:heuristic-search} to fuse the classifiers. 
 Since we want to finish a specific task of classifying among five classes, we set a upper bound of the number of classifiers $k=4$. 
@@
 In our implementation, the algorithm choose four classifiers: 3,4,1,2 in order. 
-The accuracy of the four classifiers are shown in Table~\ref{tab:classifer-accuracy}.The test set has also been balanced to make the number of positive and negative samples nearly $1:1$.
+The accuracy of the four classifiers are shown in \cref{tab:classifer-accuracy}.The test set has also been balanced to make the number of positive and negative samples nearly $1:1$.
 
-\begin{table}[h]
-    \caption{Accuracy of Chosen Binary-Classifiers}
-    \label{tab:classifer-accuracy}
+\begin{table}[!htp]
 	\begin{tabular}{|c|c|c|c|c|}
 	\hline
-	Classifier ID & 3 & 4 & 1 & 2 \\
+	& classifier-3 & classifier-4 & classifier-1 & classifier-2 \\
 	\hline
@@
 	\end{tabular}
+    \caption{Accuracy of Chosen Binary-Classifiers}
+    \label{tab:classifer-accuracy}
 \end{table}
@@
 Actually, we can determine the class uniquely with the prefix of encodings. 
-For instance, if the result of classifer-3 is $0$, we don't need to take other classifers into consideration since the only class $0$ is possible in cluster-3 according to Table~\ref{tab:cluster_label}
+For instance, if the result of classifer-3 is $0$, we don't need to take other classifers into consideration since the only class $0$ is possible in cluster-3 according to \cref{tab:cluster_label}
 
-The corresponding encoding of each class label is shown in Table~\ref{tab:encoding-and-accuarcy}.
-We can determine the class label with this encoding, the accuracy of which is also shown in Table~\ref{tab:encoding-and-accuarcy}.
+The corresponding encoding of each class label is shown in \cref{tab:encoding-and-accuarcy}.
+We can determine the class label with this encoding, the accuracy of which is also shown in \cref{tab:encoding-and-accuarcy}.
 
-\begin{table}[h]
-    \caption{Encoding and Accuracy of Each Class Label}
-    \label{tab:encoding-and-accuarcy}
+\begin{table}[!htp]
 	\begin{tabular}{|c|c|c|c|c|c|c|}
 	\hline
-	Class ID & 0 & 1 & 2 & 3 & 4 & Overall \\
+	& class-0 & class-1 & class-2 & class-3 & class-4 & Overall \\
 	\hline
@@
 	\end{tabular}
+    \caption{Encoding and Accuracy of Each Class Label}
+    \label{tab:encoding-and-accuarcy}
 \end{table}

### 2020-01-10 paper/paper.tex

--- 2020-01-10 paper/paper.tex
@@
 We only train the pruned model i.e. weights of the pruned channels will remain zero.
-After finetune, most of the classifers can reach an accuracy more than 80\%, which is much higher than the overall accuracy of the original full network.
+With a prune ratio $pr\leq0.9$, most of the classifers can reach an accuracy more than 80\% after finetune, which is much higher than the overall accuracy of the original full network.
 
 \subsection{Fusing VGGNets for Specific Tasks through CDRP Assembly}
-\paragraph{Fusion} We implement the heuristic search in Algorithm~\ref{tab:heuristic-search} to fuse the classifiers. 
-Since we want to finish a specific task of classifying among five classes, we set a upper bound of the number of classifiers $k=4$. 
-After we select these classifiers with this algorithm, different results of each classifier ($0$ and $1$ represent the sample is or isn't in the cluster respectively) correspond to a unique label.
+In this section, we implement the heuristic search in Algorithm~\ref{tab:heuristic-search} to fuse the classifiers.
+According to the 0/1 result of each classifer, we can get an unique encoding for each sample, which corresponds to a unqiue label so that we can determine the class of each test sample.
+
+\paragraph{Fusion}We implement Algorithm~\ref{tab:heuristic-search} to fuse the classifiers since we want to finish a specific task of classifying among five classes, we set a upper bound of the number of classifiers $k=4$.
+After we select these classifiers with this Algorithm~\ref{tab:heuristic-search}, different results of each classifier ($0$ and $1$ represent the sample is or isn't in the cluster respectively) correspond to a unique label.
 In our implementation, the algorithm choose four classifiers: 3,4,1,2 in order. 
-The accuracy of the four classifiers are shown in Table~\ref{tab:classifer-accuracy}.The test set has also been balanced to make the number of positive and negative samples nearly $1:1$.
+The accuracy of the four classifiers with different prune ratio is shown in Table~\ref{tab:classifer-accuracy}.The test set has also been balanced to make the number of positive and negative samples nearly $1:1$.
 
 \begin{table}[h]
+
     \caption{Accuracy of Chosen Binary-Classifiers}
@@
 	\hline
-	Accuracy & 96.0\% & 86.0\% & 91.5\% & 87.0\%\\
+	\begin{tabular}{c}Accuracy\\pr=0.95\end{tabular} & 62.3\% & 82.3\% & 83.5\% & 67.0\%\\
+	\hline
+	\begin{tabular}{c}Accuracy\\pr=0.9\end{tabular} & 96.0\% & 86.0\% & 91.5\% & 87.0\%\\
+	\hline
+	\begin{tabular}{c}Accuracy\\pr=0.8\end{tabular} & 97.5\% & 80.5\% & 94.5\% & 89.5\%\\
 	\hline
@@
 \begin{table}[h]
+
     \caption{Encoding and Accuracy of Each Class Label}
@@
 	\hline
+
 	Class ID & 0 & 1 & 2 & 3 & 4 & Overall \\
 	\hline
-	Encoding &0 & 110 & 1110 &10 & 1111 &\\
+	Encoding &0 & 110 & 1110 &10 & 1111 & -\\
 	\hline
+	\begin{tabular}{c}Accuracy\\pr=0.95\end{tabular} & 100\% & 30.0\% & 11.0\% & 28.0\% & 7.0\% & 34.4\%\\
+
+	\hline
+	\begin{tabular}{c}Accuracy\\pr=0.9\end{tabular} & 92.0\% & 93.0\% & 58.0\% & 85.0\% & 67.0\% & 79.0\%\\
+	\hline
+	\begin{tabular}{c}Accuracy\\pr=0.8\end{tabular} & 95.0\% & 91.0\% & 76.0\% & 78.0\% & 76.0\% & 83.2\%\\
+
+	\hline
+
 	\end{tabular}
 \end{table}
+
+From Table~\ref{tab:encoding-and-accuarcy}, we find the overall accuracy is quite high if prune ratio $pr\leq0.9$ while the accuracy drops dramatically when $pr=0.95$ since we prune too much channels or even destroy the connectivity of the network.
+When it comes to the trade-off between parameter number and overall accuracy, it is suitable to set prune ratio $pr=0.9$.
+Compared to the accuracy of original full model in these $5$ classes ($70.57\%$), our classifier not only achieve higher precision but also improve the efficiency.
+When $pr=0.9$, we can inference with the $4$ classifiers in parallel, which can save about $90\%$ computing consumption on a single device.
 

### 2020-01-10 paper/paper.tex

--- 2020-01-10 paper/paper.tex
@@
 We only train the pruned model i.e. weights of the pruned channels will remain zero.
-After finetune, most of the classifers can reach an accuracy more than 80\%, which is much higher than the overall accuracy of the original full network.
+With a prune ratio $pr\leq0.9$, most of the classifers can reach an accuracy more than 80\% after finetune, which is much higher than the overall accuracy of the original full network.
 
 \subsection{Fusing VGGNets for Specific Tasks through CDRP Assembly}
-\paragraph{Fusion} We implement the heuristic search in \cref{tab:heuristic-search} to fuse the classifiers. 
-Since we want to finish a specific task of classifying among five classes, we set a upper bound of the number of classifiers $k=4$. 
-After we select these classifiers with this algorithm, different results of each classifier ($0$ and $1$ represent the sample is or isn't in the cluster respectively) correspond to a unique label.
+In this section, we implement the heuristic search in \cref{tab:heuristic-search} to fuse the classifiers.
+According to the 0/1 result of each classifer, we can get an unique encoding for each sample, which corresponds to a unqiue label so that we can determine the class of each test sample.
+
+\paragraph{Fusion}We implement \cref{tab:heuristic-search} to fuse the classifiers since we want to finish a specific task of classifying among five classes, we set a upper bound of the number of classifiers $k=4$.
+After we select these classifiers with this \cref{tab:heuristic-search}, different results of each classifier ($0$ and $1$ represent the sample is or isn't in the cluster respectively) correspond to a unique label.
 In our implementation, the algorithm choose four classifiers: 3,4,1,2 in order. 
-The accuracy of the four classifiers are shown in \cref{tab:classifer-accuracy}.The test set has also been balanced to make the number of positive and negative samples nearly $1:1$.
+The accuracy of the four classifiers with different prune ratio is shown in \cref{tab:classifer-accuracy}.The test set has also been balanced to make the number of positive and negative samples nearly $1:1$.
 
-\begin{table}[!htp]
+\begin{table}[h]
+
+    \caption{Accuracy of Chosen Binary-Classifiers}
+    \label{tab:classifer-accuracy}
 	\begin{tabular}{|c|c|c|c|c|}
 	\hline
-	& classifier-3 & classifier-4 & classifier-1 & classifier-2 \\
+	Classifier ID & 3 & 4 & 1 & 2 \\
 	\hline
-	Accuracy & 96.0\% & 86.0\% & 91.5\% & 87.0\%\\
+	\begin{tabular}{c}Accuracy\\pr=0.95\end{tabular} & 62.3\% & 82.3\% & 83.5\% & 67.0\%\\
+	\hline
+	\begin{tabular}{c}Accuracy\\pr=0.9\end{tabular} & 96.0\% & 86.0\% & 91.5\% & 87.0\%\\
+	\hline
+	\begin{tabular}{c}Accuracy\\pr=0.8\end{tabular} & 97.5\% & 80.5\% & 94.5\% & 89.5\%\\
 	\hline
 	\end{tabular}
-    \caption{Accuracy of Chosen Binary-Classifiers}
-    \label{tab:classifer-accuracy}
 \end{table}
@@
 
-\begin{table}[!htp]
+\begin{table}[h]
+
+    \caption{Encoding and Accuracy of Each Class Label}
+    \label{tab:encoding-and-accuarcy}
 	\begin{tabular}{|c|c|c|c|c|c|c|}
 	\hline
-	& class-0 & class-1 & class-2 & class-3 & class-4 & Overall \\
+
+	Class ID & 0 & 1 & 2 & 3 & 4 & Overall \\
 	\hline
-	Encoding &0 & 110 & 1110 &10 & 1111 &\\
+	Encoding &0 & 110 & 1110 &10 & 1111 & -\\
 	\hline
+	\begin{tabular}{c}Accuracy\\pr=0.95\end{tabular} & 100\% & 30.0\% & 11.0\% & 28.0\% & 7.0\% & 34.4\%\\
+
+	\hline
+	\begin{tabular}{c}Accuracy\\pr=0.9\end{tabular} & 92.0\% & 93.0\% & 58.0\% & 85.0\% & 67.0\% & 79.0\%\\
+	\hline
+	\begin{tabular}{c}Accuracy\\pr=0.8\end{tabular} & 95.0\% & 91.0\% & 76.0\% & 78.0\% & 76.0\% & 83.2\%\\
+
+	\hline
+
 	\end{tabular}
-    \caption{Encoding and Accuracy of Each Class Label}
-    \label{tab:encoding-and-accuarcy}
 \end{table}
+
+From \cref{tab:encoding-and-accuarcy}, we find the overall accuracy is quite high if prune ratio $pr\leq0.9$ while the accuracy drops dramatically when $pr=0.95$ since we prune too much channels or even destroy the connectivity of the network.
+When it comes to the trade-off between parameter number and overall accuracy, it is suitable to set prune ratio $pr=0.9$.
+Compared to the accuracy of original full model in these $5$ classes ($70.57\%$), our classifier not only achieve higher precision but also improve the efficiency.
+When $pr=0.9$, we can inference with the $4$ classifiers in parallel, which can save about $90\%$ computing consumption on a single device.
 

### 2020-01-10 paper/paper.tex
Update paper.tex

--- 2020-01-10 paper/paper.tex
@@
 When it comes to the trade-off between parameter number and overall accuracy, it is suitable to set prune ratio $pr=0.9$.
+
 Compared to the accuracy of original full model in these $5$ classes ($70.57\%$), our classifier not only achieve higher precision but also improve the efficiency. 
-When $pr=0.9$, we can inference with the $4$ classifiers in parallel, which can save about $90\%$ computing consumption on a single device.
+When $pr=0.9$, we can infer with the $4$ binary-classifiers in parallel instead of applying the original network, which can save about $90\%$ computing consumption on a single device as well as improve the accuracy.
 

### 2020-01-10 code/CriticalPathPruning/CIFAR_DataLoader.py
code

@@ -33,16 +33,20 @@ class CifarLoader(object):
         self.class_image = None
         self.class_label = None
 
-    def load(self, load_cluster=False):
+    def load(self, load_cluster=False, cluster_dir = "../data"):
         if load_cluster:
-            with open("../data/clusters.pkl","rb") as file:
+            dir = os.path.join(cluster_dir,"clusters.pkl")
+            with open(dir,"rb") as file:
                 self.cluster = pickle.load(file,encoding="bytes")
-            with open("../data/class_clusters.pkl","rb") as file:
+            dir = os.path.join(cluster_dir,"class_clusters.pkl")
+            with open(dir,"rb") as file:
                 self.class_cluster = pickle.load(file,encoding="bytes")
 
-            with open("../data/clusters_test.pkl","rb") as file:
+            dir = os.path.join(cluster_dir,"clusters_test.pkl")
+            with open(dir,"rb") as file:
                 self.cluster_test = pickle.load(file,encoding="bytes")
-            with open("../data/class_clusters_test.pkl","rb") as file:
+            dir = os.path.join(cluster_dir,"class_clusters_test.pkl")
+            with open(dir,"rb") as file:
                 self.class_cluster_test = pickle.load(file,encoding="bytes")
 
         data = [unpickle(f) for f in self._source]
@@ -69,7 +73,7 @@ class CifarLoader(object):
         self._i = (self._i + batch_size) % len(self.images)
         return x, one_hot(y, 100)
 
-    def next_batch_balance(self,batch_size,target_class_id,mode = "class", type = "train"):
+    def next_batch_balance(self,batch_size,target_class_id,cluster_id=[0],mode = "class", type = "train"):
         num = batch_size // (len(target_class_id)+1)
         tmp = []
         if type == "train":
@@ -81,10 +85,12 @@ class CifarLoader(object):
             # class_label = random.sample(self.class_label[class_id],num)
             for _ in range(num):
                 i = random.randint(0,len(self.class_image[class_id])-1)
+                # if type=="train" and class_cluster[class_id][i] not in cluster_id:
+                #     i = random.randint(0, len(self.class_image[class_id]) - 1)
                 tmp.append((self.class_image[class_id][i],self.class_label[class_id][i],class_cluster[class_id][i]))
 
         other_num = batch_size - num * len(target_class_id)
-        other_id = list(set(range(100))-set(target_class_id))
[…]

### 2020-01-10 code/CriticalPathPruning/group_encoding.py

@@ -19,7 +19,7 @@ def group(IE_dir, CE_dir):
 
 
 if __name__ == '__main__':
-    dir = ['ImageEncoding', 'ClassEncoding']
+    dir = ['vgg16-d/ImageEncoding_test', 'ClassEncoding']
     if len(sys.argv) > 1: dir[0] = sys.argv[1]
     if len(sys.argv) > 2: dir[1] = sys.argv[2]
     group(*dir)

### 2020-01-10 code/CriticalPathPruning/kmeans.py

@@ -1,214 +1,0 @@
-# coding: utf-8
-import math
-import random
-import os
-import json
-from collections import defaultdict
-import numpy as np
-
-
-def distance(point1, point2):
-    """
-    计算两点之间的欧拉距离，支持多维
-    """
-    # distance = 0.0
-    # for a, b in zip(point1, point2):
-    #     distance += math.pow(a - b, 2)
-    # return math.sqrt(distance)
-    # return np.sqrt(np.sum((point1 - point2) ** 2))
-    # return np.sqrt(np.sum((point1 - point2) ** 2))
-    return np.linalg.norm(point1-point2,ord=1)
-
-
-def get_closest_dist(point, centroids):
-    min_dist = math.inf  # 初始设为无穷大
-    for i, centroid in enumerate(centroids):
-        dist = distance(centroid, point)
-        if dist < min_dist:
-            min_dist = dist
-    return min_dist
-
-
-def kpp_centers(data_set: list, k: int) -> list:
-    """
-    从数据集中返回 k 个对象可作为质心
-    """
-    cluster_centers = []
-    cluster_centers.append(random.choice(data_set))
-    d = [0 for _ in range(len(data_set))]
-    for _ in range(1, k):
-        total = 0.0
-        for i, point in enumerate(data_set):
-            d[i] = get_closest_dist(point, cluster_centers) # 与最近一个聚类中心的距离
-            total += d[i]
-        total *= random.random()
-        for i, di in enumerate(d): # 轮盘法选出下一个聚类中心；
-            total -= di
-            if total > 0:
-                continue
-            cluster_centers.append(data_set[i])
-            break
-    return cluster_centers
-
-
-def point_avg(points):
-    '''
-    Accepts a list of points, each with the same number of dimensions.
-    NB. points can have more dimensions than 2
-    Returns a new points which is the center of all the points
-    :param points:
-    :return:
-    '''
-    dimensions = len(points[0])
-
-    new_center = []
-    points = np.array(points)
-    # for dimension in range(dimensions):
-    #     dim_sum = 0
-    #     for p in points:
-    #         dim_sum += p[dimension]
-    #
-    #     # average of each dimension
-    #     new_center.append(dim_sum / float(len(points)))
-
-    return np.mean(points,axis=0)[0]
-
-
-def update_centers(date_set, assignments):
-    '''
-    Accepts a dataset and a list of assignments; the indexes of both lists correspond
-    to each other.
[…]

### 2020-01-10 code/CriticalPathPruning/test_model.py

@@ -1,0 +1,78 @@
+import json
+import pickle
+import os
+from vggClassifierModel import ClassifierModel
+from CIFAR_DataLoader import CifarDataManager
+import numpy as np
+import argparse
+
+
+def find_label(encodings,code):
+    codes = list(encodings.keys())
+    for i in range(len(code)):
+        new_codes = []
+        for item in codes:
+            if item[i]=="2" or item[i]==code[i]:
+                new_codes.append(item)
+        codes = new_codes
+        if len(new_codes)==1:
+            break
+    print(codes[0],encodings[codes[0]])
+    return list(encodings[codes[0]])[0]
+
+
+
+if __name__=="__main__":
+    parser = argparse.ArgumentParser("run finetune")
+    parser.add_argument(
+        "--model_dir", help="the directory saving the classifiers",
+        default="classifiers",type=str)
+    parser.add_argument(
+        "--chosen_dir", help="the pickle file saving the chosen classifers and encodings",
+        default="../chosen_classifier.pkl",type=str)
+    args = parser.parse_args()
+
+    data_loader = CifarDataManager()
+    class_ids = [0,1,2,3,4]
+    cluster_ids = list(range(0,20))
+    test_images = []
+    test_labels = []
+    for id in class_ids:
+        test_images += data_loader.test.class_image[id]
+        test_labels += data_loader.test.class_label[id]
+    num = len(test_labels)
+    test_images = np.array(test_images)
+    test_labels = np.array(test_labels)
+    # test_images = data_loader.test.next_batch_balance_without_onehot(num, class_ids, mode="class")
+
+    with open(args.chosen_dir,"rb") as file:
+        used, encodings = pickle.load(file,encoding="bytes")
+    codes = [""]*num
+    for item in used:
+        if int(item)<7:
+            vgg_type = "C"
+        else:
+            vgg_type = "D"
+        model = ClassifierModel(vgg_type)
+        filename = os.path.join(args.model_dir,"classifier%d.ckpt"%int(item))
+        model.from_checkpoint(filename)
+        classifier_res = model.predict(test_images, test_labels)
+        for i in range(len(classifier_res)):
+            codes[i] = codes[i] + str(classifier_res[i])
+
+    correct = 0
+    # print(codes)
+    # print(test_labels)
+    count_label = [0]*5
+    for i in range(len(codes)):
+        label = find_label(encodings,codes[i])
+        # print(label,test_labels[i])
+        # print(type(label),type(test_labels[i]))
[…]

### 2020-01-10 code/CriticalPathPruning/trim_and_test.py

@@ -4,7 +4,7 @@ import numpy as np
 d = CifarDataManager()
 
 
-model = TrimmedModel(target_class_id=[99],target_cluster_id = [0],mode="class",
+model = TrimmedModel(target_class_id=[0,1,2,3,4],target_cluster_id = [0],mode="class",
                      multiPruning=True)
 
 '''
@@ -12,7 +12,7 @@ Todo List:
     1. Modify the accuracy in trimmed network (Done)
 '''
 for _ in range(50):
-    test_images, test_labels = d.test.next_batch_balance(200,[99])
+    test_images, test_labels = d.test.next_batch_balance(200,[0,1,2,3,4])
 
     model.test_accuracy_pretrim(test_images, test_labels)
     model.assign_weight()

### 2020-01-10 code/CriticalPathPruning/vggFinetuneModel.py

@@ -7,20 +7,20 @@ import numpy as np
 import tensorflow as tf
 from sklearn.utils import shuffle
 import os
-os.environ["CUDA_VISIBLE_DEVICES"] = "1"
+os.environ["CUDA_VISIBLE_DEVICES"] = "4,5,6"
 class FineTuneModel():
     '''
     Fine Tune Model: (Basically doing transfer learning)
         1. Last FC layer neurons number would be the target class number + 1
         2. Need to transform the original label to targeted class label
     '''
-    def __init__(self, target_class_id=[0], target_cluster_id = [0], mode = "class"):
+    def __init__(self, target_class_id=[0], target_cluster_id = [0], mode = "class",cluster_dir = None):
         '''
         Set hyperparameters
         '''
         self.learning_rate = 0.1
         self.epoch = 0
-        self.prune_ratio = 0.9
+        self.prune_ratio = 0.95
 
         '''
         For one input image :
@@ -34,16 +34,33 @@ class FineTuneModel():
         if mode == "class":
             self.target_id = target_class_id
             self.target_number = len(target_class_id) + 1
+            self.cluster_dir = None
         else:
             self.target_id = target_cluster_id
             self.target_number = len(target_cluster_id) + 1
+            self.cluster_dir = os.path.join(cluster_dir,"cluster%d.json")
 
         self.target_class_id = target_class_id # assign the trim class id
+
 
         self.graph = tf.Graph()
         self.build_model(self.graph)
         print("restored the pretrained model......")
         self.restore_model(self.graph)
+
+    def from_checkpoint(self,filename):
+        # If GPU is needed
+        config = tf.ConfigProto()
+        config.gpu_options.allow_growth = True
+        self.sess = tf.Session(graph = graph, config = config)
+        # Else if CPU needed
+        # self.sess = tf.Session(graph = graph)
+        self.sess.run(self.init)
+        with graph.as_default():
+            saver = tf.train.Saver(savedVariable)
+            saver.restore(self.sess, filename)
+            print("Restored successfully!")
+
 
     '''
     Test Accuracy
@@ -67,8 +84,8 @@ class FineTuneModel():
                 new_test_labels.append(1)
         new_test_labels = np.array(new_test_labels)
 
-        p = new_test_labels==0
-        n = new_test_labels==1
+        p = ys_pred_argmax==0
+        n = ys_pred_argmax==1
 
         p_label = new_test_labels[p]
[…]

### 2020-01-10 code/cluster_label.py

@@ -1,8 +1,25 @@
 import json
+import argparse
+import os
 
 
 if __name__=="__main__":
-    with open("data/sub_encoding.txt","r") as file:
+    parser = argparse.ArgumentParser("Cluster Label")
+    parser.add_argument(
+        "--encoder_save_path", help="The file to save the encoder.",
+        default="data", type=str)
+    parser.add_argument(
+        "--start_class", help="start class of predictor",
+        default=0, type=int
+    )
+    parser.add_argument(
+        "--end_class", help="end class of predictor",
+        default=99, type=int
+    )
+    args = parser.parse_args()
+
+    dir = os.path.join(args.encoder_save_path,"sub_encoding.txt")
+    with open(dir,"r") as file:
         sub_encoding = file.readlines()
     cluster_label = {}
     for l in sub_encoding:
@@ -25,13 +42,13 @@ if __name__=="__main__":
             clusters[key][label] =  cluster_label[key][label]
     cluster_label = clusters
 
-
+    print(cluster_label)
     classifier_label = {}
 
     for key in cluster_label:
         cluster_keys = list(cluster_label[key].keys())
         cluster_size = sum(list(cluster_label[key].values()))
-        if cluster_size<500*100/len(cluster_label)/5:
+        if cluster_size<500*(args.end_class-args.start_class+1)/len(cluster_label)/5:
             continue
         tmp1 = []
         tmp2 = []
@@ -40,10 +57,12 @@ if __name__=="__main__":
                 tmp1.append(label)
                 if cluster_label[key][label]<500*0.95:
                     tmp2.append(label)
-        others = list(set(range(100))-set(tmp1))
+        others = list(set(range(args.start_class,args.end_class+1))-set(tmp1))
         tmp2 += others
-        classifier_label[key] = (tmp1,tmp2,cluster_size/(500*100))
+        classifier_label[key] = (tmp1,tmp2,cluster_size/(500*(args.end_class-args.start_class+1)))
         # cluster_label[key] = sorted(cluster_label[key],key=cluster_label[key].__getitem__,reverse=True)
         print(key,cluster_label[key],classifier_label[key])
-    with open("classifier.json","w") as file:
+
+    dir = os.path.join(args.encoder_save_path,"classifier.json")
+    with open(dir,"w") as file:
         json.dump(classifier_label,file)

### 2020-01-10 paper/paper.tex
Update paper.tex
change to booktabs
change to varnothing

--- 2020-01-10 paper/paper.tex
@@
 		\Require The inputs to the assembly problem;
-		\Ensure $D$, a classifier set satisfying constraints, or $\emptyset$ if not feasible.
-		\State $Q \gets \emptyset$; \Comment A priority queue, the last element $h$ is the key
+		\Ensure $D$, a classifier set satisfying constraints, or $\varnothing$ if not feasible.
+		\State $Q \gets \varnothing$; \Comment A priority queue, the last element $h$ is the key
 		\Function{Expand}{$D$} \Comment $D$, the classifier set
@@
 		\Function{HeuristicSearch}{}
-			\State $\Call{Expand}{\emptyset}$;
-			\While{$Q \neq \emptyset$}
+			\State $\Call{Expand}{\varnothing}$;
+			\While{$Q \neq \varnothing$}
 				\State $(D, C, h) \gets Pop(Q)$;
@@
 			\EndWhile
-			\State \Return $\emptyset$;
+			\State \Return $\varnothing$;
 		\EndFunction
@@
 	\hline
-	\multirow{2}{*}{Classifier} &\multicolumn{2}{|c|}{Possible Class Labels}\\
+	\multirow{2}{*}{Classifier} &\multicolumn{2}{c|}{Possible Class Labels}\\
 	\cline{2-3}
@@
     \label{tab:classifer-accuracy}
-	\begin{tabular}{|c|c|c|c|c|}
-	\hline
+	\begin{tabular}{ccccc}
+	\toprule
 	Classifier ID & 3 & 4 & 1 & 2 \\
-	\hline
+	\midrule
 	\begin{tabular}{c}Accuracy\\pr=0.95\end{tabular} & 62.3\% & 82.3\% & 83.5\% & 67.0\%\\
-	\hline
 	\begin{tabular}{c}Accuracy\\pr=0.9\end{tabular} & 96.0\% & 86.0\% & 91.5\% & 87.0\%\\
-	\hline
 	\begin{tabular}{c}Accuracy\\pr=0.8\end{tabular} & 97.5\% & 80.5\% & 94.5\% & 89.5\%\\
-	\hline
+	\bottomrule
 	\end{tabular}
@@
     \label{tab:encoding-and-accuarcy}
-	\begin{tabular}{|c|c|c|c|c|c|c|}
-	\hline
-
+	\begin{tabular}{ccccccc}
+	\toprule
 	Class ID & 0 & 1 & 2 & 3 & 4 & Overall \\
-	\hline
+	\midrule
 	Encoding &0 & 110 & 1110 &10 & 1111 & -\\
-	\hline
 	\begin{tabular}{c}Accuracy\\pr=0.95\end{tabular} & 100\% & 30.0\% & 11.0\% & 28.0\% & 7.0\% & 34.4\%\\
 
-	\hline
 	\begin{tabular}{c}Accuracy\\pr=0.9\end{tabular} & 92.0\% & 93.0\% & 58.0\% & 85.0\% & 67.0\% & 79.0\%\\
-	\hline
 	\begin{tabular}{c}Accuracy\\pr=0.8\end{tabular} & 95.0\% & 91.0\% & 76.0\% & 78.0\% & 76.0\% & 83.2\%\\
-
-	\hline
+	\bottomrule
 

### 2020-01-10 paper/paper.tex
write introduction, and some other adjustments

--- 2020-01-10 paper/paper.tex
@@
 \usepackage{cuted}
-\usepackage{makecell}
 
@@
 \label{sec:intro}
-The introduction \dots
+The development of deep learning has proved its great capability, and it will be more beneficial if we can plant deep learning models into edge devices like wearable devices.
+However, the limited energy supply and computational capability of edge devices lead to constraints on the scale and complexity of deep neural networks.
+The edge devices often need only to perform very specific tasks, whereas the pre-trained models deals with more general cases.
+This makes it possible to develop task-specific and light-weighted models to meet various constraints of edge device.
+
+% Network fusion is a potential way to further improve the performance of network models with the advance of edge devices, where we could deploy many models through devices, let them perform inference in parallel, and retrieve and join the results \cite{fang2019teamnet}.
+% Nevertheless, this could cause redundant complexity across models, making it unable to fully utilize the capability of each edge devices.
+
+In this paper, we first study a framework of assembling multiple small binary classifiers into one that performs complicated classification tasks.
+Figure~\ref{fig:assemble-example-venn} shows an example of the assembly problem of our interest.
 
@@
 
-Figure~\ref{fig:assemble-example-venn} shows an example of the assembly problem of our interest.
 The original dataset contains 3 classes $A_1, A_2$, and $A_3$, and we are able to decompose each into some subclasses, e.g., $A_1$ is decomposed into two subclasses of samples $A_{11}$ and $A_{12}$.
@@
 
-\subsection{Our Work}
+We then instantiate such framework in a concrete setting of image classification.
+To do so, we need to find a desirable initial set of binary classifiers which is not costly to obtain but also guarantees non-trivial solutions.
+We use critical data routing path (CDRP) method \cite{wang2018interpret} and clustering of CDRPs to extract from multiple large networks to find those classifiers with reduced complexity, and then apply the assembly framework to build task-specific model.
+Such CDRP model decomposition and assembly framework has many applications.
+\begin{itemize}
+	\item Fuse networks at a fine-grained level.
+	In the CDRP decomposition, we may use only relevant convolution kernels in the resulting classifiers.
+	Therefore we can skip redundant feature extractors instead of fusing entire networks by concatenating their outputs.
+	\item Fused networks may be trained on different datasets (but with the same task), and we can also use dataset different from the ones models are trained on as the basis of CDRP decomposition and assembly.
+	The resulting model will be able to cover tasks performed on the new dataset.
+\end{itemize}
+
+In this paper, we address the followings.
+\begin{itemize}
+	\item We propose a general assembly framework for binary classifiers and a heuristic algorithm to the search problem in \cref{sec:assembly}.
+	\item We instantiate the assembly framework based on the CDRP method for the image classification task on CIFAR-100 in \cref{sec:cdrp}.
+	\item We experiment such implementation on a subset of CIFAR-5 in \cref{sec:experiments}.
+\end{itemize}
 
@@
 
-Figure~\ref{fig:assemble-example-encoding} shows the encoding mentioned in the certificate algorithm for the intro example in Figure~\ref{fig:assemble-example-venn}.
-If we only use the encoding from $d_1, d_2, d_3$, we find no two subclasses with different labels share the same encoding, and therefore certify the correctness of the feasible solution proposed before.
-For the partial classification task for $A_3$, using two bits from $d_2, d_4$ already provides distinguishable encoding for $A_{31}$ and the remaining dummy classes.
-
 % \linespread{1.1}
 \begin{figure}[h]
-	\begin{tabular}{|c|c|cccc|}
-	\cline{1-6}
-	\multicolumn{2}{|c|}{} & $d_1$ & $d_2$ & $d_3$ & $d_4$ \\ \cline{1-6}
-	\multirow{2}{*}{$A_1$} & $A_{11}$ & 1 & 0 & 0 & 0 \\ \cline{2-6}
-	 & $A_{12}$ & 1 & 0 & 0 & 0 \\ \cline{1-6}
-	\multirow{3}{*}{$A_2$} & $A_{21}$ & 1 & 1 & 0 & 0 \\ \cline{2-6}
-	 & $A_{22}$ & 1 & 0 & 1 & 1 \\ \cline{2-6}
-	 & $A_{23}$ & 0 & 0 & 1 & 0 \\ \cline{1-6}
-	$A_3$ & $A_{31}$ & 0 & 1 & 0 & 1 \\ \cline{1-6}
-	\end{tabular}
+	\centering
+	\includegraphics[width=0.55\linewidth]{fig/encoding_example.png}
+	% \begin{tabular}{|c|c|cccc|}
+	% \cline{1-6}
+	% \multicolumn{2}{|c|}{} & $d_1$ & $d_2$ & $d_3$ & $d_4$ \\ \cline{1-6}
+	% \multirow{2}{*}{$A_1$} & $A_{11}$ & 1 & 0 & 0 & 0 \\ \cline{2-6}
+	%  & $A_{12}$ & 1 & 0 & 0 & 0 \\ \cline{1-6}
+	% \multirow{3}{*}{$A_2$} & $A_{21}$ & 1 & 1 & 0 & 0 \\ \cline{2-6}
+	%  & $A_{22}$ & 1 & 0 & 1 & 1 \\ \cline{2-6}
+	%  & $A_{23}$ & 0 & 0 & 1 & 0 \\ \cline{1-6}
+	% $A_3$ & $A_{31}$ & 0 & 1 & 0 & 1 \\ \cline{1-6}
+	% \end{tabular}
 	\caption{Encoding for the Intro Example}
@@
 % \linespread{1.0}
+
+Figure~\ref{fig:assemble-example-encoding} shows the encoding mentioned in the certificate algorithm for the intro example in Figure~\ref{fig:assemble-example-venn}.
+If we only use the encoding from $d_1, d_2, d_3$ in the orange box, no two subclasses with different labels share the same encoding, and therefore it certifies the correctness of the feasible solution proposed before.
+For the partial classification task for $A_3$, using two bits from $d_2, d_4$ in the blue box already provides distinguishable encoding for $A_{31}$ and the remaining dummy classes.
 
@@
 \begin{algorithm}[h]
-	\caption{The General Algorithm}
+    \caption{The Heuristic DFS Algorithm}
     \label{tab:heuristic-search}
@@
       \Ensure $D$, a classifier set satisfying constraints, or $\emptyset$ if not feasible.
-		\State $Q \gets \emptyset$; \Comment A priority queue, the last element $h$ is the key
-		\Function{Expand}{$D$} \Comment $D$, the classifier set
+      \Function{HeuristicSearch}{$D$}
+        \State $Q \gets \emptyset$; \Comment An array of descendent states
         \For{$d \in \mathcal{D} - D$}
@@
         \EndFor
-		\EndFunction
-		\Function{HeuristicSearch}{}
-			\State $\Call{Expand}{\emptyset}$;
-			\While{$Q \neq \emptyset$}
-				\State $(D, C, h) \gets Pop(Q)$;
-				\If{$e_0 == 0$}
-					\State \Return $D$;
+        \State Sort $Q$ by ascending entropy;
+        \For{$(D, C, h) \in Q$}
+          \If{$h == 0$}
+            \State \Return $D$; \Comment Find a hit if residual entropy is 0
           \EndIf
           \If{|D| < k}
-					\State $\Call{Expand}{D}$;
+            \State $\Call{HeuristicSearch}{D}$; \Comment Search deeper level
           \EndIf
-			\EndWhile
+        \EndFor
         \State \Return $\emptyset$;
@@
 where $p(c)$ is the probability for encoding $c$ to occur, and $p(c, l)$ is the probability of a sample having encoding $c$ and label $l$.
-Note that the label ranges over $\mathcal{L}'$, the set of target labels and one dummy label, and all labels that are not target is defined to be equal to the dummy one.
+Note that the label ranges over $\mathcal{L}'$, the set of target labels and one dummy label, and all labels that are not targets are defined to be equal to the dummy one.
 In each search iteration, the algorithm will choose the classifier set that minimizes the entropy greedily, so that the search could possibly to end with minimum search depth.
@@
 
-\paragraph{Remark.} We do not need to provide the subclasses in the input, because they can be derived from the initial set of classifiers.
-Given encodings under the initial classifier set, samples share the same encoding can be considered as a subclass, and there is no need to further split those subclasses.
-For example, in the intro example in Figure~\ref{fig:assemble-example-venn}, there is no need to distinguish $A_{11}$ and $A_{12}$ and we can group them as a single subclass.
-
 To satisfy the above constraints, we follow the previous work of Wang \textit{et al.} \cite{wang2018interpret} to use critical data routing path (CDRP) for generating the input.
@@
 We use image classification task on CIFAR-100 and VGG16 of type C and D for demonstration.
+
+\paragraph{Remark.} We do not need to provide the subclasses in the input, because they can be derived from the initial set of classifiers.
+Given encodings under the initial classifier set, samples share the same encoding can be considered as a subclass, and there is no need to further split those subclasses.
+For example, in the intro example in Figure~\ref{fig:assemble-example-venn}, there is no need to distinguish $A_{11}$ and $A_{12}$ and we can group them as a single subclass.
 
@@
 
-The results shows we can derive a good basis of binary classifers through these clusters.
+The results shows we can derive a good basis of binary classifiers through these clusters.
 First, the good mapping from cluster to class label means we can use these binary classifiers to construct subclasses mentioned in the beginning of this section.
@@
 
-Afterwards we modify the network architecture of fully connected layers to form a binary classifer $g_{\theta'}(\cdot)$. The reason to do this includes:
+Afterwards we modify the network architecture of fully connected layers to form a binary classifier $g_{\theta'}(\cdot)$. The reason to do this includes:
 \begin{itemize}
-	\item It has less parameters than 100-class classifers.
+	\item It has less parameters than 100-class classifiers.
 	\item It is easier to train, i.e. easier to have higher accuarcy.
@@
 \section{Experiments}
+\label{sec:experiments}
 \subsection{Verifying CDRP Models of VGGNets trained on CIFAR-100}
-In this section, we perform K-Means on the CDRP control gates of each sample.
-For each cluster, we get a binary-classifier to determine whether the test sample should be in the cluster.
-Then, we fine tune each classifier in the CIFAR-100 dataset.
-
-\paragraph{Clusters.} For VGGNet, we generate $1.5$ clusters per class.
+\paragraph{Clusters.} We perform K-Means on the CDRP control gates of each sample. 
+For VGGNet, we generate $1.5$ clusters per class.
 Then, we get $14$ clusters from $5$ classes, among which $7$ clusters are from VGG16-C and $7$ clusters from VGG16-D.
@@
 
-\paragraph{Classifiers.} Except some too small ones, we consider one cluster as a classifer. Each classifier judges whether the test sample should in the corresponding cluster. 
+\paragraph{Classifiers.} Except some too small ones, we consider one cluster as a classifier. Each classifier judges whether the test sample should in the corresponding cluster. 
 From Figure~\ref{fig:vgg-cluster}, we determine the possibile labels of samples in each cluster as is shown in Table~\ref{tab:cluster_label}.
@@
 Since we want to get binary-classifiers, we slightly change the original VGGNet architecture in output dimension of the last Fully-Connected Layer from $100$ to $2$. 
-We also prune the original full VGGNet in the guide of CDRP with a prune ratio $pr$ i.e. if $pr=0.9$, $90\%$ of channels in all layers are pruned. 
-As a result, each classifer only has $10\%$ parameters of the original full network.
+We also prune the original full VGGNet in the guide of CDRP with a prune ratio $0.9$ i.e. $90\%$ of channels in all layers are pruned. 
+As a result, each classifier only has $10\%$ parameters of the original full network.
 
 \paragraph{Finetune.} The classifiers we get above cannot achieve any meaningful results because they tend to classifiy all test samples not in the cluster and the weights of the last layer is initialized randomly.
-We implement finetune on these classifers to make the results more meaningful and accurate. 
+We implement finetune on these classifiers to make the results more meaningful and accurate. 
 Since the negative samples are greatly more than positive ones in the dataset, we need to implement some strategies to balance them i.e.
@@
 
-We train each classifer with $1500$ iterations with a batch size $200$. 
+We train each classifier with $1500$ iterations with a batch size $200$. 
 The learning rate is $0.1$ for the first $1200$ iterations and $0.01$ for the remaining $300$ iterations. 
 We only train the pruned model i.e. weights of the pruned channels will remain zero.
-With a prune ratio $pr\leq0.9$, most of the classifers can reach an accuracy more than 80\% after finetune, which is much higher than the overall accuracy of the original full network.
+After finetune, most of the classifiers can reach an accuracy more than 80\%, which is much higher than the overall accuracy of the original full network.
 
 \subsection{Fusing VGGNets for Specific Tasks through CDRP Assembly}
-In this section, we implement the heuristic search in Algorithm~\ref{tab:heuristic-search} to fuse the classifiers.
-According to the 0/1 result of each classifer, we can get an unique encoding for each sample, which corresponds to a unqiue label so that we can determine the class of each test sample.
-
-\paragraph{Fusion}We implement Algorithm~\ref{tab:heuristic-search} to fuse the classifiers since we want to finish a specific task of classifying among five classes, we set a upper bound of the number of classifiers $k=4$.
-After we select these classifiers with this Algorithm~\ref{tab:heuristic-search}, different results of each classifier ($0$ and $1$ represent the sample is or isn't in the cluster respectively) correspond to a unique label.
+\paragraph{Fusion} We implement the heuristic search in Algorithm~\ref{tab:heuristic-search} to fuse the classifiers. 
+Since we want to finish a specific task of classifying among five classes, we set a upper bound of the number of classifiers $k=4$. 
+After we select these classifiers with this algorithm, different results of each classifier ($0$ and $1$ represent the sample is or isn't in the cluster respectively) correspond to a unique label.
 In our implementation, the algorithm choose four classifiers: 3,4,1,2 in order. 
-The accuracy of the four classifiers with different prune ratio is shown in Table~\ref{tab:classifer-accuracy}.The test set has also been balanced to make the number of positive and negative samples nearly $1:1$.
+The accuracy of the four classifiers are shown in Table~\ref{tab:classifier-accuracy}.The test set has also been balanced to make the number of positive and negative samples nearly $1:1$.
 
 \begin{table}[h]
-
     \caption{Accuracy of Chosen Binary-Classifiers}
-    \label{tab:classifer-accuracy}
+    \label{tab:classifier-accuracy}
 	\begin{tabular}{|c|c|c|c|c|}
@@
 	\hline
-	\begin{tabular}{c}Accuracy\\pr=0.95\end{tabular} & 62.3\% & 82.3\% & 83.5\% & 67.0\%\\
-	\hline
-	\begin{tabular}{c}Accuracy\\pr=0.9\end{tabular} & 96.0\% & 86.0\% & 91.5\% & 87.0\%\\
-	\hline
-	\begin{tabular}{c}Accuracy\\pr=0.8\end{tabular} & 97.5\% & 80.5\% & 94.5\% & 89.5\%\\
+	Accuracy & 96.0\% & 86.0\% & 91.5\% & 87.0\%\\
 	\hline
@@
 \paragraph{Verifying Result.}By combining the 0/1-results of the four classifiers, we can determine the class label unqiuely of one test sample.
-For example, if the result of classifer-3 is $0$ whether results of others are all $1$s, the encoding will be $0111$ and we can determine the sample is in class $0$.
+For example, if the result of classifier-3 is $0$ whether results of others are all $1$s, the encoding will be $0111$ and we can determine the sample is in class $0$.
 
 Actually, we can determine the class uniquely with the prefix of encodings. 
-For instance, if the result of classifer-3 is $0$, we don't need to take other classifers into consideration since the only class $0$ is possible in cluster-3 according to Table~\ref{tab:cluster_label}
+For instance, if the result of classifier-3 is $0$, we don't need to take other classifiers into consideration since the only class $0$ is possible in cluster-3 according to Table~\ref{tab:cluster_label}
 
@@
 \begin{table}[h]
-
     \caption{Encoding and Accuracy of Each Class Label}
@@
 	\hline
-
 	Class ID & 0 & 1 & 2 & 3 & 4 & Overall \\
 	\hline
-	Encoding &0 & 110 & 1110 &10 & 1111 & -\\
+	Encoding &0 & 110 & 1110 &10 & 1111 &\\
 	\hline
-	\begin{tabular}{c}Accuracy\\pr=0.95\end{tabular} & 100\% & 30.0\% & 11.0\% & 28.0\% & 7.0\% & 34.4\%\\
-
-	\hline
-	\begin{tabular}{c}Accuracy\\pr=0.9\end{tabular} & 92.0\% & 93.0\% & 58.0\% & 85.0\% & 67.0\% & 79.0\%\\
-	\hline
-	\begin{tabular}{c}Accuracy\\pr=0.8\end{tabular} & 95.0\% & 91.0\% & 76.0\% & 78.0\% & 76.0\% & 83.2\%\\
-
-	\hline
-
 	\end{tabular}
 \end{table}
-
-From Table~\ref{tab:encoding-and-accuarcy}, we find the overall accuracy is quite high if prune ratio $pr\leq0.9$ while the accuracy drops dramatically when $pr=0.95$ since we prune too much channels or even destroy the connectivity of the network.
-When it comes to the trade-off between parameter number and overall accuracy, it is suitable to set prune ratio $pr=0.9$.
-
-Compared to the accuracy of original full model in these $5$ classes ($70.57\%$), our classifier not only achieve higher precision but also improve the efficiency. 
-When $pr=0.9$, we can infer with the $4$ binary-classifiers in parallel instead of applying the original network, which can save about $90\%$ computing consumption on a single device as well as improve the accuracy.
 

### 2020-01-10 paper/paper.tex
import related work

@@
 \section{Related Work}
-The related work \dots
+There have been other similar works trying to understand and prune the complexity of the CNN.
+Zhou \textit{et al.} \cite{zhou2018interpreting} \cite{zhou2018revisiting} seek to understand the influence of certain filters on the accuracy wrt.
+some specific classes of samples by ablation and dissection.
+Their work provides certain explanations of the outcome, but they do not explain how their technique can be utilize to improve or compress the model and it is only useful for network interpretation.
+Yu \textit{et al.} \cite{yu2018distilling} attempt to produce task-specific models with reduced complexity through critical path distillation.
+They identify critical paths through activation visualization for specific classes, which is more efficient than training gates to find them in our work.
+But this means their critical path models are at the class level and these models can not interact with other external models through network fusion.
+
+Qin \textit{et al.} propose the CAPTOR \cite{qin2019captor}, a framework for filter pruning also through clustering.
+Different from our clustering method, they perform the clustering on filters with similar activation maximization visualization and prune similar filters to remove redundances.
+We could also use this technique to remove redundances within a CDRP model.
+Their pruning is again performed at the class level, while ours assembly is performed at the feature level, which is more fine-grained.
+
+On the topic of network fusion, there are also many marvelous researches.
+Du \textit{et al.} \cite{du2017fused} use multiple DNNs to refine the detections of a pedestrian detection generator and fuse these DNNs by fusing their outputs.
+This type of output level fusion is coarse-grained, where redundant feature extractions may have occurred in DNNs.
+On the opposite, Feichtenhofer \textit{et al.} \cite{feichtenhofer2016convolutional} proposed an extremely fine-grained fusion of multiple CNNs for video action recognition, where they carry out spatial fusion and temporal fusion on the layer level and achieves state-of-the-art results.
+However, there are common problems of both work.
+Their framework are task-specific and is difficult to apply their techniques in other domains.
+And their works do not aim to reduce the network complexity during the fusion process.
 

### 2020-01-10 paper/paper.tex
fix missing conflict

@@
 In this paper, we first study a framework of assembling multiple small binary classifiers into one that performs complicated classification tasks.
-Figure~\ref{fig:assemble-example-venn} shows an example of the assembly problem of our interest.
+\Cref{fig:assemble-example-venn} shows an example of the assembly problem of our interest.
 
@@
 
-Figure~\ref{fig:assemble-example-encoding} shows the encoding mentioned in the certificate algorithm for the intro example in Figure~\ref{fig:assemble-example-venn}.
+\Cref{fig:assemble-example-encoding} shows the encoding mentioned in the certificate algorithm for the intro example in \Cref{fig:assemble-example-venn}.
 If we only use the encoding from $d_1, d_2, d_3$ in the orange box, no two subclasses with different labels share the same encoding, and therefore it certifies the correctness of the feasible solution proposed before.
@@
 \label{sec:assembly-algorithm}
-Based on the encoding method, we propose a search algorithm based on greedy heuristics in Algorithm~\ref{tab:heuristic-search} for finding a feasible solution to the problem instance with constraint $k$.
+Based on the encoding method, we propose a search algorithm based on greedy heuristics in \cref{tab:heuristic-search} for finding a feasible solution to the problem instance with constraint $k$.
 
@@
 \paragraph{Classifiers.} Except some too small ones, we consider one cluster as a classifier. Each classifier judges whether the test sample should in the corresponding cluster. 
-From Figure~\ref{fig:vgg-cluster}, we determine the possibile labels of samples in each cluster as is shown in Table~\ref{tab:cluster_label}.
+From \cref{fig:vgg-cluster}, we determine the possibile labels of samples in each cluster as is shown in \cref{tab:cluster_label}.
 
@@
 Since we want to get binary-classifiers, we slightly change the original VGGNet architecture in output dimension of the last Fully-Connected Layer from $100$ to $2$. 
-We also prune the original full VGGNet in the guide of CDRP with a prune ratio $0.9$ i.e. $90\%$ of channels in all layers are pruned. 
+We also prune the original full VGGNet in the guide of CDRP with a prune ratio $pr$ i.e. if $pr=0.9$, $90\%$ of channels in all layers are pruned. 
 As a result, each classifier only has $10\%$ parameters of the original full network.
@@
 We only train the pruned model i.e. weights of the pruned channels will remain zero.
-After finetune, most of the classifiers can reach an accuracy more than 80\%, which is much higher than the overall accuracy of the original full network.
+With a prune ratio $pr\leq0.9$, most of the classifiers can reach an accuracy more than 80\% after finetune, which is much higher than the overall accuracy of the original full network.
 
 \subsection{Fusing VGGNets for Specific Tasks through CDRP Assembly}
-\paragraph{Fusion} We implement the heuristic search in Algorithm~\ref{tab:heuristic-search} to fuse the classifiers. 
-Since we want to finish a specific task of classifying among five classes, we set a upper bound of the number of classifiers $k=4$. 
-After we select these classifiers with this algorithm, different results of each classifier ($0$ and $1$ represent the sample is or isn't in the cluster respectively) correspond to a unique label.
+In this section, we implement the heuristic search in \cref{tab:heuristic-search} to fuse the classifiers.
+According to the 0/1 result of each classifier, we can get an unique encoding for each sample, which corresponds to a unqiue label so that we can determine the class of each test sample.
+
+\paragraph{Fusion}We implement \cref{tab:heuristic-search} to fuse the classifiers since we want to finish a specific task of classifying among five classes, we set a upper bound of the number of classifiers $k=4$.
+After we select these classifiers with this \cref{tab:heuristic-search}, different results of each classifier ($0$ and $1$ represent the sample is or isn't in the cluster respectively) correspond to a unique label.
 In our implementation, the algorithm choose four classifiers: 3,4,1,2 in order. 
-The accuracy of the four classifiers are shown in Table~\ref{tab:classifier-accuracy}.The test set has also been balanced to make the number of positive and negative samples nearly $1:1$.
+The accuracy of the four classifiers with different prune ratio is shown in \cref{tab:classifier-accuracy}.The test set has also been balanced to make the number of positive and negative samples nearly $1:1$.
 
 \begin{table}[h]
+
     \caption{Accuracy of Chosen Binary-Classifiers}
     \label{tab:classifier-accuracy}
-	\begin{tabular}{|c|c|c|c|c|}
-	\hline
+	\begin{tabular}{ccccc}
+	\toprule
 	Classifier ID & 3 & 4 & 1 & 2 \\
-	\hline
-	Accuracy & 96.0\% & 86.0\% & 91.5\% & 87.0\%\\
-	\hline
+	\midrule
+	\begin{tabular}{c}Accuracy\\pr=0.95\end{tabular} & 62.3\% & 82.3\% & 83.5\% & 67.0\%\\
+	\begin{tabular}{c}Accuracy\\pr=0.9\end{tabular} & 96.0\% & 86.0\% & 91.5\% & 87.0\%\\
+	\begin{tabular}{c}Accuracy\\pr=0.8\end{tabular} & 97.5\% & 80.5\% & 94.5\% & 89.5\%\\
+	\bottomrule
 	\end{tabular}
@@
 Actually, we can determine the class uniquely with the prefix of encodings. 
-For instance, if the result of classifier-3 is $0$, we don't need to take other classifiers into consideration since the only class $0$ is possible in cluster-3 according to Table~\ref{tab:cluster_label}
+For instance, if the result of classifier-3 is $0$, we don't need to take other classifiers into consideration since the only class $0$ is possible in cluster-3 according to \cref{tab:cluster_label}
 
-The corresponding encoding of each class label is shown in Table~\ref{tab:encoding-and-accuarcy}.
-We can determine the class label with this encoding, the accuracy of which is also shown in Table~\ref{tab:encoding-and-accuarcy}.
+The corresponding encoding of each class label is shown in \cref{tab:encoding-and-accuarcy}. 
+We can determine the class label with this encoding, the accuracy of which is also shown in \cref{tab:encoding-and-accuarcy}.
 
 \begin{table}[h]
+
     \caption{Encoding and Accuracy of Each Class Label}
     \label{tab:encoding-and-accuarcy}
-	\begin{tabular}{|c|c|c|c|c|c|c|}
-	\hline
+	\begin{tabular}{ccccccc}
+	\toprule
 	Class ID & 0 & 1 & 2 & 3 & 4 & Overall \\
-	\hline
-	Encoding &0 & 110 & 1110 &10 & 1111 &\\
-	\hline
+	\midrule
+	Encoding &0 & 110 & 1110 &10 & 1111 & -\\
+	\begin{tabular}{c}Accuracy\\pr=0.95\end{tabular} & 100\% & 30.0\% & 11.0\% & 28.0\% & 7.0\% & 34.4\%\\
+
+	\begin{tabular}{c}Accuracy\\pr=0.9\end{tabular} & 92.0\% & 93.0\% & 58.0\% & 85.0\% & 67.0\% & 79.0\%\\
+	\begin{tabular}{c}Accuracy\\pr=0.8\end{tabular} & 95.0\% & 91.0\% & 76.0\% & 78.0\% & 76.0\% & 83.2\%\\
+	\bottomrule
+
 	\end{tabular}
 \end{table}
+
+From \cref{tab:encoding-and-accuarcy}, we find the overall accuracy is quite high if prune ratio $pr\leq0.9$ while the accuracy drops dramatically when $pr=0.95$ since we prune too much channels or even destroy the connectivity of the network.
+When it comes to the trade-off between parameter number and overall accuracy, it is suitable to set prune ratio $pr=0.9$.
+Compared to the accuracy of original full model in these $5$ classes ($70.57\%$), our classifier not only achieve higher precision but also improve the efficiency.
+When $pr=0.9$, we can inference with the $4$ classifiers in parallel, which can save about $90\%$ computing consumption on a single device.
 

### 2020-01-10 paper/paper.tex
Update paper.tex

@@
 
-\todo{The overal performance score.}
-
 We define the concept of \textit{distinguishing} as follows.
@@
 In each search iteration, the algorithm will choose the classifier set that minimizes the entropy greedily, so that the search could possibly to end with minimum search depth.
-
-\todo{Analysis}
 
@@
 In other word, the encoding for a subclass is a two-hot encoding.
-\todo{This means that the assembly problem can be solved with more efficient algorithms.}
+This means that the assembly problem can be solved with more efficient algorithms.
 
@@
 \section{Conclusion}
-The conclusion \dots
+In this work, to develop task-specific and light-weighted models for edge devices, we propose a general assembly framework for binary classifers. 
+And we formulate the choice of these classifiers into a search problem. 
+We implement this framework based on CDRP method for image classification task. 
+In our experiment, we successfully reduce about $90\%$ computing consumption by pruning $90\%$ channels in the network while reach a high classification accuracy.
+
+In future work, we may take the accuracy of classifiers into account so that we can choose binary-classifiers with performance score, which can help to achieve a higher accuracy. 
+Furthermore, we can design more efficient search algorithm according to the characteristics of subclasses, for example, like each subclass only fall into two clusters as shown in  \cref{fig:network-venn}.
 

### 2020-01-10 paper/paper.tex
Update paper.tex
write abstract

@@
 \begin{abstract}
-  The abstract \dots
+  To deploy DNN models in edge devices, we need to reduce the size and complexity of the model to fit the limited energy supply and computational capability of those devices.
+  One solution to the problem is to substitute the large network with small ones and focus only on specific tasks.
+  To give an implementation of such idea, we propose a general framework of assembling multiple binary classifiers into one that performs complicated classification tasks and give an heuristic search algorithm for the classifier combination.
+  We instantiate such framework on network fusion for image classification using critical data routing path method, and we implement it to fuse two VGGNets w.r.t. part of CIFAR-100 dataset.
+  Experiments show that we can reduce about $90\%$ computing consumption by pruning convolution kernels in networks while maintain a high classification accuracy for partial classification.
 \end{abstract}
@@
 
-In this paper, we first study a framework of assembling multiple small binary classifiers into one that performs complicated classification tasks.
+We first study a framework of assembling multiple small binary classifiers into one that performs complicated classification tasks.
 \Cref{fig:assemble-example-venn} shows an example of the assembly problem of our interest.
@@
 	\item We propose a general assembly framework for binary classifiers and a heuristic algorithm to the search problem in \cref{sec:assembly}.
-	\item We instantiate the assembly framework based on the CDRP method for the image classification task on CIFAR-100 in \cref{sec:cdrp}.
-	\item We experiment such implementation on a subset of CIFAR-5 in \cref{sec:experiments}.
+	\item We instantiate the assembly framework based on the CDRP method for the image classification task in \cref{sec:cdrp}.
+	\item We experiment such implementation on a subset of CIFAR-100 in \cref{sec:experiments}.
 \end{itemize}
@@
 \section{Conclusion}
-In this work, to develop task-specific and light-weighted models for edge devices, we propose a general assembly framework for binary classifers. 
-And we formulate the choice of these classifiers into a search problem. 
+To develop task-specific and light-weighted models for edge devices, we propose a general assembly framework for binary classifers in this paper.
+We formulate the choice of these classifiers into a search problem and design a heuristic search algorithm for it.
 We implement this framework based on CDRP method for image classification task. 
@@
 
-In future work, we may take the accuracy of classifiers into account so that we can choose binary-classifiers with performance score, which can help to achieve a higher accuracy. 
+In the future, we may take the accuracy of small classifiers into account so that we can choose binary classifiers with performance score, which can help to achieve a higher accuracy. 
 Furthermore, we can design more efficient search algorithm according to the characteristics of subclasses, for example, like each subclass only fall into two clusters as shown in  \cref{fig:network-venn}.

### 2020-01-10 paper/paper.tex

@@
     \label{tab:encoding-and-accuarcy}
+	\scalebox{0.9}{
 	\begin{tabular}{ccccccc}
@@
 	\end{tabular}
+	}
 \end{table}
@@
 \section{Conclusion}
-To develop task-specific and light-weighted models for edge devices, we propose a general assembly framework for binary classifers in this paper.
-We formulate the choice of these classifiers into a search problem and design a heuristic search algorithm for it.
+To develop task-specific and light-weighted models for edge devices, we propose a general assembly framework for binary classifiers in this paper.
+We formulate the problem of selecting and combining classifiers into a search problem and design a heuristic search algorithm to solve it.
 We implement this framework based on CDRP method for image classification task. 

### 2020-01-10 paper/paper.tex
some adjustments

@@
 To have overlapping classifiers, we decompose two different networks on the same dataset and fine tuning the CDRP models into binary classifiers.
-We use image classification task on CIFAR-100 and VGG16 of type C and D for demonstration.
+We use image classification task on CIFAR-100 and VGG16 of type C and type D for demonstration.
 
@@
 Given encodings under the initial classifier set, samples share the same encoding can be considered as a subclass, and there is no need to further split those subclasses.
-For example, in the intro example in Figure~\ref{fig:assemble-example-venn}, there is no need to distinguish $A_{11}$ and $A_{12}$ and we can group them as a single subclass.
+For example, in the intro example in \Cref{fig:assemble-example-venn}, there is no need to distinguish $A_{11}$ and $A_{12}$ and we can group them as a single subclass.
 
 \subsection{CDRP Decomposition and Clustering}
-Guideline:
-\begin{itemize}
-	\item How to train gates, the functionality of the gates, how to interpret gate weight (lambda) feature of samples (similar to original paper)
-	\item How to get decomposed classifiers: clustering
-	\item Why clustered CDRP models might work (PCA visualization demonstration) (not performance analysis, inference experiments later)
-	\item Why fine tuning the clustered CDRP model into binary classifiers, and how we fine tune them
-\end{itemize}
-
 Critical Data Routing Path is a method to find a path containing critical nodes, whose removal causes great preformance setback, from an existing trained model.
@@
 
-\paragraph{CDRP extraction}
+\paragraph{CDRP extraction.}
 
 From the original model, we introduce a scalar control gate to every output channel of one layer, with nonnegative and sparse value.
-They will be multiplied to the layer’s output channelwise, resulting in the routing nodes.
+They will be multiplied to the layer's outputs channelwise, resulting in the routing nodes.
 The nodes that are not suppressed, or have control gate weight greater zero, will be linked together to compose the routing paths.
@@
 \begin{algorithm}
-	\caption{Distillation Guided Routing, introduced in paper \cite{wang2018interpret}}
+	\caption{Distillation Guided Routing, from \cite{wang2018interpret}}
 	\label{alg:dgr}
@@
 
-\paragraph{CDRP clustering}
+\paragraph{CDRP clustering.}
 
@@
 
-\begin{figure}[!htp]
+\begin{figure}
 	\centering
@@
 
-\paragraph{Model pruning and fine tuning}
+\paragraph{Model pruning and fine tuning.}
 
@@
 \section{Experiments}
+In this section, we implement the CDRP decomposition and assembly framework instantiated in \cref{sec:cdrp}.
+We perform K-Means on the CDRP control gates of each sample and extract binary classifiers from clusters' corresponding CDRP model.
+We apply the search \cref{tab:heuristic-search} in \cref{sec:assembly-algorithm} to fuse those classifiers, and we test the performance of each binary classifiers and the combined model.
+
 \label{sec:experiments}
 \subsection{Verifying CDRP Models of VGGNets trained on CIFAR-100}
-In this section, we perform K-Means on the CDRP control gates of each sample.
-For each cluster, we get a binary-classifier to determine whether the test sample should be in the cluster.
-Then, we fine tune each classifier in the CIFAR-100 dataset.
-
 \paragraph{Clusters.} For VGGNet, we generate $1.5$ clusters per class.
@@
 
-The sample distribution of each cluster is shown in Figure~\ref{fig:vgg-cluster}.
+The sample distribution of each cluster is shown in \Cref{fig:vgg-cluster}.
 
-\begin{figure}[!htp]
+\begin{figure}[h]
     \centering
+    \begin{minipage}{0.99\linewidth}
 		\subfigure[Clusters from VGG-C]{
-    \begin{minipage}[t]{1\linewidth}
-        \includegraphics[height=1.5in,width=2.8in]{fig/chart1.pdf}
+			\includegraphics[width=\linewidth]{fig/chart1.pdf}
 			\label{fig:net2a}
+		}
     \end{minipage}
-}
 
     %\vfill
+    \begin{minipage}{0.99\linewidth}
 		\subfigure[Clusters from VGG-D]{
-    \begin{minipage}[t]{1\linewidth}
-        \includegraphics[height=1.5in,width=2.8in]{fig/chart2.pdf}
+			\includegraphics[width=\linewidth]{fig/chart2.pdf}
 			\label{fig:net2b}
+		}
     \end{minipage}
-}
     \caption{Sample Distribution of Clusters from Different Types of VGGNets}
@@
 \subsection{Fusing VGGNets for Specific Tasks through CDRP Assembly}
-In this section, we implement the heuristic search in \cref{tab:heuristic-search} to fuse the classifiers.
-According to the 0/1 result of each classifier, we can get an unique encoding for each sample, which corresponds to a unqiue label so that we can determine the class of each test sample.
 
-\paragraph{Fusion}We implement \cref{tab:heuristic-search} to fuse the classifiers since we want to finish a specific task of classifying among five classes, we set a upper bound of the number of classifiers $k=4$.
+\paragraph{Fusion.} We implement \cref{tab:heuristic-search} to fuse the classifiers since we want to finish a specific task of classifying among five classes, we set a upper bound of the number of classifiers $k=4$.
 After we select these classifiers with this \cref{tab:heuristic-search}, different results of each classifier ($0$ and $1$ represent the sample is or isn't in the cluster respectively) correspond to a unique label.
